### 2015-10-02 paper.tex
Added LaTeX files.

\documentclass{sig-alternate}

\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}
\usepackage[pdftex,urlcolor=black,colorlinks=true,linkcolor=black,citecolor=black]{hyperref}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Subsection}
\usepackage{graphicx}
% todo macro
\usepackage{color}
\newcommand{\todo}[1]{\noindent\textcolor{red}{{\bf \{TODO}: #1{\bf \}}}}

\title{From Freebase to Wikidata: The Great Migration}

\numberofauthors{3}
\author{
Thomas Pellissier Tanon, Denny Vrandečić\\
   \affaddr{Google, San Francisco}\\
   \email{\{thomaspt, vrandecic\}@google.com}
\alignauthor
Sebastian Schaffert\\
   \affaddr{Google, Zurich}\\
   \email{schaffert@google.com}
\alignauthor
Thomas Steiner\\
   \affaddr{Google, Hamburg}\\
   \email{tsteiner@google.com}
}

\begin{document}

\maketitle

\begin{abstract}
Freebase was a~collaborative knowledge base created in 2007 and acquired by Google in 2010.
Wikidata is a~collaborative knowledge base created by the Wikimedia movement in 2012.
Due to the success of Wikidata, Google decided to shut down Freebase and
help with the transfer of its content to Wikidata.
In this paper, we describe some of the ongoing transfer effort and challenges,
and provide an analysis of the transfer so far.
\end{abstract}

% a~category with the (minimum) three required fields
\category{H.4}{\todo{Hierarchy}}{Miscellaneous}

\terms{\todo{Terms}}

\keywords{\todo{Keywords}}

\section{Introduction}

Moving data between two knowledge bases that do not share a~similar design
is usually a~problematic task and requires the careful mapping between their structures.
In this paper, we describe how we facilitated the migration of Freebase content to Wikidata.
That migration made no exception to the rule, and had a~number of structural challenges.
Even more challenging was the cultural difference between the two involved communities.
The Freebase and Wikidata communities have a~very different background,
subtly different goals and understandings of their tasks,
and different requirements regarding their data.
This paper is structured as follows.
After a~short introduction to the two databases, we describe our methodology and
the metrics used to measure the migration.
In order to support the migration, we have developed a~set of open source tools
that we present in the following.
We then present the results of the migration and discuss these numbers,
as well as proposed next steps.

\section{Background}

\subsection{Freebase}

Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open source and
collaborative knowledge base created in 2007 by Metaweb and bought in 2010 by Google.
It was used as the open core of the Google Knowledge Graph,
and also in many use cases outside of Google.
Due to the success of Wikidata,
it was decided to close Freebase and support the migration of Freebase' content to Wikidata.
Freebase' content relies on the notions of topics, facts, types, and properties.
Each Freebase topic has a~stable identifier called a~mid and one or more types
and uses properties from these types in order to provide facts.
For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
and the type \texttt{/government/us\_president} that allows the entity to have
a fact with the property \texttt{/government/us\_president/presidency\_number}
and the literal integer ``44'' as the value.

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/freebase-cvt-obama.png}
\caption{Example of CVT: presidency of Barack Obama}
\label{fig-cvt-obama}
\end{figure}

To represent complex values like geocoordinates or to annotate relations,
for example in order to add start and end dates for a~position held,
Freebase has introduced the notion of Compound Value Types (CVTs, see \autoref{fig-cvt-obama}).
They behave like topics, \emph{e.g.}, have a~mid and can have types,
but do not have the \texttt{/common/topic} type.
The content of Freebase has been imported from various sources like Wikipedia or IMDB
and, so, Google does not own the copyright of some parts of the Freebase content
like images or long entity descriptions extracted from Wikipedia.
As of the closing of Freebase, it counted more than 3~billion facts
about almost 50M~entities.

\subsection{Wikidata}

Wikidata\footnote{Wikidata: \url{https://www.wikidata.org}}
is a~collaborative knowledge base
launched in October 2012 and hosted by the Wikimedia Foundation.
Its community has been growing quickly since the beginning and as of mid 2015,
the community comprises about 6,000 active contributors.

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/Wikidata-statement.png}
\caption{An example of Wikidata statement (from
\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
\label{fig-statement}
\end{figure}

Wikidata content relies on the notions of item and statement.
An item represent a~concept, has a~stable identifier and may has some labels,
descriptions and aliases in multiple languages, links to pages about this concept
in the others Wikimedia projects, like Wikipedia, and statements.
Contrary to Freebase, Wikidata encodes with its statements not true facts
but claims from different sources.
A statement is composed of one claim and zero or more references of this claim.
The claim itself is composed on one main (property, value) couple that encodes
the main fact like ``population is 8,173,900'' and optional qualifiers
to add information about the main affirmation like ``as of June 2012''.
As of mid 2015, Wikidata counted about 66M~statements on 14M~entities.
For more about Wikidata see \cite{vrandevcic2014wikidata}
and for a~comparison between Freebase and Wikidata see \cite{farbercomparative}.

\section{Challenges of the migration}

Migrating data from Freebase to Wikidata faced a~number of challenges:

\subsection{Licensing}
\label{sec-licensing}

The first challenge is regarding the licenses under which the datasets are published.
Wikidata is published under a~Creative Commons~0 (CC0) licence (similar to the public domain),
while Freebase is under a~Creative Commons By licence and contains data
imported from external projects not owned by Google,
like images or descriptions extracted from Wikipedia.
In a~first step we filtered the Freebase dump from this kind of content
before being able to have a~dump that Google could relicense under CC0.
This step reduces the number of republishable Freebase facts by about 42M~facts.

\subsection{References}

The second challenge is that the Wikidata community is very interested to have references
for their statements, sources that Freebase usually did not store except for
some specific data like populations and unemployment rates.
For these two specific cases we have just kept the references from Freebase.
In order to provide the Wikidata community with references for the facts in Freebase
we have reused data from the Knowledge Vault, another Google project with the aim
to extract facts from the web (see \cite{dong2014knowledge}).
Whereas the fact extraction was usually correct, the pages Knowledge Vault extracted
the references from often do not meet the requirement for a~good reference:
they include pages in social networks, shopping sites, filesharers, \emph{etc.}
It became necessary to filter and curate the references before inclusion in Wikidata.

\subsection{Data quality}

The quality of the data in Freebase was challenged by the Wikidata community.
For example, a~small city in France had an ISO country code%
\footnote{See \url{http://www.freebase.com/m/03cc0d0}}.
Another example, Boston (the city in Massachusetts) has the type \textit{/people/person}.
A fully automatic upload of all the content from Freebase into Wikidata
did not seem advisable as the expectations of the community regarding
the quality of the content automatically added to Wikidata are high (and rightly so).
Also, whereas an upload of all the data might have lead to accelerated growth
in the short term, such a~fast upload might also endanger the sense of ownership
the Wikidata community has for its data.
Instead we decided to rely on human curation and created Primary Sources,
a simple tool which displays statements to the user that may be added to the currently shown item.
The user can, with only one click, reject the statement or approve it and save it to Wikidata.
It is currently available as a~gadget, an opt-in option in Wikidata.
This tool has no dependencies on Freebase and may be easily reused by other projects
which may want to import data into Wikidata.
For that we have implemented an upload API and a~feature that allows users
to display only statements from a~given dataset.
In fact, during the project one other researcher approached us in order to upload
a dataset extracted from natural language text.
A statistics dashboard has also been created in order to monitor the curation work
\url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}
and the source code of the tool is available on GitHub:
\url{https://github.com/google/primarysources}.

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/primary-sources.png}
\caption{Primary Sources user interface}
\end{figure}

Currently (August~18, 2015) the tool has been used by more than a~hundred users
who have performed more than 15,000 approve or reject actions.
More than 12M~statements are uploaded to the tool.

\subsection{Mappings}

\subsubsection{Mappings of items}

Another challenge is to get a~good mapping between Freebase topics and properties
and Wikidata items and properties.
Two mappings between Freebase topics and Wikidata items were initially available,
and we worked on further mappings.
A first one has been created by Google in October 2013%
\footnote{Freebase mappings \url{http://developers.google.com/freebase/data}}
and is based on Wikipedia links already present in Freebase: if a~Freebase topic and
a Wikidata items share at least two Wikipedia links, then they are about the same subject.
The quality of this mapping is considered as very good by the Wikidata community
who have uploaded it to the wiki and further curated and maintained it by hand.
It maps 1.15M~of Freebase topic.
A second mapping has been created by Samsung, and is actively maintained%
\footnote{Samsung mappings \url{http://github.com/Samsung/KnowledgeSharingPlatform}.}.
It is based on the same idea but matches a~Freebase topic with a~Wikidata item
even if there is only a~single Wikipedia link shared.
The quality of the mapping is lower (there are some wrong matches,
often because there is no clear separation between topics and disambiguation pages in Wikipedia)
but it provides 4.4M~links.
As we have seen before, our quality target is not very high,
so we have chosen to merge the two dumps and, for the 6,000 conflicts,
to prioritize the mapping given by Wikidata.
To improve the resulting mapping we have also tried to do some reconciliation
based on external database IDs shared by Freebase and Wikidata, like MusicBrainz, VIAF, \emph{etc.}
With this technique we were able to match 0.8M~IDs,
creating a~mapping for 0.6M~topics---most of them already in our dataset.
This resulted in an additional 84,000 items mapped.
We also used data from Google's Knowledge Graph to add 0.1M~further mappings
matching also a~topic and an item if they share a~Wikipedia link.
We could maybe add some more data by looking at functional relations like ``father'' and ``mother''.
But these relations only apply to relatively small sets of data (like well known families)
and the functional assumption may run into some edge cases.
For example, the \texttt{/people/person/parents} property in Freebase also covers also stepparents,
creating cases where a~person has more than one male or female \texttt{/people/person/parents}.
Eventually, with these four sources we mapped 4.56M~items.
We believe that by doing so we have mapped most of the topics that could be automatically mapped
as suggested by the small increases added by the ID reconciliation approach
and the Knowledge Graph data.
Furthermore, the mapped topics have an average number of facts of about~13.9,
whereas the topics that were not mapped have an average of 5.7~facts.
We have mapped the majority of topics with more than 80~facts.
This allows us to conclude that we have mapped the most important items of Freebase.

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/facts-topics-mapping.png}
\caption{Number of mapped and not mapped topics with more than x facts.
Note the log scale on both axis.}
\end{figure}

\subsubsection{Mapping of properties}

For the mapping between Freebase and Wikidata properties we have chosen to do it by hand
with the help of the Wikidata community.
With that we have been able to map quickly around 360~properties
(note that Wikidata has a~total of 1,660 properties, and Freebase has around 37,700 properties).
For the mapping of properties where the domain are other topics or literals
this mapping provides the Wikidata property to use.
We have also implemented a~special case for \texttt{/people/person/parents}
in order to be able to map them to Wikidata properties ``father'' and ``mother''
based on the person gender.
The mapping of CVTs is more complicated because it is not possible to have a~1~to~1 relationship
between Freebase and Wikidata properties: the CVT is linked to the subject topic by one property
and has properties pointing to its component values, whereas the Wikidata statement
has a~main property value group that is qualified by other such groups.
In order to map a~CVT to a~statement, we have to know which of the CVT's properties
should be used as the main value of the statement, with the others being mapping to qualifiers.
In order to keep a~simple mapping associating one Wikidata property to one Freebase property,
we map both the property linking the topic to the CVT
and the main property of the CVT to the same Wikidata property, and, during the mapping process,
we pick the later as the main property of the CVT.
For example, if we try to map the same CVT as \autoref{fig-cvt-obama}
we will use the Wikidata property ``position held (P39)'' to map
\texttt{/politician/government\_positions\_held} and
\texttt{/government\_position\_held/office\_position\_or\_title}, use ``start time (P580)''
for \texttt{/government\_position\_held/from} and ``end time (P582)'' for
\texttt{/government\_position\_held/to}.
With this mapping the created Wikidata statement will be
like the one presented in \autoref{fig-statement-obama}.

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/wikidata-statement-obama.png}
\caption{Target Wikidata statement}
\label{fig-statement-obama}
\end{figure}

For CVTs that include sources, we map the property that links the CVT
to the source as a~Wikidata reference instead of a~qualifier.
The last challenge is to do the real mapping, taking care of CVTs
and the complex datatypes of Wikidata.
For CVTs, when we have a~triple whose value is a~CVT, we just retrieve it,
map all its component triples (while ignoring ones that can't be mapped)
and apply the above mechanism to get its main value.
For values, we use the datatype information stored with Wikidata properties
in order to cast values to the right type.
For quantities we assume that the amounts are precise
as there is no precision information in Freebase.
For globe coordinates we have hardcoded the mapping of the \texttt{/location/geocode} CVT
into the globe-coordinate value type of Wikibase
and use the same precision guess algorithm as the one used by Wikidata user interface.
For dates we just map the date and time values (encoded using XSD%
\footnote{\url{ http://www.w3.org/TR/xmlschema11-2/}} types)
to the Wikidata ``time'' datatype but we filterout dates before 1920 that have
a higher precision than year because we do not know
if there are in Julian or Gregorian calendar and so,
we are not able to fill the ``calendar'' metadata of the Wikidata ``time'' datatype.

\section{How numbers lie}

Here is an overview of the size of the last dump of Freebase:

\begin{itemize}
  \setlength\itemsep{0em}
  \item 48M~topics
  \item 2,997M triples
  \item 442M facts owned by Google\footnote{These ``facts'' are the Freebase triples
      after having filterout the data about ids (\texttt{/type/object/id}),
      types (\texttt{/type/object/type}), labels and descriptions (\texttt{/type/object/name},
      \texttt{/common/topic/description}...) and triples that should be filtered
      for legal reasons (see \autoref{sec-licensing}).}
  \item 68M~labels
\end{itemize}

To compare, Wikidata contains (as of August 2015):

\begin{itemize}
    \setlength\itemsep{0em}
    \item 14.5M~items
    \item 66M~statements
    \item 82M~labels
\end{itemize}

But why are these numbers so different?
Regarding the number of topics, Freebase has a~lot of topics about subjects
that do not match the Wikidata notability criteria%
\footnote{\url{https://www.wikidata.org/wiki/Wikidata:Notability}}.
For example, Freebase has 11.3M~musical recordings, 8.3M~music canonical versions,
2.6M~ISBNs, \emph{etc.}
We also cannot compare the number of facts and the number of statements directly,
even considering the lower number of topics.
Freebase encodes its knowledge in far many more facts than Wikidata needs statements.
Properties in Freebase often have a~reverse property used in order to be able
to traverse the Freebase graph easily in both directions.
For example the property \texttt{/people/person/place\_of\_birth} will have as reverse
the property \texttt{/location/location/people\_born\_here} that encodes
exactly the same semantic information.
Such reverses sometimes exist in Wikidata (like ``children'' for ``father'' and ``mother'')
but are far less common.
Another point is that CVTs use a~lot of facts to tell the same thing that
would be represented by a~single Wikidata statement.
For example, to encode that Barack Obama is the president of the United States from June~20, 2009,
Freebase requires more than six facts as shown in \autoref{fig-cvt-obama}.
If we try to encode Wikidata statements as if they were Freebase facts, \emph{i.e.},
by removing sources, representing statements with qualifiers using CVTs
and adding reverse properties it would lead to 110M of facts,
\emph{i.e.}, 167\% of the raw number of statements.
Sometimes, Freebase contains also duplicate data.
For example, a~lot of cities in the United States have duplicate CVTs for the population
where the only change is the encoding of the source
%\footnote{See, for example, \url{http://www.freebase.com/m/01jr6}.}.

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/wikidata-time-space.png}
\caption{Time and spatial distribution of Wikidata items.
Longitude is in $x$ axis and time, following a~power law ($y' = y^8$), is in $y$ axis}
\label{fig-time-space-wikidata}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/freebase-time-space.png}
\caption{Same figure for Freebase entities}
\label{fig-time-space-freebase}
\end{figure}

We have also created a~time-spatial visualization of Freebase and Wikidata in order
to get an idea of the coverage of the two knowledge bases
(see \autoref{fig-time-space-wikidata} and \autoref{fig-time-space-freebase}).
The used method is to extract the earliest date and the longitude
linked to each knowledge base entities
and propagate them to the connected entities which do not have such data
using a~decreasing exponential distribution.
We see that the two knowledge bases follow the same basic patterns,
with a~coverage mostly concentrated on Europe and North America,
and there are no strong differences between them.
The coverage of the after 2000 entities seems better in Freebase, maybe because of
the presence of a~lot of musical data missing in Wikidata and of the U.S.
population CVTs.
The big horizontal lines seems to be mostly due on places that do not have any linked date
and so inherit the foundation date of their country.
For Wikidata, two lines that are caused by this behavior are the big line over the U.S.A around 1780
and the one covering Russia around 850.
We could conclude from this visualization that Wikidata, even with its smaller size,
seems to have a~nearly as good coverage of the world as Freebase.
To conclude, it is tricky to find good ways to compare the two databases
and good metrics of success for the migration and we could state that, for a~knowledge base,
containing far more triples than the other does not mean
it contains the same proportion of additional good data.

\section{Statistics on the migration}

From the Freebase dump we have been able to create more than 17M~Wikidata claims
(\emph{i.e.}, statement without references) including 1.5M~IDs.
For that we have used 31M~facts.
When we add some references we get 19.6M~statements, and, after removing 1M~of duplicates
and the ones already in Wikidata, we obtain 14M~new statements.
So, if all these statements were added to Wikidata,
it would lead to a~21\% increase of Wikidata statements number.
But why are these numbers so low compared to the size of Freebase?
We believe that the main reason is that we have only mapped to Wikidata 4.56M~items, (\emph{i.e.},
only 9.5\% of Freebase topics), that are the subject of only 64M~facts.
So, we could not hope to map more than 64M~statements
assuming that we could map all reverse properties, and we couldn't.
So, assuming that we do not care about the not mapped topics,
we have created a~statement for more than 24\% of the facts.
If we restrict ourselves to the reviewed facts, a~set of 1.6M~facts
that have been human curated, we have far better results.
There are 0.58M~facts which subjects are mapped to Wikidata and 0.52M~of them
(\emph{i.e.}, 92\%) are converted into Wikidata statements.
And we would get another 1\% if we would be able
to map the properties \texttt{/people/person/weight\_kg}
and \texttt{/people/person/height\_meters} that Wikidata are not supporting yet.
58\% of the statements created from reviewed fact are already in Wikidata,
allowing us to add 0.25M~of new reviewed statements to Wikidata.

\section{What could we do next?}

We believe that the main way of improvements is to extend the migration to more Freebase topics
by suggesting Wikidata users to create new Wikidata items.
A possible way of doing it is to create a~small gamified user interface that would allow users
to create new Wikidata items for a~suggested topic or to add map them to an existing Wikidata item.
In order to suggest interesting topics to add to Wikidata
we could rank the not mapped yet topics per number of incoming links from already mapped topic
and filter not interesting types like ISBNs.
Another way of improvement is to upload using a~bot high quality datasets,
like the reviewed facts or some sets,
for external ids in order to speed up the integration of Freebase content into Wikidata.
We have already started to upload the simple reviewed facts about humans
like birth date, death place or gender using a~bot.
We have also started to investigate on importing some labels
that are in Freebase and are missing in Wikidata.
In the 17.2M~of Freebase labels for mapped topics only 0.9M, \emph{i.e.},
5\%, are missing in Wikidata.

\section{Conclusion}

We have been able in a~fairly short amount of time to provide to the Wikidata community
more than 14M~of new Wikidata statements using a~new tool
well integrated into the Wikidata user interface.
The effort needed to map two fairly different knowledge bases has also been a~good occasion
to highlight the difficulty to have good metrics to measure the size
and, so, the ``value'', of such databases.
We hope that this project will allow to increase the completeness of Wikidata and,
helped by the comparison to another database, to improve its quality.

\bibliographystyle{abbrv}
\bibliography{biblio}

\balancecolumns
\end{document}

### 2015-10-05 paper.tex
Typo detail
Some abstract and author tuning.

@@
 \author{
-Thomas Pellissier Tanon, Denny Vrandečić\\
-   \affaddr{Google, San Francisco}\\
+Thomas Pellissier Tanon,\titlenote{The author was an intern at Google when the majority of the work was done.}\ Denny Vrandečić\\
+   \affaddr{Google, San Francisco, United States of America}\\   
    \email{\{thomaspt, vrandecic\}@google.com}
@@
 Sebastian Schaffert\\
-   \affaddr{Google, Zurich}\\
+   \affaddr{Google, Zurich, Switzerland}\\   
    \email{schaffert@google.com}
@@
 Thomas Steiner\\
-   \affaddr{Google, Hamburg}\\
+   \affaddr{Google, Hamburg, Germany}\\   
    \email{tsteiner@google.com}
@@
 \begin{abstract}
-Freebase was a~collaborative knowledge base created in 2007 and acquired by Google in 2010.
-Wikidata is a~collaborative knowledge base created by the Wikimedia movement in 2012.
+Collaborative knowledge bases that make their data available in machine-readable form
+as structured data are central to many companies' data strategies.
+One example of such collaborative knowledge bases is Freebase (\url{www.freebase.com}),
+created with proprietary technologies in 2007 by a~company called Metaweb,
+which was then acquired by Google in 2010.
+Another example is Wikidata (\url{www.wikidata.org}),
+a~collaborative knowledge base developed in the open since 2012 by Wikimedia Deutschland
+and operated by the Wikimedia Foundation.
 Due to the success of Wikidata, Google decided to shut down Freebase and
-help with the transfer of its content to Wikidata.
-In this paper, we describe some of the ongoing transfer effort and challenges,
-and provide an analysis of the transfer so far.
+help with the transfer of its content to Wikidata through a~crowdsourcing approach.
+In this paper, we describe the ongoing transfer efforts and challenges,
+and provide an analysis of the process so far.
 \end{abstract}
@@
 \footnote{See \url{http://www.freebase.com/m/03cc0d0}}.
-Another example, Boston (the city in Massachusetts) has the type \textit{/people/person}.
+Another example, Boston (the city in Massachusetts) has the type \texttt{/people/person}.
 A fully automatic upload of all the content from Freebase into Wikidata

### 2015-10-05 paper.tex
Some introduction, paper structure, and bibliography fixes.

@@
 In this paper, we describe how we facilitated the migration of Freebase content to Wikidata.
-That migration made no exception to the rule, and had a~number of structural challenges.
-Even more challenging was the cultural difference between the two involved communities.
+That migration was no exception to this rule, and had a~number of \emph{structural} challenges.
+Even more challenging was the \emph{cultural} difference between the two involved communities.
 The Freebase and Wikidata communities have a~very different background,
@@
 and different requirements regarding their data.
-This paper is structured as follows.
-After a~short introduction to the two databases, we describe our methodology and
-the metrics used to measure the migration.
+\todo{Expand}
+
+The remainder of this paper is structured as follows.
+After an introduction to the two collaborative knowledge bases
+Freebase and Wikidata in \autoref{sec:background},
+we describe our methodology and the metrics used to measure the migration
+in \autoref{sec:challenges-of-the-migration}.
 In order to support the migration, we have developed a~set of open source tools
-that we present in the following.
-We then present the results of the migration and discuss these numbers,
-as well as proposed next steps.
+that we present in \autoref{sec:primary-sources-tool}.
+We then present the results of the migration
+and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
+The paper terminates with an outlook at proposed next steps
+and a~conclusion in \autoref{sec:future-work-and-conclusion}.
 
-\section{Background}
+\section{Background}\label{sec:background}
 
@@
 
-\section{Challenges of the migration}
+\section{Challenges of the migration}\label{sec:challenges-of-the-migration}
 
@@
 
-\subsection{Data quality}
+\subsection{Data Quality}
 
@@
 
-\subsubsection{Mappings of items}
+\subsubsection{Mappings of Items}
 
@@
 
-\subsubsection{Mapping of properties}
+\subsubsection{Mapping of Properties}
 
@@
 
-\section{How numbers lie}
+\section{Primary Sources Tool}\label{sec:primary-sources-tool}
+
+\subsection{Data Preparation}
+
+\todo{Denny: write me}
+
+\subsection{Back-end of the Tool}
+
+\todo{Sebastian: write me}
+
+\subsection{Front-end of the Tool}
+
+\todo{Tom: write me}
+
+\section{Statistics on the Migration}\label{sec:statistics-of-the-migration}
 
@@
 
-\section{Statistics on the migration}
+\subsection{Raw Statistics}
 
@@
 
-\section{What could we do next?}
+\section{Future Work and Conclusion}\label{sec:future-work-and-conclusion}
 
@@
 
-\section{Conclusion}
-
 We have been able in a~fairly short amount of time to provide to the Wikidata community

### 2015-10-05 paper.tex
Reworked Freebase subsection.

@@
 Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open source and
-collaborative knowledge base created in 2007 by Metaweb and bought in 2010 by Google.
+collaborative knowledge base created in 2007 by Metaweb and acquired in 2010 by Google.
 It was used as the open core of the Google Knowledge Graph,
-and also in many use cases outside of Google.
+and also has many use cases outside of Google.
+
 Due to the success of Wikidata,
-it was decided to close Freebase and support the migration of Freebase' content to Wikidata.
-Freebase' content relies on the notions of topics, facts, types, and properties.
-Each Freebase topic has a~stable identifier called a~mid and one or more types
-and uses properties from these types in order to provide facts.
+it was decided to close Freebase and support the migration of its contents to Wikidata.
+Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
+Each Freebase topic has a~stable identifier called \emph{``mid''} (for Metaweb ID),
+one or more types, and uses properties from these types in order to provide facts.
 For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
@@
 
-\begin{figure}
+\begin{figure}[!htbp]
 \centering
 \includegraphics[width=8.45 cm]{img/freebase-cvt-obama.png}
-\caption{Example of CVT: presidency of Barack Obama}
+\caption{\todo{Crop, get PDF version} Example of CVT: presidency of Barack Obama}
 \label{fig-cvt-obama}
@@
 
-To represent complex values like geocoordinates or to annotate relations,
-for example in order to add start and end dates for a~position held,
+To represent complex values like geographic coordinates or to annotate relations,
+for example, in order to add start and end dates for a~position held,
 Freebase has introduced the notion of Compound Value Types (CVTs, see \autoref{fig-cvt-obama}).
@@
 but do not have the \texttt{/common/topic} type.
-The content of Freebase has been imported from various sources like Wikipedia or IMDB
-and, so, Google does not own the copyright of some parts of the Freebase content
+
+The contents of Freebase have been imported from various sources like Wikipedia
+or the Internet Movie Database IMDB,
+in consequence Google does not own the copyright of some parts of the contents of the knowledge base
 like images or long entity descriptions extracted from Wikipedia.
-As of the closing of Freebase, it counted more than 3~billion facts
-about almost 50M~entities.
+As of the closing of Freebase on March~31, 2015,
+it counted more than 3~billion facts about almost 50M~entities.
 
@@
 
-\begin{figure}
+\begin{figure}[!htbp]
 \centering
 \includegraphics[width=8.45 cm]{img/Wikidata-statement.png}
-\caption{An example of Wikidata statement (from
+\caption{\todo{Get PDF version} An example of Wikidata statement (from
 	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
@@
 
-\begin{figure}
+\begin{figure}[!htbp]
 \centering

### 2015-10-05 paper.tex
Reworked Wikidata subsection.

@@
 
-Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open source and
+Freebase\footnote{Freebase: \url{https://www.freebase.com/}} is an open source and
 collaborative knowledge base created in 2007 by Metaweb and acquired in 2010 by Google.
@@
 \caption{\todo{Crop, get PDF version} Example of CVT: presidency of Barack Obama}
-\label{fig-cvt-obama}
+\label{fig:cvt-obama}
 \end{figure}
@@
 for example, in order to add start and end dates for a~position held,
-Freebase has introduced the notion of Compound Value Types (CVTs, see \autoref{fig-cvt-obama}).
+Freebase has introduced the notion of Compound Value Types (CVTs, see \autoref{fig:cvt-obama}).
 They behave like topics, \emph{e.g.}, have a~mid and can have types,
@@
 
-Wikidata\footnote{Wikidata: \url{https://www.wikidata.org}}
+Wikidata\footnote{Wikidata: \url{https://www.wikidata.org/wiki/Wikidata:Main_Page}}
 is a~collaborative knowledge base
 launched in October 2012 and hosted by the Wikimedia Foundation.
-Its community has been growing quickly since the beginning and as of mid 2015,
+Its community has been growing quickly since the beginning, and as of mid 2015,
 the community comprises about 6,000 active contributors.
+
+Wikidata contents rely on the notions of \emph{item} and \emph{statement}.
+An item represent a~concept, has a~stable identifier and may have some labels,
+descriptions, and aliases in multiple languages, links to pages about this concept
+in the others Wikimedia projects, like Wikipedia, and statements.
+Contrary to Freebase, Wikidata encodes with its statements not true facts,
+but \emph{claims} from different sources.
+
+A~statement is composed of one claim and zero or more references for this claim.
+The claim itself is composed of one main property--value couple that encodes
+the main (claimed) fact like ``population is 8,173,900'' and optional qualifiers
+to add information about it like ``as of June 2012''.
+\autoref{fig:statement} illustrates the used nomenclature with an example.
+
+The contents of Wikidata are freely available under a~Creative Commons~0 (CC0) license.
+As of mid 2015, Wikidata counted about 66M~statements on 14M~entities.
+For more background information about Wikidata, see~\cite{vrandevcic2014wikidata}
+by Vrandečić and Krötzsch.
+For a~comparison between Freebase and Wikidata,
+we refer the reader to~\cite{farbercomparative} by Färber \emph{et~al.}
 
@@
 	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
-\label{fig-statement}
+\label{fig:statement}
 \end{figure}
-
-Wikidata content relies on the notions of item and statement.
-An item represent a~concept, has a~stable identifier and may has some labels,
-descriptions and aliases in multiple languages, links to pages about this concept
-in the others Wikimedia projects, like Wikipedia, and statements.
-Contrary to Freebase, Wikidata encodes with its statements not true facts
-but claims from different sources.
-A statement is composed of one claim and zero or more references of this claim.
-The claim itself is composed on one main (property, value) couple that encodes
-the main fact like ``population is 8,173,900'' and optional qualifiers
-to add information about the main affirmation like ``as of June 2012''.
-As of mid 2015, Wikidata counted about 66M~statements on 14M~entities.
-For more about Wikidata see \cite{vrandevcic2014wikidata}
-and for a~comparison between Freebase and Wikidata see \cite{farbercomparative}.
 
@@
 The first challenge is regarding the licenses under which the datasets are published.
-Wikidata is published under a~Creative Commons~0 (CC0) licence (similar to the public domain),
-while Freebase is under a~Creative Commons By licence and contains data
+Wikidata is published under a~Creative Commons~0 (CC0) license (similar to the public domain),
+while Freebase is under a~Creative Commons By license and contains data
 imported from external projects not owned by Google,
@@
 we have reused data from the Knowledge Vault, another Google project with the aim
-to extract facts from the web (see \cite{dong2014knowledge}).
+to extract facts from the web (see~\cite{dong2014knowledge}).
 Whereas the fact extraction was usually correct, the pages Knowledge Vault extracted
@@
 we pick the later as the main property of the CVT.
-For example, if we try to map the same CVT as \autoref{fig-cvt-obama}
+For example, if we try to map the same CVT as \autoref{fig:cvt-obama}
 we will use the Wikidata property ``position held (P39)'' to map
@@
 With this mapping the created Wikidata statement will be
-like the one presented in \autoref{fig-statement-obama}.
+like the one presented in \autoref{fig:statement-obama}.
 
@@
 \caption{Target Wikidata statement}
-\label{fig-statement-obama}
+\label{fig:statement-obama}
 \end{figure}
@@
 For example, to encode that Barack Obama is the president of the United States from June~20, 2009,
-Freebase requires more than six facts as shown in \autoref{fig-cvt-obama}.
+Freebase requires more than six facts as shown in \autoref{fig:cvt-obama}.
 If we try to encode Wikidata statements as if they were Freebase facts, \emph{i.e.},
@@
 Longitude is in $x$ axis and time, following a~power law ($y' = y^8$), is in $y$ axis}
-\label{fig-time-space-wikidata}
+\label{fig:time-space-wikidata}
 \end{figure}
@@
 \caption{Same figure for Freebase entities}
-\label{fig-time-space-freebase}
+\label{fig:time-space-freebase}
 \end{figure}
@@
 to get an idea of the coverage of the two knowledge bases
-(see \autoref{fig-time-space-wikidata} and \autoref{fig-time-space-freebase}).
+(see \autoref{fig:time-space-wikidata} and \autoref{fig:time-space-freebase}).
 The used method is to extract the earliest date and the longitude

### 2015-10-06 paper.tex
Use pdf for facts-topic-mapping file
Converts Wikidata-statement image to PDF

@@
 \centering
-\includegraphics[width=8.45 cm]{img/Wikidata-statement.png}
-\caption{\todo{Get PDF version} An example of Wikidata statement (from
+\includegraphics[width=8.45 cm]{img/Wikidata_statement.pdf}
+\caption{An example of Wikidata statement (from
 	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
@@
 \centering
-\includegraphics[width=8.45 cm]{img/facts-topics-mapping.png}
+\includegraphics[width=8.45 cm]{img/facts-topics-mapping.pdf}
 \caption{Number of mapped and not mapped topics with more than x facts.

### 2015-10-07 paper.tex
Converts freebase-cvt-obama to PDF
Reworked Section 3.1.

@@
 \centering
-\includegraphics[width=8.45 cm]{img/freebase-cvt-obama.png}
-\caption{\todo{Crop, get PDF version} Example of CVT: presidency of Barack Obama}
+\includegraphics[trim=0cm 3cm 0cm 5cm, width=8.45 cm]{img/freebase-cvt-obama.pdf}
+\caption{Exemplary Compound Value Type (CVT) in Freebase: Presidency of Barack Obama}
+%The source is https://docs.google.com/document/d/1ELrBtxxs4ghhe7FloTUnhvpD3f7RFczT7UfxahAfjgE/edit
 \label{fig:cvt-obama}
@@
 \includegraphics[width=8.45 cm]{img/Wikidata_statement.pdf}
-\caption{An example of Wikidata statement (from
+\caption{Wikidata nomenclature illustrated with an example (Source:
 	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
@@
 
-Migrating data from Freebase to Wikidata faced a~number of challenges:
+During our ongoing efforts with the migration of Freebase to Wikidata
+we were faced with a~number of technical and non-technical challenges
+that we will outline in the following.
 
@@
 
-The first challenge is regarding the licenses under which the datasets are published.
-Wikidata is published under a~Creative Commons~0 (CC0) license (similar to the public domain),
-while Freebase is under a~Creative Commons By license and contains data
-imported from external projects not owned by Google,
+The first challenge concerns the licenses under which the datasets are published.
+Wikidata is published under a~Creative Commons~0 (CC0~1.0) license
+that effectively puts the data in the public domain,
+whereas Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license
+and contains data imported from external projects not owned by Google,
 like images or descriptions extracted from Wikipedia.
-In a~first step we filtered the Freebase dump from this kind of content
-before being able to have a~dump that Google could relicense under CC0.
-This step reduces the number of republishable Freebase facts by about 42M~facts.
+In a~first step, we filtered the Freebase dump for this kind of content
+before being able to create a~dump that we could relicense under CC0~1.0.
+This step reduced the number of Freebase facts that could be republished by about 42M~facts
+from 3~billion facts in the original corpus.
 
@@
 Note the log scale on both axis.}
+%Data sheet: https://docs.google.com/spreadsheets/d/1jYGVIqAmyouHKjvhM6FbpgTD8bb5tkJy9PEMELkuMwo/edit
 \end{figure}

### 2015-10-07 paper.tex
Reworked Section 3.2.

@@
 
-The second challenge is that the Wikidata community is very interested to have references
-for their statements, sources that Freebase usually did not store except for
-some specific data like populations and unemployment rates.
-For these two specific cases we have just kept the references from Freebase.
-In order to provide the Wikidata community with references for the facts in Freebase
-we have reused data from the Knowledge Vault, another Google project with the aim
-to extract facts from the web (see~\cite{dong2014knowledge}).
+The second challenge is that the Wikidata community is very eager to have references
+for their statements, \emph{i.e.}, sources that Freebase usually did not store,
+except for some specific data like populations and unemployment rates.
+For these two specific cases, we have just kept the references from Freebase.
+In order to provide the Wikidata community with references for the facts in Freebase,
+we have reused data from another Google research project
+called Knowledge Vault~\cite{dong2014knowledge} aimed at extracting facts from the Web.
 Whereas the fact extraction was usually correct, the pages Knowledge Vault extracted
-the references from often do not meet the requirement for a~good reference:
-they include pages in social networks, shopping sites, filesharers, \emph{etc.}
-It became necessary to filter and curate the references before inclusion in Wikidata.
+the references from often do not meet the Wikidata requirements for reliable references:
+they include pages in social networks, shopping sites, file sharing hosters, \emph{etc.}
+It became necessary to filter the references before potential inclusion in Wikidata
+by introducing a~domain blacklist.%
+\footnote{URL blacklist:
+\url{https://www.wikidata.org/wiki/Wikidata:Primary_sources_tool/URL_blacklist}}
 

### 2015-10-08 paper.tex
Reworked Section 3.3.

@@
 
-The quality of the data in Freebase was challenged by the Wikidata community.
-For example, a~small city in France had an ISO country code%
-\footnote{See \url{http://www.freebase.com/m/03cc0d0}}.
-Another example, Boston (the city in Massachusetts) has the type \texttt{/people/person}.
-A fully automatic upload of all the content from Freebase into Wikidata
-did not seem advisable as the expectations of the community regarding
-the quality of the content automatically added to Wikidata are high (and rightly so).
-Also, whereas an upload of all the data might have lead to accelerated growth
-in the short term, such a~fast upload might also endanger the sense of ownership
-the Wikidata community has for its data.
-Instead we decided to rely on human curation and created Primary Sources,
-a simple tool which displays statements to the user that may be added to the currently shown item.
-The user can, with only one click, reject the statement or approve it and save it to Wikidata.
-It is currently available as a~gadget, an opt-in option in Wikidata.
-This tool has no dependencies on Freebase and may be easily reused by other projects
-which may want to import data into Wikidata.
-For that we have implemented an upload API and a~feature that allows users
-to display only statements from a~given dataset.
-In fact, during the project one other researcher approached us in order to upload
-a dataset extracted from natural language text.
-A statistics dashboard has also been created in order to monitor the curation work
-\url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}
-and the source code of the tool is available on GitHub:
-\url{https://github.com/google/primarysources}.
+The data quality of Freebase was examined thoroughly by the Wikidata community
+and anecdotal evidence indeed confirmed that there were certain challenges.
+For example, a~small city in France was assigned an ISO country code,%
+\footnote{See \url{http://www.freebase.com/m/03cc0d0}}
+then Boston (the city in Massachusetts) had the type \texttt{/people/person},
+and several other occurrences of data quality issues were revealed.
+In consequence, a~fully automatic upload of all the contents from Freebase into Wikidata
+did not seem advisable as the expectations of the Wikidata community regarding the
+quality of automatically uploaded data are high (and rightly so).
+Despite the fact that an automated upload of all the data
+would have led to accelerated growth in the short term,
+such a~fast increase of available data would certainly have endangered
+the sense of ownership of the Wikidata community for its data.
+As an alternative approach, we decided to rely on crowdsourced human curation
+and created the \emph{Primary Sources Tool},
+a~software solution that displays Freebase statements
+for verification to the user that can be added to the currently shown Wikidata item.
+The tool will be described in more detail in \autoref{sec:primary-sources-tool},
+we provide a~short summary of its functionality here.
+\autoref{fig:primary-sources-tool} shows a~screenshot of the user interface
+of the tool that integrates nicely into the Wikidata user interface.
+The user can, with just one click, reject or approve a~statement,
+and, in case of approval, therewith add the statement to Wikidata.
+The Primary Sources Tool is currently available as a~so-called gadget,
+\emph{i.e.}, as an opt-in feature in Wikidata.
+This tool has no dependencies on Freebase and can be easily reused for other projects
+that want to import datasets into Wikidata.
+Therefore, we have implemented an upload API in the back-end
+and a~filter in the front-end that allows users to display only statements from a~given dataset.
+This flexibility is much-wanted, and during the development period of the project
+another researcher approached us in order to upload a~dataset extracted from natural language text.
+To visualize the migration progress, we have created a~realtime dashboard
+available at \url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}.
+The code of the Primary Sources Tool is openly available
+(\url{https://github.com/google/primarysources}) under the terms of the Apache~2.0 license.
+At the time of writing (October, 2015), the tool has been used by more than hundred users
+who performed about 30,000 approval or rejection actions.
+More than 12M~statements have been uploaded in total.
 
@@
 \includegraphics[width=8.45 cm]{img/primary-sources.png}
-\caption{Primary Sources user interface}
+\caption{Primary Sources Tool user interface}
+\label{fig:primary-sources-tool}
 \end{figure}
-
-Currently (August~18, 2015) the tool has been used by more than a~hundred users
-who have performed more than 15,000 approve or reject actions.
-More than 12M~statements are uploaded to the tool.
 

### 2015-10-08 paper.tex
Reworked Section 3.4.1.

@@
 For example, a~small city in France was assigned an ISO country code,%
-\footnote{See \url{http://www.freebase.com/m/03cc0d0}}
+\footnote{Freebase item page of the city of Saint-Martin: \url{http://www.freebase.com/m/03cc0d0}}
 then Boston (the city in Massachusetts) had the type \texttt{/people/person},
@@
 for verification to the user that can be added to the currently shown Wikidata item.
-The tool will be described in more detail in \autoref{sec:primary-sources-tool},
-we provide a~short summary of its functionality here.
-\autoref{fig:primary-sources-tool} shows a~screenshot of the user interface
-of the tool that integrates nicely into the Wikidata user interface.
-The user can, with just one click, reject or approve a~statement,
-and, in case of approval, therewith add the statement to Wikidata.
-The Primary Sources Tool is currently available as a~so-called gadget,
-\emph{i.e.}, as an opt-in feature in Wikidata.
-This tool has no dependencies on Freebase and can be easily reused for other projects
-that want to import datasets into Wikidata.
-Therefore, we have implemented an upload API in the back-end
-and a~filter in the front-end that allows users to display only statements from a~given dataset.
-This flexibility is much-wanted, and during the development period of the project
-another researcher approached us in order to upload a~dataset extracted from natural language text.
-To visualize the migration progress, we have created a~realtime dashboard
-available at \url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}.
-The code of the Primary Sources Tool is openly available
-(\url{https://github.com/google/primarysources}) under the terms of the Apache~2.0 license.
-At the time of writing (October, 2015), the tool has been used by more than hundred users
-who performed about 30,000 approval or rejection actions.
-More than 12M~statements have been uploaded in total.
+The tool will be described in more detail in \autoref{sec:primary-sources-tool}.
 
-\begin{figure}[!htbp]
-\centering
-\includegraphics[width=8.45 cm]{img/primary-sources.png}
-\caption{Primary Sources Tool user interface}
-\label{fig:primary-sources-tool}
-\end{figure}
-
-\subsection{Mappings}
+\subsection{Data Mappings}
 
@@
 
-Another challenge is to get a~good mapping between Freebase topics and properties
+The last challenge concerns the data mappings between Freebase topics and properties
 and Wikidata items and properties.
 Two mappings between Freebase topics and Wikidata items were initially available,
-and we worked on further mappings.
-A first one has been created by Google in October 2013%
-\footnote{Freebase mappings \url{http://developers.google.com/freebase/data}}
+and in addition to those, we worked on further mappings.
+A~first one has been created by Google in October 2013%
+\footnote{Freebase mappings: \url{http://developers.google.com/freebase/data}}
 and is based on Wikipedia links already present in Freebase: if a~Freebase topic and
-a Wikidata items share at least two Wikipedia links, then they are about the same subject.
-The quality of this mapping is considered as very good by the Wikidata community
-who have uploaded it to the wiki and further curated and maintained it by hand.
-It maps 1.15M~of Freebase topic.
-A second mapping has been created by Samsung, and is actively maintained%
-\footnote{Samsung mappings \url{http://github.com/Samsung/KnowledgeSharingPlatform}.}.
-It is based on the same idea but matches a~Freebase topic with a~Wikidata item
-even if there is only a~single Wikipedia link shared.
-The quality of the mapping is lower (there are some wrong matches,
-often because there is no clear separation between topics and disambiguation pages in Wikipedia)
-but it provides 4.4M~links.
-As we have seen before, our quality target is not very high,
-so we have chosen to merge the two dumps and, for the 6,000 conflicts,
-to prioritize the mapping given by Wikidata.
-To improve the resulting mapping we have also tried to do some reconciliation
-based on external database IDs shared by Freebase and Wikidata, like MusicBrainz, VIAF, \emph{etc.}
-With this technique we were able to match 0.8M~IDs,
-creating a~mapping for 0.6M~topics---most of them already in our dataset.
-This resulted in an additional 84,000 items mapped.
-We also used data from Google's Knowledge Graph to add 0.1M~further mappings
-matching also a~topic and an item if they share a~Wikipedia link.
-We could maybe add some more data by looking at functional relations like ``father'' and ``mother''.
-But these relations only apply to relatively small sets of data (like well known families)
-and the functional assumption may run into some edge cases.
-For example, the \texttt{/people/person/parents} property in Freebase also covers also stepparents,
-creating cases where a~person has more than one male or female \texttt{/people/person/parents}.
-Eventually, with these four sources we mapped 4.56M~items.
-We believe that by doing so we have mapped most of the topics that could be automatically mapped
-as suggested by the small increases added by the ID reconciliation approach
+a~Wikidata item share at least two Wikipedia links, they are assumed to describe the same subject.
+The quality of this mapping is considered very good by the Wikidata community,
+who thus have uploaded it to the Wiki and further curated and maintained it by hand.
+It maps 1.15M~Freebase topics to their corresponding Wikidata items.
+A~second actively maintained mapping has been created by Samsung.%
+\footnote{Samsung mappings: \url{http://github.com/Samsung/KnowledgeSharingPlatform}}
+It is based on the same idea, but matches a~Freebase topic with a~Wikidata item
+even if there is only a~single shared Wikipedia link.
+The precision of the mapping is naturally lower compared to Google's mapping,
+as there are more wrong matches (often because there is no clear separation between topics
+and disambiguation pages in Wikipedia), however, the recall increases to 4.4M~links.
+As we have seen before \todo{Where?}, our quality target is not very high \todo{We should never write this},
+so we have chosen to merge the two dumps \todo{The mappings dumps I suppose?} and, for the resulting 6,000 conflicts,
+decided to prioritize the mapping given by Wikidata \todo{That is, Google's?}.
+To improve the resulting mapping, we have also tried to do some reconciliation
+based on external database IDs shared by Freebase and Wikidata, like MusicBrainz \todo{Citation needed}, VIAF \todo{Citation needed}, \emph{etc.}
+With this technique, we were able to match 800K~IDs \todo{IDs? Is that MusicBrainz or VIAF IDs?},
+creating a~mapping for 600K~topics---most of them already in our dataset \todo{Which dataset?}.
+This resulted in an additional 84K items mapped.
+We also used data \todo{What data exactly?} from Google's Knowledge Graph \todo{Citation desirable} to add 100K~further mappings
+by also matching a~topic and an item if they share a~Wikipedia link \todo{Wasn't it leveraging the Knowledge Graph?}.
+There is some potential to add some more data by looking at functional relations
+like ``father'' and ``mother'', but these relations only apply to relatively small sets of data
+(like well known families) and the functional assumptions may run into some edge cases.
+For example, the \texttt{/people/person/parents} property in Freebase also covers stepparents,
+which may create cases where a~person has more than one male or female \texttt{/people/person/parents}.
+Eventually, with these four sources \todo{Google, Samsung, MusicBrainz, VIAF, Knowledge Graph. 5 Sources?}, we mapped 4.56M~items.
+To the best of our knowledge, therewith we have already mapped
+most of the topics that could be mapped automatically, 
+which is also backed by the comparably small increases gained from the ID reconciliation approach \todo{Referring to MusicBrainz and VIAF?}
 and the Knowledge Graph data.
 Furthermore, the mapped topics have an average number of facts of about~13.9,
-whereas the topics that were not mapped have an average of 5.7~facts.
+whereas the topics that were not mapped have an average number of 5.7~facts.
 We have mapped the majority of topics with more than 80~facts.
-This allows us to conclude that we have mapped the most important items of Freebase.
+This allows us to conclude that we have mapped the most important items of Freebase \todo{Easy "reviewer 2" question: why 80?}.
 
@@
 \caption{Number of mapped and not mapped topics with more than x facts.
-Note the log scale on both axis.}
+Note the log scale on both axes.}
 %Data sheet: https://docs.google.com/spreadsheets/d/1jYGVIqAmyouHKjvhM6FbpgTD8bb5tkJy9PEMELkuMwo/edit
@@
 \section{Primary Sources Tool}\label{sec:primary-sources-tool}
+
+As outlined earlier, the \emph{Primary Sources Tool} is a~crowdsourced human curation
+software solution that displays Freebase statements
+for verification to the user that can be added to the currently shown Wikidata item.
+The user can, with just one click, reject or approve a~statement,
+and, in case of approval, therewith add the statement to Wikidata.
+The Primary Sources Tool is currently available as a~so-called gadget,
+\emph{i.e.}, as an opt-in feature in Wikidata.
+This tool has no dependencies on Freebase and can be easily reused for other projects
+that want to import datasets into Wikidata.
+Therefore, we have implemented an upload API in the back-end
+and a~filter in the front-end that allows users to display only statements from a~given dataset.
+This flexibility is much-wanted, and during the development period of the project
+another researcher approached us in order to upload a~dataset extracted from natural language text.
+To visualize the migration progress, we have created a~realtime dashboard
+available at \url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}.
+The code of the Primary Sources Tool is openly available
+(\url{https://github.com/google/primarysources}) under the terms of the Apache~2.0 license.
+At the time of writing (October, 2015), the tool has been used by more than hundred users
+who performed about 30,000 approval or rejection actions.
+More than 12M~statements have been uploaded in total.
+\autoref{fig:primary-sources-tool} shows a~screenshot of the user interface
+of the tool that integrates nicely into the Wikidata user interface.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=8.45 cm]{img/primary-sources.png}
+\caption{Primary Sources Tool user interface}
+\label{fig:primary-sources-tool}
+\end{figure}
 

### 2015-10-09 paper.tex
Fix some TODOs and reply of other
I am not sure if I have really addressed your TODOs

@@
 
-Wikidata\footnote{Wikidata: \url{https://www.wikidata.org/wiki/Wikidata:Main_Page}}
+Wikidata\footnote{Wikidata: \url{https://www.wikidata.org}}
 is a~collaborative knowledge base
@@
 \subsection{Data Quality}
+\label{sec-dataquality}
 
@@
 and disambiguation pages in Wikipedia), however, the recall increases to 4.4M~links.
-As we have seen before \todo{Where?}, our quality target is not very high \todo{We should never write this},
-so we have chosen to merge the two dumps \todo{The mappings dumps I suppose?} and, for the resulting 6,000 conflicts,
-decided to prioritize the mapping given by Wikidata \todo{That is, Google's?}.
+As we have seen in section \autoref{sec-dataquality} the mapped data will be human curated before the importation,
+so we have chosen to merge the two mapping dumps and, for the resulting 6,000 conflicts,
+decided to prioritize the Google's mapping.
 To improve the resulting mapping, we have also tried to do some reconciliation
-based on external database IDs shared by Freebase and Wikidata, like MusicBrainz \todo{Citation needed}, VIAF \todo{Citation needed}, \emph{etc.}
-With this technique, we were able to match 800K~IDs \todo{IDs? Is that MusicBrainz or VIAF IDs?},
-creating a~mapping for 600K~topics---most of them already in our dataset \todo{Which dataset?}.
+based on external databases IDs shared by Freebase and Wikidata, like
+MusicBrainz,\footnote{MusicBrainz: \url{https://musicbrainz.org}}
+VIAF,\footnote{VIAF: \url{http://viaf.org}} \emph{etc.}
+With this technique, we were able to match 800K~external database IDs \todo{not sure if it's understandable},
+creating a~mapping for 600K~topics---most of them already in the merge of Google's and Samsung's mappings.
 This resulted in an additional 84K items mapped.
-We also used data \todo{What data exactly?} from Google's Knowledge Graph \todo{Citation desirable} to add 100K~further mappings
-by also matching a~topic and an item if they share a~Wikipedia link \todo{Wasn't it leveraging the Knowledge Graph?}.
+We also used Google's Knowledge Graph\footnote{Google Knowledge Graph introduction blog post: \url{https://googleblog.blogspot.com/2012/05/introducing-knowledge-graph-things-not.html} \todo{Better reference?}} to add 100K~further mappings
+by also matching a~topic and an item if they share a~Wikipedia link \todo{Wasn't it leveraging the Knowledge Graph?
+-- Yes, but not sure how to rewrite this section.
+I have added a reference to the introduction article.
+We should maybe have Denny's input about it}.
 There is some potential to add some more data by looking at functional relations
@@
 which may create cases where a~person has more than one male or female \texttt{/people/person/parents}.
-Eventually, with these four sources \todo{Google, Samsung, MusicBrainz, VIAF, Knowledge Graph. 5 Sources?}, we mapped 4.56M~items.
+Eventually, with these four sources \todo{Google, Samsung, MusicBrainz, VIAF, Knowledge Graph. 5 Sources? -- Google, Samsung, external IDs, Knowledge Graph}, we mapped 4.56M~items.
 To the best of our knowledge, therewith we have already mapped
 most of the topics that could be mapped automatically, 
-which is also backed by the comparably small increases gained from the ID reconciliation approach \todo{Referring to MusicBrainz and VIAF?}
+which is also backed by the comparably small increases gained from the ID reconciliation approach \todo{Referring to MusicBrainz and VIAF? -- yes}
 and the Knowledge Graph data.
@@
 whereas the topics that were not mapped have an average number of 5.7~facts.
-We have mapped the majority of topics with more than 80~facts.
-This allows us to conclude that we have mapped the most important items of Freebase \todo{Easy "reviewer 2" question: why 80?}.
+We have mapped the majority of topics with more than 47~facts (191K~non mapped topics \textit{vs.} 195K~mapped).
+This allows us to conclude that we have mapped the most important items of Freebase.
 

### 2015-10-10 paper.tex
Reworked Subsection 3.4, 3.5, and Abstract.

@@
 as structured data are central to many companies' data strategies.
-One example of such collaborative knowledge bases is Freebase (\url{www.freebase.com}),
-created with proprietary technologies in 2007 by a~company called Metaweb,
+One such collaborative knowledge base is Freebase (\url{www.freebase.com}),
+initially created with proprietary technologies by a~company called Metaweb,
 which was then acquired by Google in 2010.
@@
 and operated by the Wikimedia Foundation.
-Due to the success of Wikidata, Google decided to shut down Freebase and
-help with the transfer of its content to Wikidata through a~crowdsourcing approach.
-In this paper, we describe the ongoing transfer efforts and challenges,
+Due to the success of Wikidata, in~2015, Google decided to shut down Freebase and
+help the community with the transfer of its content to Wikidata through a~crowdsourcing approach.
+In this paper, we describe the ongoing transfer efforts and data mapping challenges,
 and provide an analysis of the process so far.
+For the task, we have created a~software solution called \emph{Primary Sources Tool}
+that we have released as open source to facilitate this and future data migrations.
+Throughout the migration, we have gained deep insights into both Wikidata and Freebase,
+and share and discuss detailed statistics on both knowledge bases. 
 \end{abstract}
@@
 Due to the success of Wikidata,
-it was decided to close Freebase and support the migration of its contents to Wikidata.
+it was decided to close Freebase and support the migration of its content to Wikidata.
 Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
@@
 
-The contents of Freebase have been imported from various sources like Wikipedia
+The content of Freebase has been imported from various sources like Wikipedia
 or the Internet Movie Database IMDB,
-in consequence Google does not own the copyright of some parts of the contents of the knowledge base
+in consequence Google does not own the copyright of some parts of the content of the knowledge base
 like images or long entity descriptions extracted from Wikipedia.
@@
 
-Wikidata contents rely on the notions of \emph{item} and \emph{statement}.
+Wikidata's data model relies on the notions of \emph{item} and \emph{statement}.
 An item represent a~concept, has a~stable identifier and may have some labels,
@@
 
-The contents of Wikidata are freely available under a~Creative Commons~0 (CC0) license.
+The content of Wikidata is freely available under a~Creative Commons~0 (CC0) license.
 As of mid 2015, Wikidata counted about 66M~statements on 14M~entities.
@@
 \subsection{Licensing}
-\label{sec-licensing}
+\label{sec:licensing}
 
@@
 \subsection{Data Quality}
-\label{sec-dataquality}
+\label{sec:dataquality}
 
@@
 and several other occurrences of data quality issues were revealed.
-In consequence, a~fully automatic upload of all the contents from Freebase into Wikidata
+In consequence, a~fully automatic upload of all the content from Freebase into Wikidata
 did not seem advisable as the expectations of the Wikidata community regarding the
@@
 
-\subsection{Data Mappings}
+\subsection{Data Topic Mappings}
 
-\subsubsection{Mappings of Items}
+\subsubsection{Merger of Existing Mappings}
 
@@
 The quality of this mapping is considered very good by the Wikidata community,
-who thus have uploaded it to the Wiki and further curated and maintained it by hand.
+who thus have decided to use it and further curate and maintain it by hand.
 It maps 1.15M~Freebase topics to their corresponding Wikidata items.
@@
 and disambiguation pages in Wikipedia), however, the recall increases to 4.4M~links.
-As we have seen in section \autoref{sec-dataquality} the mapped data will be human curated before the importation,
-so we have chosen to merge the two mapping dumps and, for the resulting 6,000 conflicts,
-decided to prioritize the Google's mapping.
-To improve the resulting mapping, we have also tried to do some reconciliation
-based on external databases IDs shared by Freebase and Wikidata, like
-MusicBrainz,\footnote{MusicBrainz: \url{https://musicbrainz.org}}
+As we have shown in \autoref{sec:dataquality},
+that human curation is required before importation anyway,
+which is why we have decided to merge the two mapping dumps,
+and for the resulting 6,000 conflicts decided to prioritize Google's mapping.
+
+\subsubsection{Reconciliation Based on External Database IDs}
+
+To improve the result, we have also done some reconciliation based on third-party database IDs
+shared by Freebase and Wikidata, like MusicBrainz,\footnote{MusicBrainz: \url{https://musicbrainz.org}}
 VIAF,\footnote{VIAF: \url{http://viaf.org}} \emph{etc.}
-With this technique, we were able to match 800K~external database IDs \todo{not sure if it's understandable},
-creating a~mapping for 600K~topics---most of them already in the merge of Google's and Samsung's mappings.
-This resulted in an additional 84K items mapped.
-We also used Google's Knowledge Graph\footnote{Google Knowledge Graph introduction blog post: \url{https://googleblog.blogspot.com/2012/05/introducing-knowledge-graph-things-not.html} \todo{Better reference?}} to add 100K~further mappings
-by also matching a~topic and an item if they share a~Wikipedia link \todo{Wasn't it leveraging the Knowledge Graph?
--- Yes, but not sure how to rewrite this section.
-I have added a reference to the introduction article.
-We should maybe have Denny's input about it}.
-There is some potential to add some more data by looking at functional relations
+With this technique, we were able to match 800K~external database IDs,
+creating an additional mapping for 600K~topics---%
+most of them already in the merged version of Google's and Samsung's mappings.
+Eventually, this reconciliation effort resulted in an additional 84K mapped items.
+We also used Google's Knowledge Graph~\cite{singhal2012} to add 100K~further mappings
+by also matching a~topic and an item if they share a~Wikipedia link with the Knowledge Graph item.
+There is some potential to add more data by looking at functional relations
 like ``father'' and ``mother'', but these relations only apply to relatively small sets of data
-(like well known families) and the functional assumptions may run into some edge cases.
+(like well known families), and the functional assumptions may run into some edge cases.
 For example, the \texttt{/people/person/parents} property in Freebase also covers stepparents,
 which may create cases where a~person has more than one male or female \texttt{/people/person/parents}.
-Eventually, with these four sources \todo{Google, Samsung, MusicBrainz, VIAF, Knowledge Graph. 5 Sources? -- Google, Samsung, external IDs, Knowledge Graph}, we mapped 4.56M~items.
-To the best of our knowledge, therewith we have already mapped
-most of the topics that could be mapped automatically, 
-which is also backed by the comparably small increases gained from the ID reconciliation approach \todo{Referring to MusicBrainz and VIAF? -- yes}
-and the Knowledge Graph data.
-Furthermore, the mapped topics have an average number of facts of about~13.9,
-whereas the topics that were not mapped have an average number of 5.7~facts.
-We have mapped the majority of topics with more than 47~facts (191K~non mapped topics \textit{vs.} 195K~mapped).
+Eventually, with these four sources (Google mapping, Samsung mapping, external IDs, Knowledge Graph),
+we mapped 4.56M~items in total.
+
+\subsubsection{Mapping Completeness Analysis}
+
+Thanks to these efforts, we have already mapped most of the topics that could be mapped automatically,
+which is also backed by the comparably small increases gained from the ID reconciliation approach 
+and the Knowledge Graph data described in the previous paragraph.
+Furthermore, the \emph{mapped} topics have an average number of facts of about~13.9,
+whereas the topics that were \emph{not} mapped have an average number of only 5.7~facts.
+We have mapped the majority of topics with more than 47~facts
+(191K~non mapped topics \textit{vs.} 195K~mapped topics).
 This allows us to conclude that we have mapped the most important items of Freebase.
@@
 \includegraphics[width=8.45 cm]{img/facts-topics-mapping.pdf}
-\caption{Number of mapped and not mapped topics with more than x facts.
-Note the log scale on both axes.}
+\caption{Number of mapped and not mapped topics with more than $x$ facts (log scale on both axes)}
 %Data sheet: https://docs.google.com/spreadsheets/d/1jYGVIqAmyouHKjvhM6FbpgTD8bb5tkJy9PEMELkuMwo/edit
@@
 
-\subsubsection{Mapping of Properties}
+\subsection{Data Property Mapping}
 
@@
 with the help of the Wikidata community.
-With that we have been able to map quickly around 360~properties
+With that, we have been able to quickly map around 360~properties
 (note that Wikidata has a~total of 1,660 properties, and Freebase has around 37,700 properties).
-For the mapping of properties where the domain are other topics or literals
+For the mapping of properties where the domain are other topics or literals,
 this mapping provides the Wikidata property to use.
@@
 based on the person gender.
-The mapping of CVTs is more complicated because it is not possible to have a~1~to~1 relationship
+The mapping of CVTs (see \autoref{fig:cvt-obama}) is more complicated,
+because it is not possible to have a~\mbox{1-to-1} relationship
 between Freebase and Wikidata properties: the CVT is linked to the subject topic by one property
@@
 In order to map a~CVT to a~statement, we have to know which of the CVT's properties
-should be used as the main value of the statement, with the others being mapping to qualifiers.
-In order to keep a~simple mapping associating one Wikidata property to one Freebase property,
-we map both the property linking the topic to the CVT
+should be used as the main value of the statement, with the others being mapped to qualifiers.
+In order to keep a~simple mapping that associates one Wikidata property to one Freebase property,
+we map both the property that links the topic to the CVT
 and the main property of the CVT to the same Wikidata property, and, during the mapping process,
-we pick the later as the main property of the CVT.
-For example, if we try to map the same CVT as \autoref{fig:cvt-obama}
-we will use the Wikidata property ``position held (P39)'' to map
+pick the latter as the main property of the CVT.
+For example, if we map the CVT shown in \autoref{fig:cvt-obama},
+we first use the Wikidata property \texttt{position held (P39)} to map
 \texttt{/politician/government\_positions\_held} and
-\texttt{/government\_position\_held/office\_position\_or\_title}, use ``start time (P580)''
-for \texttt{/government\_position\_held/from} and ``end time (P582)'' for
-\texttt{/government\_position\_held/to}.
-With this mapping the created Wikidata statement will be
-like the one presented in \autoref{fig:statement-obama}.
+\texttt{/government\_position\_held/office\_position\_or\_title}.
+Second, for the qualifiers, we use \texttt{start time (P580)}
+for \texttt{/government\_position\_held/from} and \texttt{end time (P582)}
+for \texttt{/government\_position\_held/to}.
+With the resulting property mapping, the created Wikidata statement
+looks like the one presented in \autoref{fig:statement-obama}.
 
@@
 to the source as a~Wikidata reference instead of a~qualifier.
-The last challenge is to do the real mapping, taking care of CVTs
-and the complex datatypes of Wikidata.
+The hardest part then is to actually create the full topic mapping
+by considering CVTs and the complex datatypes of Wikidata.
 For CVTs, when we have a~triple whose value is a~CVT, we just retrieve it,
-map all its component triples (while ignoring ones that can't be mapped)
+map all its component triples (while ignoring ones that cannot be mapped)
 and apply the above mechanism to get its main value.
@@
 in order to cast values to the right type.
-For quantities we assume that the amounts are precise
+For quantities, we assume that the amounts are precise,
 as there is no precision information in Freebase.
-For globe coordinates we have hardcoded the mapping of the \texttt{/location/geocode} CVT
-into the globe-coordinate value type of Wikibase
-and use the same precision guess algorithm as the one used by Wikidata user interface.
-For dates we just map the date and time values (encoded using XSD%
+For globe coordinates, we have hardcoded the mapping of the \texttt{/location/geocode} CVT
+into the globe-coordinate value type of Wikidata
+and use the same precision guessing algorithm as the one used by the Wikidata user interface.
+For dates, we just map the date and time values (encoded using XSD%
 \footnote{\url{ http://www.w3.org/TR/xmlschema11-2/}} types)
-to the Wikidata ``time'' datatype but we filterout dates before 1920 that have
-a higher precision than year because we do not know
-if there are in Julian or Gregorian calendar and so,
-we are not able to fill the ``calendar'' metadata of the Wikidata ``time'' datatype.
+to the Wikidata ``time'' datatype, however, filter out dates before 1920 that have
+a~higher precision than year because we do not know
+if they are relative to the Julian or the Gregorian calendar.
+In such cases, we are not able to fill the ``calendar'' value of the Wikidata ``time'' datatype.
 
@@
       \texttt{/common/topic/description}...) and triples that should be filtered
-      for legal reasons (see \autoref{sec-licensing}).}
+      for legal reasons (see \autoref{sec:licensing}).}
   \item 68M~labels

### 2015-10-13 paper.tex
Removes an outdated sentence
Wikidata now supports quantities with units
Beggining of 4.1

@@
 
-\todo{Denny: write me}
+In order to prepare the data for the integration into the Primary Sources Tool, we have created a set of scripts which map the content of the last Freebase dump into Wikidata statements.\footnote{The source code is available under the terms of the Apache~2.0 license here: \url{https://github.com/google/freebase-wikidata-converter}}.
+
+Primary Sources has been developed at the same time as the mapping tool: we have first created a small dataset of around 1M statements based on a few properties (\texttt{/people/person/birth\_place}...) and deployed both the first dataset and a basic version of the tool in order to get user feedbacks.
+Then, we progressively had more statement to the tool database and made the opt-in process to use the tool inside of Wikidata easier, from a line to copy and paste in a user page to an option in user preference.
+So, we were able to both increase slowly the number of users of the tool and the size of the tool database.
+
+The process of adding data by small batches of 1 or 2M each time allowed us to detect some performances issues in the tool and to fix them before they became too important.
+And other good effect is it allowed us to have quick feedbacks from the community about the already mapped data and, so, to adapt easily the mapping scripts and to fix quickly the data already in the tool.
+
+\todo{Thomas: Proofread and expand}
 
@@
 
-\todo{Sebastian: write me}
+\todo{Sebastian or Thomas: write me}
 
@@
 (\emph{i.e.}, 92\%) are converted into Wikidata statements.
-And we would get another 1\% if we would be able
-to map the properties \texttt{/people/person/weight\_kg}
-and \texttt{/people/person/height\_meters} that Wikidata are not supporting yet.
 58\% of the statements created from reviewed fact are already in Wikidata,

### 2015-10-13 paper.tex
Reworked Sections 4.0 and 4.1.

--- 2015-10-10 paper.tex
@@
 As outlined earlier, the \emph{Primary Sources Tool} is a~crowdsourced human curation
-software solution that displays Freebase statements
-for verification to the user that can be added to the currently shown Wikidata item.
-The user can, with just one click, reject or approve a~statement,
+software solution that displays Freebase statements for verification to the user
+so that these statements can be added to the currently shown Wikidata item.
+With just one click, the user can reject or approve a~statement,
 and, in case of approval, therewith add the statement to Wikidata.
-The Primary Sources Tool is currently available as a~so-called gadget,
-\emph{i.e.}, as an opt-in feature in Wikidata.
-This tool has no dependencies on Freebase and can be easily reused for other projects
-that want to import datasets into Wikidata.
+The code of the Primary Sources Tool is openly available
+under the terms of the Apache~2.0 license (\url{https://github.com/google/primarysources}).
+The tool is deployed as a~so-called gadget,
+\emph{i.e.}, as an easily activatable add-on feature in Wikidata.
+It is independent from Freebase and can easily be reused to import other datasets into Wikidata.
 Therefore, we have implemented an upload API in the back-end
-and a~filter in the front-end that allows users to display only statements from a~given dataset.
-This flexibility is much-wanted, and during the development period of the project
+and a~dataset filter in the front-end that allows users
+to display only statements from a~selected dataset.
+This flexibility is indeed much-wanted, and during the development period of the project
 another researcher approached us in order to upload a~dataset extracted from natural language text.
 To visualize the migration progress, we have created a~realtime dashboard
-available at \url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}.
-The code of the Primary Sources Tool is openly available
-(\url{https://github.com/google/primarysources}) under the terms of the Apache~2.0 license.
-At the time of writing (October, 2015), the tool has been used by more than hundred users
+available publicly at \url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}.
+At the time of writing (October, 2015), the tool has been used by more than a~hundred users
 who performed about 30,000 approval or rejection actions.
@@
 \autoref{fig:primary-sources-tool} shows a~screenshot of the user interface
-of the tool that integrates nicely into the Wikidata user interface.
+of the tool that integrates nicely with the Wikidata user interface.
 
@@
 
-\todo{Denny: write me}
+In order to prepare the data for integration into the Primary Sources Tool,
+we have created a set of scripts which map the content
+of the last Freebase dump to Wikidata statements.%
+\footnote{The source code is available under the terms of the Apache~2.0 license:
+\url{https://github.com/google/freebase-wikidata-converter}}
+The Primary Sources Tool was developed in parallel with the mapping tool.
+We first created a~small dataset of around 1M statements
+based on few select properties (\emph{e.g.}, \texttt{/people/person/birth\_place})
+and deployed both the first dataset and a~basic version of the tool
+in order to gather initial user feedback.
+In the following, we progressively added more statements to the tool's database back-end
+and made the opt-in process to use the tool in Wikidata easier for users.
+Initially, in order to use the tool, users had to manually copy and paste a~line
+in their individual \texttt{common.js} user profiles,
+whereas after the conversion to a~Wikidata gadget,
+the tool could simply be activated via an option in the user preferences.
+Thereby, we were able to both slowly increase the number of users of the tool
+and upscale the tool's database back-end without risking performance bottlenecks.
+The process of adding data in small batches of 1M~to~2M statements per batch allowed us
+to detect some potential performances issues in the tool and fix them
+before they became actual problems.
+Another positive side-effect of this approach was that it allowed us to gather quick feedback
+from the community about the already mapped data and thus to adapt the mapping scripts easily
+and correct minor issues with the data early on already in the back-end.
 

### 2015-10-13 paper.tex
Reworked Sections 5.1 and 5.2.

@@
 \usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{textcomp}
+\usepackage{gensymb}
 % todo macro
@@
 
-Here is an overview of the size of the last dump of Freebase:
+\subsection{Quantitative Comparison}
+
+In order to put the statistics in this section in context,
+in the following we provide an overview of the size of the last dump of Freebase
+from March 2015:
 
@@
   \item 2,997M triples
-  \item 442M facts owned by Google\footnote{These ``facts'' are the Freebase triples
-      after having filterout the data about ids (\texttt{/type/object/id}),
-      types (\texttt{/type/object/type}), labels and descriptions (\texttt{/type/object/name},
-      \texttt{/common/topic/description}...) and triples that should be filtered
-      for legal reasons (see \autoref{sec:licensing}).}
+  \item 442M facts owned by Google%
+    \footnote{These facts are the remaining Freebase triples
+      after filtering out data about IDs (\texttt{/type/object/id}),
+      types (\texttt{/type/object/type}), labels, descriptions (\texttt{/type/object/name},
+      \texttt{/common/topic/description}, \emph{etc.}), and triples that were removed
+      due to their licensing (see \autoref{sec:licensing})}
   \item 68M~labels
@@
 
-To compare, Wikidata contains (as of August 2015):
+As a~direct comparison, below the raw statistics for Wikidata as of August 2015
+that make the differences in pure size between the two knowledge bases quite evident.
 
@@
 
-But why are these numbers so different?
+Why are these numbers so different?
 Regarding the number of topics, Freebase has a~lot of topics about subjects
-that do not match the Wikidata notability criteria%
-\footnote{\url{https://www.wikidata.org/wiki/Wikidata:Notability}}.
-For example, Freebase has 11.3M~musical recordings, 8.3M~music canonical versions,
-2.6M~ISBNs, \emph{etc.}
+that do not match Wikidata's notability criteria.%
+\footnote{Wikidata notability criteria:
+\url{https://www.wikidata.org/wiki/Wikidata:Notability}}
+For example, Freebase holds data about 11.3M~musical recordings,
+8.3M~music canonical versions, 2.6M~ISBNs, \emph{etc.} that are not contained in Wikidata.
 We also cannot compare the number of facts and the number of statements directly,
 even considering the lower number of topics.
-Freebase encodes its knowledge in far many more facts than Wikidata needs statements.
-Properties in Freebase often have a~reverse property used in order to be able
-to traverse the Freebase graph easily in both directions.
-For example the property \texttt{/people/person/place\_of\_birth} will have as reverse
-the property \texttt{/location/location/people\_born\_here} that encodes
-exactly the same semantic information.
-Such reverses sometimes exist in Wikidata (like ``children'' for ``father'' and ``mother'')
+Freebase encodes its knowledge far more redundantly than Wikidata.
+To illustrate this, properties in Freebase often have a~\emph{reverse} property
+that is used in order to be able to traverse the Freebase graph easily in both directions.
+For example, the property \texttt{/people/person/place\_of\_birth} has the corresponding
+reverse property \texttt{/location/location/people\_born\_here}
+that encodes exactly the same semantic information.
+Such reverse properties sometimes exist in Wikidata
+(like \texttt{children} for \texttt{father} and \texttt{mother}),
 but are far less common.
-Another point is that CVTs use a~lot of facts to tell the same thing that
-would be represented by a~single Wikidata statement.
-For example, to encode that Barack Obama is the president of the United States from June~20, 2009,
+Another point is that CVTs use a~lot of facts to convey the exact same information
+that can be represented with a~single Wikidata statement.
+For example, to encode that Barack Obama is the president of the United States as of June~20, 2009,
 Freebase requires more than six facts as shown in \autoref{fig:cvt-obama}.
-If we try to encode Wikidata statements as if they were Freebase facts, \emph{i.e.},
-by removing sources, representing statements with qualifiers using CVTs
-and adding reverse properties it would lead to 110M of facts,
+If we attempted to encode Wikidata statements as if they were Freebase facts, \emph{i.e.},
+by removing sources, representing statements with qualifiers using CVTs,
+and adding reverse properties, this would lead to 110M facts,
 \emph{i.e.}, 167\% of the raw number of statements.
-Sometimes, Freebase contains also duplicate data.
-For example, a~lot of cities in the United States have duplicate CVTs for the population
-where the only change is the encoding of the source
-%\footnote{See, for example, \url{http://www.freebase.com/m/01jr6}.}.
+In a~considerable amount of cases, Freebase also contains duplicate data.
+For example, many cities in the United States have duplicate CVTs for the population,
+where the only change is the encoding of the source.
 
-\begin{figure}[!htbp]
+\subsection{Spatio-Temporal Comparison}
+
+In order to get an idea of the coverage of the two knowledge bases,
+we have further created a~spatio-temporal visualization of Freebase and Wikidata 
+that is shown in \autoref{fig:time-space}.
+The used method is to extract the earliest date and the longitude
+linked to each of the entities of the two knowledge bases
+and propagate them to the connected entities which do not have such data
+using a~decreasing exponential distribution \todo{Please clarify the ``propagate'' part}.
+We see that the two knowledge bases follow the same basic patterns,
+with their coverage mostly concentrated on Europe and North America.
+There are no strong differences between them,
+yet coverage of \mbox{\emph{post}-year-2000} entities seems better in Freebase.
+Our theory is that this is \emph{(i)}~due to the absence of a~lot of musical data in Wikidata
+that in contrast is present in Freebase,
+and \emph{(ii)} due to the US population CVTs in Freebase.
+The big horizontal lines in \autoref{fig:freebase} and more even in \autoref{fig:wikidata}
+can most probably be traced back to places that do not have any linked date,
+and in consequence inherit the foundation date of their country.
+For Wikidata (\autoref{fig:wikidata}), two lines that are definitely caused by this effect
+are the big line over the USA around 1780
+and the one covering Russia around 850.
+One possible conclusion from this visualization could be that Wikidata,
+despite its smaller absolute size, appears to have
+a~nearly as complete coverage of the world as Freebase.
+Nonetheless, it is very challenging to find objective ways to compare the two databases
+and good metrics of success for the migration.
+We certainly note that for knowledge bases the amount of triples is not an adequate measure
+to judge the proportion of additional good data.
+
+\begin{figure*}[!htbp]
     \centering
-\includegraphics[width=8.45 cm]{img/wikidata-time-space.png}
-\caption{Time and spatial distribution of Wikidata items.
-Longitude is in $x$ axis and time, following a~power law ($y' = y^8$), is in $y$ axis}
-\label{fig:time-space-wikidata}
-\end{figure}
-
-\begin{figure}[!htbp]
-\centering
-\includegraphics[width=8.45 cm]{img/freebase-time-space.png}
-\caption{Same figure for Freebase entities}
-\label{fig:time-space-freebase}
-\end{figure}
-
-We have also created a~time-spatial visualization of Freebase and Wikidata in order
-to get an idea of the coverage of the two knowledge bases
-(see \autoref{fig:time-space-wikidata} and \autoref{fig:time-space-freebase}).
-The used method is to extract the earliest date and the longitude
-linked to each knowledge base entities
-and propagate them to the connected entities which do not have such data
-using a~decreasing exponential distribution.
-We see that the two knowledge bases follow the same basic patterns,
-with a~coverage mostly concentrated on Europe and North America,
-and there are no strong differences between them.
-The coverage of the after 2000 entities seems better in Freebase, maybe because of
-the presence of a~lot of musical data missing in Wikidata and of the U.S.
-population CVTs.
-The big horizontal lines seems to be mostly due on places that do not have any linked date
-and so inherit the foundation date of their country.
-For Wikidata, two lines that are caused by this behavior are the big line over the U.S.A around 1780
-and the one covering Russia around 850.
-We could conclude from this visualization that Wikidata, even with its smaller size,
-seems to have a~nearly as good coverage of the world as Freebase.
-To conclude, it is tricky to find good ways to compare the two databases
-and good metrics of success for the migration and we could state that, for a~knowledge base,
-containing far more triples than the other does not mean
-it contains the same proportion of additional good data.
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{img/freebase-time-space.png}
+        \caption{Freebase}
+        \label{fig:freebase}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{img/wikidata-time-space.png}
+        \caption{Wikidata}
+        \label{fig:wikidata}
+    \end{subfigure}
+    \caption{Spatio-temporal distribution of Freebase and Wikidata items,
+      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time from the year 0 to 2015, following a~power law ($y' = y^8$)}
+    \label{fig:time-space}
+\end{figure*}
 

### 2015-10-13 paper.tex
Reworked Section 6.

@@
 This flexibility is indeed much-wanted, and during the development period of the project
-another researcher approached us in order to upload a~dataset extracted from natural language text.
+another researcher approached us in order to upload
+a~dataset extracted from natural language text.
 To visualize the migration progress, we have created a~realtime dashboard
@@
 that can be represented with a~single Wikidata statement.
-For example, to encode that Barack Obama is the president of the United States as of June~20, 2009,
+For example, to encode that Barack Obama is the president
+of the United States as of June~20, 2009,
 Freebase requires more than six facts as shown in \autoref{fig:cvt-obama}.
@@
     \caption{Spatio-temporal distribution of Freebase and Wikidata items,
-      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time from the year 0 to 2015, following a~power law ($y' = y^8$)}
+      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
+      from the year 0 to 2015, following a~power law ($y' = y^8$)}
     \label{fig:time-space}
@@
 
-From the Freebase dump we have been able to create more than 17M~Wikidata claims
-(\emph{i.e.}, statement without references) including 1.5M~IDs.
-For that we have used 31M~facts.
-When we add some references we get 19.6M~statements, and, after removing 1M~of duplicates
-and the ones already in Wikidata, we obtain 14M~new statements.
-So, if all these statements were added to Wikidata,
-it would lead to a~21\% increase of Wikidata statements number.
-But why are these numbers so low compared to the size of Freebase?
-We believe that the main reason is that we have only mapped to Wikidata 4.56M~items, (\emph{i.e.},
-only 9.5\% of Freebase topics), that are the subject of only 64M~facts.
-So, we could not hope to map more than 64M~statements
-assuming that we could map all reverse properties, and we couldn't.
-So, assuming that we do not care about the not mapped topics,
-we have created a~statement for more than 24\% of the facts.
-If we restrict ourselves to the reviewed facts, a~set of 1.6M~facts
-that have been human curated, we have far better results.
-There are 0.58M~facts which subjects are mapped to Wikidata and 0.52M~of them
-(\emph{i.e.}, 92\%) are converted into Wikidata statements.
+From the Freebase dump, we have been able to create more than 17M~Wikidata claims
+(\emph{i.e.}, statements without references), including 1.5M~IDs.
+For that, we have used 31M~Freebase facts.
+With additional references, we obtain 19.6M~statements, and, after removing 1M~duplicates
+and facts already contained in Wikidata, we obtain 14M~new statements.
+Thus, if all these statements were added to Wikidata,
+this would lead to a~21\% increase of the number of statements in Wikidata.
+The question raises why these numbers are so low compared to the size of Freebase.
+We argue that the main reason is that we have only mapped 4.56M~items to Wikidata,
+\emph{i.e.}, only 9.5\% of Freebase's topics in total, which are the subject of only 64M~facts.
+Even under ideal circumstances, we cannot map more than 64M~statements,
+and this is assuming that we could map all reverse properties, which, in fact, we could not.
+So leaving aside the not mapped topics, we have created a~statement for more than 24\% of the facts.
+If we restrict ourselves to reviewed facts---a~set of 1.6M~human curated facts---we have far better results.
+There are 0.58M~facts whose subjects are mapped to Wikidata, and 0.52M~of them
+(\emph{i.e.}, 92\%) are converted to Wikidata statements.
 58\% of the statements created from reviewed fact are already in Wikidata,
@@
 
-We believe that the main way of improvements is to extend the migration to more Freebase topics
+We reckon that the most improvements can be achieved
+by extending the migration to more Freebase topics
 by suggesting Wikidata users to create new Wikidata items.
-A possible way of doing it is to create a~small gamified user interface that would allow users
-to create new Wikidata items for a~suggested topic or to add map them to an existing Wikidata item.
-In order to suggest interesting topics to add to Wikidata
-we could rank the not mapped yet topics per number of incoming links from already mapped topic
-and filter not interesting types like ISBNs.
-Another way of improvement is to upload using a~bot high quality datasets,
-like the reviewed facts or some sets,
-for external ids in order to speed up the integration of Freebase content into Wikidata.
-We have already started to upload the simple reviewed facts about humans
+A~possible way of realizing this is to create a~user interface%
+---possibly leveraging elements of gamification---%
+that would allow users to create new Wikidata items for a~suggested topic
+or to add a~mapping for them to an existing Wikidata item.
+In order to suggest interesting topics to add to Wikidata,
+we could rank the not mapped yet topics per number of incoming links
+from already mapped topics and filter less interesting types like ISBNs.
+Another area for improvement is to upload high quality datasets using a~bot,
+like the reviewed facts or some sets for external IDs,
+in order to speed up the integration of Freebase content into Wikidata.
+We have already started to upload simple reviewed facts about humans
 like birth date, death place or gender using a~bot.
-We have also started to investigate on importing some labels
-that are in Freebase and are missing in Wikidata.
-In the 17.2M~of Freebase labels for mapped topics only 0.9M, \emph{i.e.},
-5\%, are missing in Wikidata.
+We have also begun to import labels that are in Freebase and are absent from Wikidata.
+In the 17.2M~Freebase labels for mapped topics, only 0.9M, \emph{i.e.}, 5\%, are missing in Wikidata.
 
-We have been able in a~fairly short amount of time to provide to the Wikidata community
-more than 14M~of new Wikidata statements using a~new tool
-well integrated into the Wikidata user interface.
+Concluding, in a~fairly short amount of time, we have been able
+to provide to the Wikidata community more than 14M~new Wikidata statements
+using a~novel customizable and generalizable software solution called Primary Sources Tool
+that is well integrated into the Wikidata user interface.
 The effort needed to map two fairly different knowledge bases has also been a~good occasion
-to highlight the difficulty to have good metrics to measure the size
-and, so, the ``value'', of such databases.
-We hope that this project will allow to increase the completeness of Wikidata and,
-helped by the comparison to another database, to improve its quality.
+to highlight the difficulty of having good metrics to measure the size
+and in consequence the ``value'' of such collaborative knowledge bases.
+We envision that this project now with Freebase, and for even more datasets in the future,
+will facilitate to increase the completeness of Wikidata.
 

### 2015-10-14 paper.tex
PDFs for figures. Strict ACM style.
Wrote Section 4.3. Added another screenshot.

@@
-\documentclass{sig-alternate}
+%\documentclass{sig-alternate}
+\documentclass{acm_proc_article-sp}
 
@@
 Thomas Pellissier Tanon,\titlenote{The author was an intern at Google when the majority of the work was done.}\ Denny Vrandečić\\
-   \affaddr{Google, San Francisco, United States of America}\\   
+   \affaddr{Google San Francisco, United States of America}\\   
    \email{\{thomaspt, vrandecic\}@google.com}
@@
 Sebastian Schaffert\\
-   \affaddr{Google, Zurich, Switzerland}\\   
+   \affaddr{Google Zurich, Switzerland}\\   
    \email{schaffert@google.com}
@@
 Thomas Steiner\\
-   \affaddr{Google, Hamburg, Germany}\\   
+   \affaddr{Google Hamburg, Germany}\\   
    \email{tsteiner@google.com}
@@
 \centering
-\includegraphics[width=8.45 cm]{img/wikidata-statement-obama.png}
+\includegraphics[width=1\columnwidth]{img/wikidata-statement-obama.pdf}
 \caption{Target Wikidata statement}
@@
 More than 12M~statements have been uploaded in total.
-\autoref{fig:primary-sources-tool} shows a~screenshot of the user interface
+\autoref{fig:primary-sources-tool} shows two screenshots
 of the tool that integrates nicely with the Wikidata user interface.
@@
     \centering
-\includegraphics[width=8.45 cm]{img/primary-sources.png}
-\caption{Primary Sources Tool user interface}
+    \begin{subfigure}[b]{1.0\columnwidth}
+        \includegraphics[width=\textwidth]{img/primary-sources.pdf}
+        \caption{Incoming references}
+        \label{fig:barack-obama}
+    \end{subfigure}
+    \begin{subfigure}[b]{1.0\columnwidth}
+        \includegraphics[width=\textwidth]{img/wikidata-cause-of-death.pdf}
+        \caption{Incoming claims and references}
+        \label{fig:cause-of-death}
+    \end{subfigure}
+    \caption{Primary Sources Tool user interface, incoming data from Freebase shown in light blue}
     \label{fig:primary-sources-tool}
@@
 in order to gather initial user feedback.
-In the following, we progressively added more statements to the tool's database back-end
-and made the opt-in process to use the tool in Wikidata easier for users.
-Initially, in order to use the tool, users had to manually copy and paste a~line
-in their individual \texttt{common.js} user profiles,
-whereas after the conversion to a~Wikidata gadget,
-the tool could simply be activated via an option in the user preferences.
-Thereby, we were able to both slowly increase the number of users of the tool
-and upscale the tool's database back-end without risking performance bottlenecks.
-The process of adding data in small batches of 1M~to~2M statements per batch allowed us
-to detect some potential performances issues in the tool and fix them
-before they became actual problems.
+In the following, we progressively added more statements to the tool's database back-end.
+Thereby, we were able to slowly upscale the tool's database back-end
+without risking back-end performance bottlenecks.
+The process of adding data in small batches of 1M~to~2M statements per batch
+further allowed us to detect some potential issues in the front-end
+and fix them before they became actual problems.
 Another positive side-effect of this approach was that it allowed us to gather quick feedback
@@
 and correct minor issues with the data early on already in the back-end.
+Upon approval or rejection of either a~claim or a~reference,
+the Wikidata item page in question reloads in order to reflect
+the potentially changed state of the migration, as,
+in case of incoming claims with references, freshly accepted claims 
+can require incoming references to be attached elsewhere in the hierarchy.
 
@@
 
-\todo{Tom: write me}
+For the front-end, our objective was to make the migration process
+as close to the natural Wikidata editing flow as possible.
+Ideally, the user should barely notice the different underlying datasources
+when navigating Wikidata.
+To achieve this, we have in a~first step created a~Wikidata \emph{user script}.
+Wikidata user scripts are part of the Wikidata tool chain%
+\footnote{Wikidata tool chain:
+\url{https://www.wikidata.org/wiki/Wikidata:Tools}}
+and are created by users, but unlike gadgets---to be explained in the following---%
+do not appear in a~user's preferences.
+Instead, one has to add a~line of code into ones \texttt{common.js} file
+in order to activate and use the script.
+User scripts can be created by anyone and might not always be stable.
+Once a~user script has matured, it can be converted into a~\emph{gadget}.
+Gadgets are scripts that are likewise created by users,
+but which can be simply enabled in user preferences under the section ``Gadgets''.
+They can only be edited by administrators and are assumed to be stable.
+With our front-end, we went through this maturation steps
+and started with a~user script called \texttt{freebase2wikidata.js}%
+\footnote{Initial user script:
+\url{https://www.wikidata.org/wiki/User:Tomayac/freebase2wikidata.js}}
+that we later converted into a~gadget.%
+\footnote{Final gadget: \url{https://www.wikidata.org/wiki/MediaWiki:Gadget-PrimarySources.js}}
+\autoref{fig:primary-sources-tool} illustrates the user interface in action.
+Existing Wikidata statements are shown as usual,
+Freebase facts that could potentially be imported into Wikidata are shown in light blue
+with instead of an ``edit'' button two new buttons ``approve reference'' and ``reject reference''
+(\autoref{fig:barack-obama}) or ``approve claim'' and ``reject claim''
+(\autoref{fig:cause-of-death}) respectively.
 
@@
   \item 442M facts owned by Google%
-    \footnote{These facts are the remaining Freebase triples
+    \footnote{That is, the remaining Freebase triples
       after filtering out data about IDs (\texttt{/type/object/id}),
       types (\texttt{/type/object/type}), labels, descriptions (\texttt{/type/object/name},
-      \texttt{/common/topic/description}, \emph{etc.}), and triples that were removed
-      due to their licensing (see \autoref{sec:licensing})}
+      \texttt{/common/topic/description}, \emph{etc.}), and triples removed
+      for licensing (see \autoref{sec:licensing})}
   \item 68M~labels
@@
     \centering
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{1.0\columnwidth}
         \includegraphics[width=\textwidth]{img/freebase-time-space.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{1.0\columnwidth}
         \includegraphics[width=\textwidth]{img/wikidata-time-space.png}
@@
       the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
-      from the year 0 to 2015, following a~power law ($y' = y^8$)}
+      from the year 0 to 2015, following a~power law ($y' = y^8$) \todo{Create PDF versions of both diagrams}}
     \label{fig:time-space}

### 2015-10-14 paper.tex
Beggining of section 4.2

@@
 
-\todo{Sebastian or Thomas: write me}
+For the back-end, our objective was to have a REST API allowing us
+to serve efficiently the front-end of the tool and providing statistical data.
+Each statement has a status allowing to query only statements that have been
+approved, rejected, not reviewed yet, \textit{etc.}
+We keep also an history of all status changes allowing to display a list of the tool top users
+and, so, to give to the Wikidata contributors a more gamified experience.
+
+The storage is done using an SQL database where each statement is fully exploded into atomic parts (property, value, qualifier...) allowing us to do easily queries on the tool data like ``get all the statements with property \texttt{P31}'', and so, to easily fix mapping errors detected by the tool users.
+
+\todo{Review and expand}
 

### 2015-10-14 paper.tex
Precisions on the propagation

--- 2015-10-14 paper.tex
@@
 
-\numberofauthors{3}
+\numberofauthors{5}
 \author{
-Thomas Pellissier Tanon,\titlenote{The author was an intern at Google when the majority of the work was done.}\ Denny Vrandečić\\
-   \affaddr{Google San Francisco, United States of America}\\   
-   \email{\{thomaspt, vrandecic\}@google.com}
+\alignauthor
+Thomas Pellissier Tanon\titlenote{The author was an intern at Google when the majority of the work was done.}
+   \affaddr{Google, San Francisco, USA}\\   
+   \email{thomaspelta@gmail.com}
+\alignauthor
+Denny Vrandečić
+   \affaddr{Google, San Francisco, USA}\\   
+   \email{vrandecic@google.com}
 \alignauthor
 Sebastian Schaffert\\
-   \affaddr{Google Zurich, Switzerland}\\   
+   \affaddr{Google, Zurich, Switzerland}\\   
    \email{schaffert@google.com}
+\and
 \alignauthor
 Thomas Steiner\\
-   \affaddr{Google Hamburg, Germany}\\   
-   \email{tsteiner@google.com}
+   \affaddr{Google, Hamburg, Germany}\\   
+   \email{tomac@google.com}
+\alignauthor
+Lydia Pintscher\\
+   \affaddr{Wikimedia, Berlin, Germany}\\   
+   \email{mail@pintscher.de}
 }
-
 \begin{document}
@@
 \begin{abstract}
-Collaborative knowledge bases that make their data available in machine-readable form
-as structured data are central to many companies' data strategies.
-One such collaborative knowledge base is Freebase (\url{www.freebase.com}),
-initially created with proprietary technologies by a~company called Metaweb,
-which was then acquired by Google in 2010.
-Another example is Wikidata (\url{www.wikidata.org}),
-a~collaborative knowledge base developed in the open since 2012 by Wikimedia Deutschland
-and operated by the Wikimedia Foundation.
-Due to the success of Wikidata, in~2015, Google decided to shut down Freebase and
-help the community with the transfer of its content to Wikidata through a~crowdsourcing approach.
+Collaborative knowledge bases that make their data freely available in a~machine-readable form
+are central for the data strategy of many projects and organizations.
+One such collaborative knowledge base is Freebase, initially launched by Metaweb in 2007,
+who were then acquired by Google in 2010.
+Another example is Wikidata, a~collaborative knowledge base developed by
+Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
+Due to the success of Wikidata, Google decided 2015 to shut down Freebase and
+help the community with the transfer of Freebase's content to Wikidata.
 In this paper, we describe the ongoing transfer efforts and data mapping challenges,
-and provide an analysis of the process so far.
-For the task, we have created a~software solution called \emph{Primary Sources Tool}
-that we have released as open source to facilitate this and future data migrations.
-Throughout the migration, we have gained deep insights into both Wikidata and Freebase,
+and provide an analysis of the effort so far.
+We have created the \emph{Primary Sources Tool}
+that we have released as open source to facilitate the transfer of this dataset,
+but also future data migrations.
+Throughout the migration, we have gained insights into both Wikidata and Freebase,
 and share and discuss detailed statistics on both knowledge bases. 
@@
 is usually a~problematic task and requires the careful mapping between their structures.
-In this paper, we describe how we facilitated the migration of Freebase content to Wikidata.
+In this paper, we describe how we facilitated the migration of
+Freebase\footnote{Freebase: \url{https://www.freebase.com}} content to
+Wikidata.\footnote{Wikidata: \url{https://www.wikidata.org}}
 That migration was no exception to this rule, and had a~number of \emph{structural} challenges.
@@
 
-Freebase\footnote{Freebase: \url{https://www.freebase.com/}} is an open source and
+Freebase is an open source and
 collaborative knowledge base created in 2007 by Metaweb and acquired in 2010 by Google.
@@
 \includegraphics[trim=0cm 3cm 0cm 5cm, width=8.45 cm]{img/freebase-cvt-obama.pdf}
-\caption{Exemplary Compound Value Type (CVT) in Freebase: Presidency of Barack Obama}
+\caption{Exemplary Compound Value Type (CVT) in Freebase: Presidency of Barack Obama.}
 %The source is https://docs.google.com/document/d/1ELrBtxxs4ghhe7FloTUnhvpD3f7RFczT7UfxahAfjgE/edit
@@
 \caption{Wikidata nomenclature illustrated with an example (Source:
-	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
+	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg}).}
 \label{fig:statement}
@@
 This allows us to conclude that we have mapped the most important items of Freebase.
+\autoref{fig:mapped-not-mapped} provides an overview of mapped and non-mapped items
+put in relation to the number of facts per item.
 
@@
   \includegraphics[width=8.45 cm]{img/facts-topics-mapping.pdf}
-\caption{Number of mapped and not mapped topics with more than $x$ facts (log scale on both axes)}
+  \caption{Number of mapped and not mapped topics with more than $x$ facts (log scale on both axes).}
+  \label{fig:mapped-not-mapped}
   %Data sheet: https://docs.google.com/spreadsheets/d/1jYGVIqAmyouHKjvhM6FbpgTD8bb5tkJy9PEMELkuMwo/edit  
@@
 for \texttt{/government\_position\_held/from} and \texttt{end time (P582)}
-for \texttt{/government\_position\_held/to}.
+for\linebreak \texttt{/government\_position\_held/to}.
 With the resulting property mapping, the created Wikidata statement
@@
 \includegraphics[width=1\columnwidth]{img/wikidata-statement-obama.pdf}
-\caption{Target Wikidata statement}
+\caption{Wikidata statement for a~Freebase Compound Value Type (CVT).
+  See \autoref{fig:cvt-obama} for comparison.}
 \label{fig:statement-obama}
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[!t]
     \centering
@@
         \includegraphics[width=\textwidth]{img/primary-sources.pdf}
-        \caption{Incoming references}
+        \caption{Incoming references.}
         \label{fig:barack-obama}
@@
         \includegraphics[width=\textwidth]{img/wikidata-cause-of-death.pdf}
-        \caption{Incoming claims and references}
+        \caption{Incoming claims and references.}
         \label{fig:cause-of-death}
     \end{subfigure}
-    \caption{Primary Sources Tool user interface, incoming data from Freebase shown in light blue}
+    \caption{Primary Sources Tool user interface. Statements coming from
+       Freebase that are not yet available in Wikidata are shown in light blue.
+       Users can approve or reject these statements using the ``approve'' or ``reject'' buttons.}
     \label{fig:primary-sources-tool}
@@
 
-\todo{Sebastian or Thomas: write me}
+The objective of the back-end was to have a~REST API allowing us
+to serve data efficiently to the front-end of the tool and
+providing statistical data about the approvals and rejections done over time.
+As the resources of the Wikimedia foundation are limited,
+the back-end was implemented in highly optimized C++
+and runs as a~FastCGI application in the lighttpd Web server.
+\autoref{fig:architecture} shows the overall architecture of the Primary Sources tool.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\columnwidth]{img/architecture.png}
+    \caption{Primary Sources Tool architecture. The front-end is implemented in
+      JavaScript and sends HTTP requests to the C++ back-end to retrieve and
+      update entities or statements, which are stored in a relational database.
+      \todo{Create PDF version of the diagram, improve consistency of used terms}}
+    \label{fig:architecture}
+\end{figure}
+
+Entities and statements are stored in a relational database (MySQL or SQLite)
+and follow the Wikidata data structure with an additional status field
+to keep track of statements that either already have been approved or rejected,
+or not yet visited.
+Statements can be grouped in ``datasets'' and ``uploads'' to
+distinguish data from different sources.\footnote{At the time of this writing,
+the back-end contained five different datasets.}
+
+The REST API of the back-end supports the following main types of requests:
+
+\begin{itemize}
+  \setlength\itemsep{0em}
+  \item Get an entity (\emph{i.e.}, its statements) by Wikidata QID
+  (\emph{e.g.}, \verb|GET /entities/Q2529789|).
+  \item Get a~random entity with unapproved (or approved or rejected) statements
+  (\verb|/entities/any|).
+  \item Get a~statement by database ID (\verb|GET /statements/1|) or get a~list of
+  random statements (\verb|GET /statements/any|).
+  \item Set a~new state for a~statement \\(\verb|POST /statements/1?state=approved&user=Alice|).
+\end{itemize}
+
+All GET requests support an additional \verb|&state={state}| query parameter to filter by state.
+This allows Wikidata developers to examine statements
+that have already been updated (\emph{e.g.}, ``return 10 random rejected statements'')
+for further analysis.
+The default of this parameter is \verb|unapproved|.
+
+In addition to these main request types, the REST API also provides endpoints
+for importing and deleting datasets, as well as for retrieving the system's status.%
+\footnote{The system's status is also presented in more convenient form at
+\url{http://tools.wmflabs.org/wikidata-primary-sources/status.html}.}
+
+All update activity around statements is logged in an activity log
+for statistical purposes using the Wikidata user name of the user who performed the update.
+Activity information can be displayed in an aggregated leader board form
+(top users, top rejecters, trends, \emph{etc.}) to add aspects of gamification to the migration process.
 
@@
 linked to each of the entities of the two knowledge bases
-and propagate them to the connected entities which do not have such data
-using a~decreasing exponential distribution \todo{Please clarify the ``propagate'' part}.
+and propagate them to the connected entities which do not have such data.
+To implement this propagation we set as value (date or longitude) the average of the values of the entities which distance is less than $10$ with,
+as weighting, $2^{-d}$ with $d$ the distance between the two entities.
 We see that the two knowledge bases follow the same basic patterns,
@@
         \includegraphics[width=\textwidth]{img/freebase-time-space.png}
-        \caption{Freebase}
+        \caption{Spatio-temporal distribution of Freebase.}
         \label{fig:freebase}
@@
         \includegraphics[width=\textwidth]{img/wikidata-time-space.png}
-        \caption{Wikidata}
+        \caption{Spatio-temporal distribution of Wikidata.}
         \label{fig:wikidata}
@@
       the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
-      from the year 0 to 2015, following a~power law ($y' = y^8$) \todo{Create PDF versions of both diagrams}}
+      from the year 0 to 2015, following a~power law ($y' = y^8$). \todo{Create PDF versions of both diagrams}}
     \label{fig:time-space}
@@
 Concluding, in a~fairly short amount of time, we have been able
-to provide to the Wikidata community more than 14M~new Wikidata statements
+to provide to the Wikidata community more than\linebreak 14M~new Wikidata statements
 using a~novel customizable and generalizable software solution called Primary Sources Tool

### 2015-10-14 paper.tex
Rewrote section on backend. Still working on a small architecture diagram.

--- 2015-10-14 paper.tex
@@
     \end{subfigure}
-    \caption{Primary Sources Tool user interface, incoming data from Freebase shown in light blue}
+    \caption{Primary Sources Tool user interface. Statements coming from
+      Freebase and not yet available in Wikidata are shown in light blue. Users
+      can approve or reject these statements using the ``approve''/``reject'' buttons.}
     \label{fig:primary-sources-tool}
@@
 
-\subsection{Back-end of the Tool}
+\subsection{Backend of the Tool}
 
-\todo{Sebastian or Thomas: write me}
+The objective of the backend was to have a REST API allowing us to serve data
+efficiently to the front-end of the tool and providing statistical data about
+the approvals and rejections done over time. As the resources of the Wikimedia
+foundation are limited, the backend has been implemented in C++ and runs as a
+fastcgi application in the lighttpd webserver.
+
+Entities and statements are stored in an SQL database (MySQL or SQLite) and
+follow the Wikidata data structure with an additional status field to keep track
+of statements that have already been approved or rejected, or not yet
+visited. Statements can be grouped in ``datasets'' and ``uploads'' to
+distinguish data from different sources.\footnote{At the time of this writing,
+  the backend contained 5 different datasets}
+
+The REST API of the backend supports the following types of queries:
+\begin{itemize}
+\item Get an entity (i.e. its statements) by Wikidata QID
+  (e.g. \verb|GET /entities/Q2529789|).
+\item Get a random entity with unapproved (or approved, rejected) statements
+  (\verb|/entities/any|).
+\item Get a statement by database ID (\verb|GET /statements/1|) or get a list of
+  random statements (\verb|GET /statements/any|).
+\item Set a new state for a statement \\(\verb|POST /statements/1?state=approved&user=Alice|).
+\end{itemize}
+All GET requests support an additional \Verb|state=...| query parameter to
+filter by state. This allows Wikidata developers to analyse statements that have
+already been updated (e.g. ``return 10 random rejected statements'') for further
+analysis. The default of this parameter is \verb|unapproved|.
+
+In addition to these main request types, the REST API also provides endpoints
+for importing and deleting datasets, as well as for retrieving system
+status.\footnote{The system status is also presented in more convenient form at
+  \url{http://tools.wmflabs.org/wikidata-primary-sources/status.html}}
+
+All update activity around statements is logged in an activity log for
+statistical purposes using the Wikidata user name of the user who performed the
+update. Activity information can be displayed in an aggregated form (top users,
+top rejecters, trends) to give to the Wikidata contributors a more gamified
+experience.
+
+\todo{Review and expand}
 

### 2015-10-14 paper.tex
Fix typo.
Add architecture diagram.

@@
 
-Entities and statements are stored in an SQL database (MySQL or SQLite) and
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\columnwidth]{img/architecture.png}
+    \caption{Sources Tool Architecture. The frontend is implemented in
+      Javascript and sends REST requests to the C++ backend to retrieve and
+      update entities or statements, which are stored in a relational database.}
+    \label{fig:architecture}
+\end{figure}
+
+Entities and statements are stored in a relational database (MySQL or SQLite) and
 follow the Wikidata data structure with an additional status field to keep track
@@
 
-The REST API of the backend supports the following types of queries:
+The REST API of the backend supports the following main types of requests:
 \begin{itemize}
@@
 \end{itemize}
-All GET requests support an additional \Verb|state=...| query parameter to
+All GET requests support an additional \verb|state=...| query parameter to
 filter by state. This allows Wikidata developers to analyse statements that have
@@
 experience.
-
-\todo{Review and expand}
 

### 2015-10-14 paper.tex
Reviewed Sebastian's Section 4.2. Minor random changes.

--- 2015-10-14 paper.tex
@@
 
-\numberofauthors{5}
+\numberofauthors{3}
 \author{
-\alignauthor
-Thomas Pellissier Tanon\titlenote{The author was an intern at Google when the majority of the work was done.}
-   \affaddr{Google, San Francisco, USA}\\   
-   \email{thomaspelta@gmail.com}
-\alignauthor
-Denny Vrandečić
-   \affaddr{Google, San Francisco, USA}\\   
-   \email{vrandecic@google.com}
+Thomas Pellissier Tanon,\titlenote{The author was an intern at Google when the majority of the work was done.} Denny Vrandečić\\
+   \affaddr{Google San Francisco, United States of America}\\   
+   \email{\{thomaspt, vrandecic\}@google.com}
 \alignauthor
 Sebastian Schaffert\\
-   \affaddr{Google, Zurich, Switzerland}\\   
+   \affaddr{Google Zurich, Switzerland}\\   
    \email{schaffert@google.com}
-\and
 \alignauthor
 Thomas Steiner\\
-   \affaddr{Google, Hamburg, Germany}\\   
-   \email{tomac@google.com}
-\alignauthor
-Lydia Pintscher\\
-   \affaddr{Wikimedia, Berlin, Germany}\\   
-   \email{mail@pintscher.de}
+   \affaddr{Google Hamburg, Germany}\\   
+   \email{tsteiner@google.com}
 }
+
 \begin{document}
@@
 \begin{abstract}
-Collaborative knowledge bases that make their data freely available in a~machine-readable form
-are central for the data strategy of many projects and organizations.
-One such collaborative knowledge base is Freebase, initially launched by Metaweb in 2007,
-who were then acquired by Google in 2010.
-Another example is Wikidata, a~collaborative knowledge base developed by
-Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
-Due to the success of Wikidata, Google decided 2015 to shut down Freebase and
-help the community with the transfer of Freebase's content to Wikidata.
+Collaborative knowledge bases that make their data available in machine-readable form
+as structured data are central to many companies' data strategies.
+One such collaborative knowledge base is Freebase (\url{www.freebase.com}),
+initially created with proprietary technologies by a~company called Metaweb,
+which was then acquired by Google in 2010.
+Another example is Wikidata (\url{www.wikidata.org}),
+a~collaborative knowledge base developed in the open since 2012 by Wikimedia Deutschland
+and operated by the Wikimedia Foundation.
+Due to the success of Wikidata, in~2015, Google decided to shut down Freebase and
+help the community with the transfer of its content to Wikidata through a~crowdsourcing approach.
 In this paper, we describe the ongoing transfer efforts and data mapping challenges,
-and provide an analysis of the effort so far.
-We have created the \emph{Primary Sources Tool}
-that we have released as open source to facilitate the transfer of this dataset,
-but also future data migrations.
-Throughout the migration, we have gained insights into both Wikidata and Freebase,
+and provide an analysis of the process so far.
+For the task, we have created a~software solution called \emph{Primary Sources Tool}
+that we have released as open source to facilitate this and future data migrations.
+Throughout the migration, we have gained deep insights into both Wikidata and Freebase,
 and share and discuss detailed statistics on both knowledge bases. 
@@
 is usually a~problematic task and requires the careful mapping between their structures.
-In this paper, we describe how we facilitated the migration of
-Freebase\footnote{Freebase: \url{https://www.freebase.com}} content to
-Wikidata.\footnote{Wikidata: \url{https://www.wikidata.org}}
+In this paper, we describe how we facilitated the migration of Freebase content to Wikidata.
 That migration was no exception to this rule, and had a~number of \emph{structural} challenges.
@@
 
-Freebase is an open source and
+Freebase\footnote{Freebase: \url{https://www.freebase.com/}} is an open source and
 collaborative knowledge base created in 2007 by Metaweb and acquired in 2010 by Google.
@@
 linked to each of the entities of the two knowledge bases
-and propagate them to the connected entities which do not have such data.
-To implement this propagation we set as value (date or longitude) the average of the values of the entities which distance is less than $10$ with,
-as weighting, $2^{-d}$ with $d$ the distance between the two entities.
+and propagate them to the connected entities which do not have such data
+using a~decreasing exponential distribution \todo{Please clarify the ``propagate'' part}.
 We see that the two knowledge bases follow the same basic patterns,

### 2015-10-15 paper.tex
small changes in abstract

@@
 \begin{abstract}
-Collaborative knowledge bases that make their data available in machine-readable form
-as structured data are central to many companies' data strategies.
-One such collaborative knowledge base is Freebase (\url{www.freebase.com}),
-initially created with proprietary technologies by a~company called Metaweb,
-which was then acquired by Google in 2010.
-Another example is Wikidata (\url{www.wikidata.org}),
-a~collaborative knowledge base developed in the open since 2012 by Wikimedia Deutschland
+Collaborative knowledge bases that make their data freely available in a machine-readable form
+are central for the data strategy of many projects and organizations.
+One such collaborative knowledge base is Freebase,
+initially launched by Metaweb in 2007.
+Metaweb was acquired by Google in 2010.
+Another example is Wikidata,
+a~collaborative knowledge base developed by Wikimedia Deutschland since 2012
 and operated by the Wikimedia Foundation.
-Due to the success of Wikidata, in~2015, Google decided to shut down Freebase and
-help the community with the transfer of its content to Wikidata through a~crowdsourcing approach.
+Due to the success of Wikidata, Google decided 2015 to shut down Freebase and
+help the community with the transfer of Freebase's content to Wikidata.
 In this paper, we describe the ongoing transfer efforts and data mapping challenges,
-and provide an analysis of the process so far.
-For the task, we have created a~software solution called \emph{Primary Sources Tool}
-that we have released as open source to facilitate this and future data migrations.
-Throughout the migration, we have gained deep insights into both Wikidata and Freebase,
+and provide an analysis of the effort so far.
+We have created the \emph{Primary Sources Tool}
+that we have released as open source to facilitate the transfer of this dataset,
+but also future data migrations.
+Throughout the migration, we have gained insights into both Wikidata and Freebase,
 and share and discuss detailed statistics on both knowledge bases. 

### 2015-10-15 paper.tex
Added Lydia. Some minor corrections in abstract.

@@
 
-\numberofauthors{3}
+\numberofauthors{5}
 \author{
-Thomas Pellissier Tanon,\titlenote{The author was an intern at Google when the majority of the work was done.} Denny Vrandečić\\
-   \affaddr{Google San Francisco, United States of America}\\   
-   \email{\{thomaspt, vrandecic\}@google.com}
+\alignauthor
+Thomas Pellissier Tanon\titlenote{The author was an intern at Google when the majority of the work was done.}
+   \affaddr{Google, San Francisco, USA}\\   
+   \email{thomaspelta@gmail.com}
+\alignauthor
+Denny Vrandečić
+   \affaddr{Google, San Francisco, USA}\\   
+   \email{vrandecic@google.com}
 \alignauthor
 Sebastian Schaffert\\
-   \affaddr{Google Zurich, Switzerland}\\   
+   \affaddr{Google, Zurich, Switzerland}\\   
    \email{schaffert@google.com}
+\and
 \alignauthor
 Thomas Steiner\\
-   \affaddr{Google Hamburg, Germany}\\   
-   \email{tsteiner@google.com}
+   \affaddr{Google, Hamburg, Germany}\\   
+   \email{tomac@google.com}
+\alignauthor
+Lydia Pintscher\\
+   \affaddr{Wikimedia, Berlin, Germany}\\   
+   \email{mail@pintscher.de}
 }
-
 \begin{document}
@@
 \begin{abstract}
-Collaborative knowledge bases that make their data freely available in a machine-readable form
+Collaborative knowledge bases that make their data freely available in a~machine-readable form
 are central for the data strategy of many projects and organizations.
-One such collaborative knowledge base is Freebase,
-initially launched by Metaweb in 2007.
-Metaweb was acquired by Google in 2010.
-Another example is Wikidata,
-a~collaborative knowledge base developed by Wikimedia Deutschland since 2012
-and operated by the Wikimedia Foundation.
+One such collaborative knowledge base is Freebase, initially launched by Metaweb in 2007,
+who were then acquired by Google in 2010.
+Another example is Wikidata, a~collaborative knowledge base developed by
+Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
 Due to the success of Wikidata, Google decided 2015 to shut down Freebase and

### 2015-10-15 paper.tex
Add precisions about the date-longitude propagation
(please review the English)

@@
 linked to each of the entities of the two knowledge bases
-and propagate them to the connected entities which do not have such data
-using a~decreasing exponential distribution \todo{Please clarify the ``propagate'' part}.
+and propagate them to the connected entities which do not have such data.
+To implement this propagation we set as value (date or longitude)
+the average of the values of the entities which distance is less than $10$ with,
+as weighting, $2^{-d}$ with $d$ the distance between the two entities.
 We see that the two knowledge bases follow the same basic patterns,

### 2015-10-15 paper.tex
Change Thomas's email address
Minor corrections in affiliations and style/grammar.

--- 2015-10-15 paper.tex
@@
    \affaddr{Google, San Francisco, USA}\\   
-   \email{thomaspelta@gmail.com}
+   \email{\mbox{thomas@pellissier-tanon.fr}}
 \alignauthor
-Denny Vrandečić
+Denny Vrandečić\\
    \affaddr{Google, San Francisco, USA}\\   
@@
 In order to prepare the data for integration into the Primary Sources Tool,
-we have created a set of scripts which map the content
+we have created a~set of scripts which map the content
 of the last Freebase dump to Wikidata statements.%
@@
       JavaScript and sends HTTP requests to the C++ back-end to retrieve and
-      update entities or statements, which are stored in a relational database.
+      update entities or statements, which are stored in a~relational database.
       \todo{Create PDF version of the diagram, improve consistency of used terms}}
@@
 
-Entities and statements are stored in a relational database (MySQL or SQLite)
+Entities and statements are stored in a~relational database (MySQL or SQLite)
 and follow the Wikidata data structure with an additional status field
@@
 linked to each of the entities of the two knowledge bases
-and propagate them to the connected entities which do not have such data
-using a~decreasing exponential distribution \todo{Please clarify the ``propagate'' part}.
+and propagate them to the connected entities that do not have such data.
+To implement this propagation, we set as value (date or longitude)
+the average of the values of the entities whose distance is $<10$
+with $2^{-d}$ as weighting, $d$~being the distance between the two entities.
 We see that the two knowledge bases follow the same basic patterns,

### 2015-10-15 paper.tex
Moves spatio-temporal projections to PDF

@@
     \begin{subfigure}[b]{1.0\columnwidth}
-        \includegraphics[width=\textwidth]{img/freebase-time-space.png}
+        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
         \caption{Spatio-temporal distribution of Freebase.}
@@
     \begin{subfigure}[b]{1.0\columnwidth}
-        \includegraphics[width=\textwidth]{img/wikidata-time-space.png}
+        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
         \caption{Spatio-temporal distribution of Wikidata.}
@@
       the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
-      from the year 0 to 2015, following a~power law ($y' = y^8$). \todo{Create PDF versions of both diagrams}}
+      from the year 0 to 2015, following a~power law ($y' = y^8$).}
     \label{fig:time-space}

### 2015-10-15 paper.tex
PDF version of the reworked architecture diagram.

--- 2015-10-15 paper.tex
@@
     \centering
-    \includegraphics[width=.7\columnwidth]{img/architecture.png}
+    \includegraphics[width=.7\columnwidth]{img/architecture.pdf}
     \caption{Primary Sources Tool architecture. The front-end is implemented in
       JavaScript and sends HTTP requests to the C++ back-end to retrieve and
-      update entities or statements, which are stored in a~relational database.
-      \todo{Create PDF version of the diagram, improve consistency of used terms}}
+      update entities or statements, which are stored in a~relational database.}
     \label{fig:architecture}
+    % Source: https://docs.google.com/a/google.com/drawings/d/1vKAftQVjrso907UtbMXnEOabXwQHDVyyz2ewxcqz3b0/edit?usp=sharing
 \end{figure}

### 2015-10-15 paper.tex
Minor text improvements.

@@
     \centering
-    \includegraphics[width=.7\columnwidth]{img/architecture.pdf}
-    \caption{Primary Sources Tool architecture. The front-end is implemented in
-      JavaScript and sends HTTP requests to the C++ back-end to retrieve and
-      update entities or statements, which are stored in a~relational database.}
+    \includegraphics[width=.65\columnwidth]{img/architecture.pdf}
+    \caption{Primary Sources Tool architecture. The front-end (JavaScript) sends
+      HTTP requests to the back-end (C++) to retrieve and update entities or
+      statements, stored in a~relational database. Approved statements are in
+      addition written by the front-end to the Wikidata REST API.}    
     \label{fig:architecture}
@@
   (\emph{e.g.}, \verb|GET /entities/Q2529789|).
+  \item Get all entities with unapproved (or approved or rejected) statements
+  (\verb|/entities/all|).
   \item Get a~random entity with unapproved (or approved or rejected) statements
   (\verb|/entities/any|).
-  \item Get a~statement by database ID (\verb|GET /statements/1|) or get a~list of
+  \item Get a~statement by database ID (\verb|GET /statements/1|), get all
+    statements (\verb|GET /statements/all|), or get a~list of
   random statements (\verb|GET /statements/any|).

### 2015-10-15 paper.tex
added section related work (still empty)

@@
 and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
+In \autoref{sec:related-work} we discuss the relation to other work.
 The paper terminates with an outlook at proposed next steps
@@
 Freebase is an open source and
-collaborative knowledge base created in 2007 by Metaweb and acquired in 2010 by Google.
+collaborative knowledge base created in 2007 by Metaweb and 
+acquired in 2010 by Google~\cite{freebase}.
 It was used as the open core of the Google Knowledge Graph,
@@
 For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
-and the type \texttt{/government/us\_president} that allows the entity to have
+and the type \texttt{/government/us\_president} (among others) that allows the entity to have
 a fact with the property \texttt{/government/us\_president/presidency\_number}
@@
 
+\section{Related Work}\label{sec:related-work}
+
+There has been a lot of research on ontology mapping.
+
 \section{Future Work and Conclusion}\label{sec:future-work-and-conclusion}

### 2015-10-15 paper.tex
Added cats and other meta

@@
 
-% a~category with the (minimum) three required fields
-\category{H.4}{\todo{Hierarchy}}{Miscellaneous}
+\category{H.3.5}{Information Storage and Retrieval}{Online Information Systems}
+\category{H.5.3}{Information Interfaces}{Group and Organization Interfaces?Web-based interactions}
+\category{I.2.4}{Artifical Intelligence}{Knowledge Representation}
+\category{K.4.3}{Computers and Society}{Organizational Impacts Computer-supported collaborative work}
 
-\terms{\todo{Terms}}
+\terms{Human Factors, Documentation}
 
-\keywords{\todo{Keywords}}
+\keywords{AIW: AI for Web-Based Collaboration and Cooperation, AIW: Crowdsourcing Techniques and Methodologies, KRR: Knowledge Acquisition}
 
@@
 
-Freebase is an open source and
+Freebase is an open and
 collaborative knowledge base created in 2007 by Metaweb and 
@@
 It was used as the open core of the Google Knowledge Graph,
-and also has many use cases outside of Google.
+and has found many use cases outside of Google.
+Due to the success of Wikidata,
+Google announced in 2014 to close Freebase and offer most of its content to the
+Wikidata community~\cite{freebase-end}.
 
-Due to the success of Wikidata,
-it was decided to close Freebase and support the migration of its content to Wikidata.
 Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
@@
 
-To represent complex values like geographic coordinates or to annotate relations,
-for example, in order to add start and end dates for a~position held,
-Freebase has introduced the notion of Compound Value Types (CVTs, see \autoref{fig:cvt-obama}).
-They behave like topics, \emph{e.g.}, have a~mid and can have types,
-but do not have the \texttt{/common/topic} type.
+Freebase uses Compound Value Types (CVTs, see \autoref{fig:cvt-obama}) to represent
+n-ary relations with $n>2$, e.g. values like geographic coordinates,
+political positions held with a start and end date, or actors playing a specific character in a movie.
+CVT values are much like topics, \emph{i.e.} they have a~mid and can have types
+(usually only the compound value type).
 

### 2015-10-15 paper.tex
Updated intro

@@
 are central for the data strategy of many projects and organizations.
-One such collaborative knowledge base is Freebase, initially launched by Metaweb in 2007,
-who were then acquired by Google in 2010.
-Another example is Wikidata, a~collaborative knowledge base developed by
-Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
-Due to the success of Wikidata, Google decided 2015 to shut down Freebase and
-help the community with the transfer of Freebase's content to Wikidata.
+The two major collaborative knowledge bases are Google's Freebase and Wikimedia's Wikidata.
+Due to the success of Wikidata, Google decided in 2015 to offer the content of Freebase
+to the Wikidata community.
 In this paper, we describe the ongoing transfer efforts and data mapping challenges,
 and provide an analysis of the effort so far.
-We have created the \emph{Primary Sources Tool}
-that we have released as open source to facilitate the transfer of this dataset,
-but also future data migrations.
+We describe the \emph{Primary Sources Tool}, which aims to facilitate
+this and future data migrations.
 Throughout the migration, we have gained insights into both Wikidata and Freebase,
@@
 \category{H.5.3}{Information Interfaces}{Group and Organization Interfaces?Web-based interactions}
-\category{I.2.4}{Artifical Intelligence}{Knowledge Representation}
+\category{I.2.4}{Artificial Intelligence}{Knowledge Representation}
 \category{K.4.3}{Computers and Society}{Organizational Impacts Computer-supported collaborative work}
@@
 
+Large web-based knowledge bases that make their data available
+under free licenses in a~machine-readable form
+have become central for the data strategy of many projects and organizations.
+They find applications in areas as diverse as web search,
+natural language annotation, or translation.
+\todo{add references to papers with examples}
+
+One such collaborative knowledge base is Freebase,
+initially launched by Metaweb in 2007 and acquired by Google in 2010.
+Another example is Wikidata, a~collaborative knowledge base developed by
+Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
+Due to the success of Wikidata, Google announced in 2014 to shut down Freebase and
+help the community with the transfer of Freebase's content to Wikidata.
+
 Moving data between two knowledge bases that do not share a~similar design
 is usually a~problematic task and requires the careful mapping between their structures.
-In this paper, we describe how we facilitated the migration of
-Freebase\footnote{Freebase: \url{https://www.freebase.com}} content to
-Wikidata.\footnote{Wikidata: \url{https://www.wikidata.org}}
-That migration was no exception to this rule, and had a~number of \emph{structural} challenges.
+The migration from Freebase to Wikidata was no exception to this rule:
+we encountered a~number of \emph{structural} challenges.
 Even more challenging was the \emph{cultural} difference between the two involved communities.
@@
 and different requirements regarding their data.
-\todo{Expand}
 
-The remainder of this paper is structured as follows.
-After an introduction to the two collaborative knowledge bases
-Freebase and Wikidata in \autoref{sec:background},
-we describe our methodology and the metrics used to measure the migration
+In this paper we describe how we support the Wikidata community with
+the migration of Freebase content to Wikidata.
+We created the \emph{Primary Sources Tool},
+released as open source to facilitate the transfer of the Freebase dataset.
+The \emph{Primary Sources Tool} is also developed with an eye on
+future data migrations from other source.
+We created and published mappings of the Freebase dataset.
+Throughout the migration, we have gained insights into both Wikidata and Freebase,
+and share and discuss detailed statistics on both knowledge bases.
+
+The paper is structured as follows.
+First, we introduce Freebase and Wikidata in \autoref{sec:background}.
+Then we describe our methodology and the metrics used to measure the migration
 in \autoref{sec:challenges-of-the-migration}.
@@
 and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
-In \autoref{sec:related-work} we discuss the relation to other work.
-The paper terminates with an outlook at proposed next steps
+Before we close, we discuss related work in \autoref{sec:related-work},
+followed by an outlook at proposed next steps
 and a~conclusion in \autoref{sec:future-work-and-conclusion}.
@@
 
-Freebase is an open and
+Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open and
 collaborative knowledge base created in 2007 by Metaweb and 
@@
 
-Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
-Each Freebase topic has a~stable identifier called \emph{``mid''} (for Metaweb ID),
+Freebase is build on the notions of \emph{objects}, \emph{facts}, \emph{types}, and \emph{properties}.
+Each Freebase object has a~stable identifier called a \emph{``mid''} (for Metaweb ID),
 one or more types, and uses properties from these types in order to provide facts.
-For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
+For example, the Freebase object for Barack Obama has the mid \texttt{/m/02mjmr}
 and the type \texttt{/government/us\_president} (among others) that allows the entity to have
@@
 n-ary relations with $n>2$, e.g. values like geographic coordinates,
-political positions held with a start and end date, or actors playing a specific character in a movie.
-CVT values are much like topics, \emph{i.e.} they have a~mid and can have types
-(usually only the compound value type).
+political positions held with a start and end date, or actors playing a character in a movie.
+CVT values are just objects, \emph{i.e.} they have a~mid and can have types
+(although they usually have only the compound value type itself).
+Most non-CVT objects are called \emph{topics} in order to discern them from CVTs.
 
-The content of Freebase has been imported from various sources like Wikipedia
-or the Internet Movie Database IMDB,
-in consequence Google does not own the copyright of some parts of the content of the knowledge base
-like images or long entity descriptions extracted from Wikipedia.
-As of the closing of Freebase on March~31, 2015,
+The content of Freebase has been partially imported from various sources like Wikipedia
+or the license-compatible part of MusicBrainz.
+Over the years, the Freebase community and Google have maintained the knowledge base.
+When Freebase was turned read-only on March~31, 2015,
 it counted more than 3~billion facts about almost 50M~entities.
+
+The data from Freebase is published as an N-Triples dump in RDF~\cite{rdf} under
+the Creative Commons CC-BY license.\footnote{\url{https://developers.google.com/freebase/data}}
 
@@
 is a~collaborative knowledge base
-launched in October 2012 and hosted by the Wikimedia Foundation.
-Its community has been growing quickly since the beginning, and as of mid 2015,
-the community comprises about 6,000 active contributors.
+launched in October 2012 and hosted by the Wikimedia Foundation~\cite{vrandevcic2014wikidata}.
+Its community has been growing quickly, and as of mid 2015,
+the community comprises about 6,000 active contributors~\cite{wikidatastats}.
 
 Wikidata's data model relies on the notions of \emph{item} and \emph{statement}.
-An item represent a~concept, has a~stable identifier and may have some labels,
+An item represents an~entity, has a~stable identifier and may have labels,
 descriptions, and aliases in multiple languages, links to pages about this concept
-in the others Wikimedia projects, like Wikipedia, and statements.
-Contrary to Freebase, Wikidata encodes with its statements not true facts,
-but \emph{claims} from different sources.
+in the others Wikimedia projects, most prominently Wikipedia, and statements.
+Contrary to Freebase, Wikidata statements do not aim to encode true facts,
+but \emph{claims} from different sources which can also contradict each other.
 
-A~statement is composed of one claim and zero or more references for this claim.
+A~statement is composed of a claim and zero or more references for this claim.
 The claim itself is composed of one main property--value couple that encodes
@@
 to add information about it like ``as of June 2012''.
-\autoref{fig:statement} illustrates the used nomenclature with an example.
+\autoref{fig:statement} illustrates the terminology with an example.
 
-The content of Wikidata is freely available under a~Creative Commons~0 (CC0) license.
-As of mid 2015, Wikidata counted about 66M~statements on 14M~entities.
-For more background information about Wikidata, see~\cite{vrandevcic2014wikidata}
-by Vrandečić and Krötzsch.
-For a~comparison between Freebase and Wikidata,
-we refer the reader to~\cite{farbercomparative} by Färber \emph{et~al.}
+The content of Wikidata is available under the Creative Commons CC0 license.
+As of mid 2015, Wikidata counted about 66M~statements on 14M~entities. \todo{update}
+
+A~comparison between Freebase, Wikidata, and other free and open knowledge bases
+(DBpedia, YAGO, and OpenCyc) is available in~\cite{farbercomparative}.
 
@@
 \includegraphics[width=8.45 cm]{img/Wikidata_statement.pdf}
-\caption{Wikidata nomenclature illustrated with an example (Source:
+\caption{Wikidata terminology illustrated with an example (Source:
 	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg}).}
@@
 like images or descriptions extracted from Wikipedia.
+In consequence Google does not own the copyright of some parts of the content of the knowledge base,
+such as images or long entity descriptions extracted from Wikipedia.
 In a~first step, we filtered the Freebase dump for this kind of content

### 2015-10-16 paper.tex
fix year for Freebase to Wikidata decision
The decision was announced in 2014. This is also mentioned later in the paper.
open source -> open source software
Something is released either under an open source license or as open source software

@@
 The two major collaborative knowledge bases are Google's Freebase and Wikimedia's Wikidata.
-Due to the success of Wikidata, Google decided in 2015 to offer the content of Freebase
+Due to the success of Wikidata, Google decided in 2014 to offer the content of Freebase
 to the Wikidata community.
@@
 We created the \emph{Primary Sources Tool},
-released as open source to facilitate the transfer of the Freebase dataset.
+released as open source software to facilitate the transfer of the Freebase dataset.
 The \emph{Primary Sources Tool} is also developed with an eye on

### 2015-10-16 paper.tex
CC0 is not a license but a rights waiver
https://en.wikipedia.org/wiki/Creative_Commons_license#Zero_.2F_public_domain
update statement and item numbers
data taken from https://tools.wmflabs.org/wikidata-todo/stats.php

@@
 
-The content of Wikidata is available under the Creative Commons CC0 license.
+The content of Wikidata is available under Creative Commons CC0.
 As of mid 2015, Wikidata counted about 66M~statements on 14M~entities. \todo{update}
@@
 The first challenge concerns the licenses under which the datasets are published.
-Wikidata is published under a~Creative Commons~0 (CC0~1.0) license
+Wikidata is published under Creative Commons~0 (CC0~1.0)
 that effectively puts the data in the public domain,

### 2015-10-16 paper.tex
add todo for number of properties

--- 2015-10-16 paper.tex
@@
 With that, we have been able to quickly map around 360~properties
-(note that Wikidata has a~total of 1,660 properties, and Freebase has around 37,700 properties).
+(note that Wikidata has a~total of 1,660 properties, and Freebase has around 37,700 properties
+\todo{This should probably have a date. As of today Wikidata has 1863 properties.}).
 For the mapping of properties where the domain are other topics or literals,

### 2015-10-16 paper.tex
add todo for time-frame
This sentence otherwise reads strange.
one already too much in this sentence ;-)

@@
 in order to gather initial user feedback.
-In the following, we progressively added more statements to the tool's database back-end.
+In the following \todo{Weeks? Months?}, we progressively added more statements to the tool's database back-end.
 Thereby, we were able to slowly upscale the tool's database back-end
@@
 from the community about the already mapped data and thus to adapt the mapping scripts easily
-and correct minor issues with the data early on already in the back-end.
+and correct minor issues with the data early on in the back-end.
 Upon approval or rejection of either a~claim or a~reference,

### 2015-10-16 paper.tex
capitalize Foundation in Wikimedia Foundation

@@
 providing statistical data about the approvals and rejections done over time.
-As the resources of the Wikimedia foundation are limited,
+As the resources of the Wikimedia Foundation are limited,
 the back-end was implemented in highly optimized C++

### 2015-10-16 paper.tex
improve wording
switch my email address

@@
    \affaddr{Wikimedia, Berlin, Germany}\\   
-   \email{mail@pintscher.de}
+   \email{lydia@pintscher.de}
 }
@@
 The content of Wikidata is available under the Creative Commons CC0 license.
-As of mid 2015, Wikidata counted about 66M~statements on 14M~entities. \todo{update}
+As of September 2015, Wikidata counted about 70M~statements on 18M~entities.
 
@@
 this would lead to a~21\% increase of the number of statements in Wikidata.
-The question raises why these numbers are so low compared to the size of Freebase.
+This raises the question why these numbers are so low compared to the size of Freebase.
 We argue that the main reason is that we have only mapped 4.56M~items to Wikidata,

### 2015-10-16 paper.tex
CC0 is not a license but a rights waiver
https://en.wikipedia.org/wiki/Creative_Commons_license#Zero_.2F_public_domain

@@
 
-The content of Wikidata is available under the Creative Commons CC0 license.
+The content of Wikidata is available under Creative Commons CC0.
 As of September 2015, Wikidata counted about 70M~statements on 18M~entities.

### 2015-10-16 paper.tex
add section about social scaling of Wikidata and long-term maintenance

@@
 The tool will be described in more detail in \autoref{sec:primary-sources-tool}.
+
+\subsection{Long-term maintenance}
+\label{sec:longtermmaintenance}
+
+Wikidata's editing community is in charge of the project's content. This includes collecting the
+data as well as long-term maintenance of it. Data needs to be updated as the world changes but also
+kept free of vandalism. An increase in the amount of data comes with an increase in maintenance
+cost for the community. Simply ingesting the Freebase data would have meant overwhelming the
+existing editors and thereby harming the project in the long run. To counter this, a significant
+increase in the amount of data needs to go along with either an increase in the number of editors
+or providing of tools to assist the existing editors to allow them to be more effective. With the
+Primary Sources Tool we aim to help grow the community in step with the amount of data. It is
+useful as a means to get more people to edit because it lowers the barrier to entry. It does this
+by making it easier to find potential edits. At the same time it helps make some of the existing
+editors more effective by allowing them to add statements with a single click.
 

### 2015-10-16 paper.tex
improved keywords (got wrong conference, fixed image
references

@@
 
-\keywords{AIW: AI for Web-Based Collaboration and Cooperation, AIW: Crowdsourcing Techniques and Methodologies, KRR: Knowledge Acquisition}
+\keywords{Crowdsourcing systems, Semantic Web, Wikidata, Freebase}
 
@@
 
-The content of Freebase has been partially imported from various sources like Wikipedia
-or the license-compatible part of MusicBrainz.
+The content of Freebase has been partially imported from various sources
+such as Wikipedia~\cite{wikipedia-works} or
+the license-compatible part of MusicBrainz~\cite{musicbrainz}.
 Over the years, the Freebase community and Google have maintained the knowledge base.
@@
 The first challenge concerns the licenses under which the datasets are published.
-Wikidata is published under Creative Commons~0 (CC0~1.0)
+Wikidata is published under the Creative Commons~0 (CC0~1.0)~\cite{cc0} license.
 that effectively puts the data in the public domain,
@@
 
+\begin{figure*}[!ht]
+    \centering
+    \begin{subfigure}[b]{1.0\columnwidth}
+        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
+        \caption{Spatio-temporal distribution of Freebase.}
+        \label{fig:freebase}
+    \end{subfigure}
+    \begin{subfigure}[b]{1.0\columnwidth}
+        \includegraphics[width=\textwidth]{img/wikidata-projection-bw.pdf}
+        \caption{Spatio-temporal distribution of Wikidata.}
+        \label{fig:wikidata}
+    \end{subfigure}
+    \caption{Spatio-temporal distribution of Freebase and Wikidata items,
+      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
+      from the year 0 to 2015, following a~power law ($y' = y^8$).}
+    \label{fig:time-space}
+\end{figure*}
+
 In order to get an idea of the coverage of the two knowledge bases,
@@
 to judge the proportion of additional good data.
-
-\begin{figure*}[!htbp]
-    \centering
-    \begin{subfigure}[b]{1.0\columnwidth}
-        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
-        \caption{Spatio-temporal distribution of Freebase.}
-        \label{fig:freebase}
-    \end{subfigure}
-    \begin{subfigure}[b]{1.0\columnwidth}
-        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
-        \caption{Spatio-temporal distribution of Wikidata.}
-        \label{fig:wikidata}
-    \end{subfigure}
-    \caption{Spatio-temporal distribution of Freebase and Wikidata items,
-      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
-      from the year 0 to 2015, following a~power law ($y' = y^8$).}
-    \label{fig:time-space}
-\end{figure*}
 

### 2015-10-16 paper.tex
Subdivided related work section (still needs content)

@@
 
+\begin{figure*}[h]
+    \centering
+    \begin{subfigure}[b]{1.0\columnwidth}
+        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
+        \caption{Spatio-temporal distribution of Freebase.}
+        \label{fig:freebase}
+    \end{subfigure}
+    \begin{subfigure}[b]{1.0\columnwidth}
+        \includegraphics[width=\textwidth]{img/wikidata-projection-bw.pdf}
+        \caption{Spatio-temporal distribution of Wikidata.}
+        \label{fig:wikidata}
+    \end{subfigure}
+    \caption{Spatio-temporal distribution of Freebase and Wikidata items,
+      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
+      from the year 0 to 2015, following a~power law ($y' = y^8$).}
+    \label{fig:time-space}
+\end{figure*}
+
 \subsection{Quantitative Comparison}
@@
 
-\begin{figure*}[!ht]
-    \centering
-    \begin{subfigure}[b]{1.0\columnwidth}
-        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
-        \caption{Spatio-temporal distribution of Freebase.}
-        \label{fig:freebase}
-    \end{subfigure}
-    \begin{subfigure}[b]{1.0\columnwidth}
-        \includegraphics[width=\textwidth]{img/wikidata-projection-bw.pdf}
-        \caption{Spatio-temporal distribution of Wikidata.}
-        \label{fig:wikidata}
-    \end{subfigure}
-    \caption{Spatio-temporal distribution of Freebase and Wikidata items,
-      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
-      from the year 0 to 2015, following a~power law ($y' = y^8$).}
-    \label{fig:time-space}
-\end{figure*}
-
 In order to get an idea of the coverage of the two knowledge bases,
@@
 
-There has been a lot of research on ontology mapping.
+For the challenges listed in \autoref{section:challenges-of-the-migration}
+there is a body of work dealing with it. In many cases, the problems we have encountered in
+this migration have turned out to be much simpler than the problems solved in existing research.
+
+\textbf{Data licensing.}
+Only dealing with two open licenses.
+
+\textbf{Topic mappings.}
+Since both databases build on Wikipedia...
+
+\textbf{Schema mappings.}
+There has been extensive research on the topic of mapping the structures
+of two databases or knowledge bases~\cite{mappingsurvey1,mappingsurvey2,mappingsurvey3}.
+The current work is, in many technical respects, rather simple:
+we are looking for a one-directional mapping (since the case of data
+flowing from Wikidata back to Freebase is not relevant),
+for a one-off data flow (since Freebase is now read-only),
+evaluated by human contributors (therefore the quality of the mapping
+
+\textbf{Data maintenance.}
+Should also cover references (kvault) and quality.
 

### 2015-10-16 paper.tex
Tiny correction in Abstract. Correct categories.

@@
 this and future data migrations.
-Throughout the migration, we have gained insights into both Wikidata and Freebase,
+Throughout the migration, we have gained deep insights into both Wikidata and Freebase,
 and share and discuss detailed statistics on both knowledge bases. 
@@
 
+% \category{CR number}{category}{sub-category}[optional subject descriptor]
 \category{H.3.5}{Information Storage and Retrieval}{Online Information Systems}
-\category{H.5.3}{Information Interfaces}{Group and Organization Interfaces?Web-based interactions}
+\category{H.5.3}{Information Interfaces}{Group and Organization Interfaces}[Web-based interactions]
 \category{I.2.4}{Artificial Intelligence}{Knowledge Representation}
-\category{K.4.3}{Computers and Society}{Organizational Impacts Computer-supported collaborative work}
+\category{K.4.3}{Computers and Society}{Organizational Impacts}[Com\-puter-supported collaborative work]
 

### 2015-10-16 paper.tex
Proof-reading Section 1.

@@
 
-Large web-based knowledge bases that make their data available
+Large Web-based knowledge bases that make their data available
 under free licenses in a~machine-readable form
 have become central for the data strategy of many projects and organizations.
-They find applications in areas as diverse as web search,
+They find applications in areas as diverse as Web search,
 natural language annotation, or translation.
@@
 Due to the success of Wikidata, Google announced in 2014 to shut down Freebase and
-help the community with the transfer of Freebase's content to Wikidata.
+help the community with the transfer of Freebase's content to Wikidata~\cite{freebase2014shutdown}.
 
@@
 The migration from Freebase to Wikidata was no exception to this rule:
-we encountered a~number of \emph{structural} challenges.
-Even more challenging was the \emph{cultural} difference between the two involved communities.
+we encountered a~number of to-be-expected \emph{structural} challenges.
+However, even more demanding was the \emph{cultural} difference between the two involved communities.
 The Freebase and Wikidata communities have a~very different background,
@@
 
-In this paper we describe how we support the Wikidata community with
+In this paper, we describe how we support the Wikidata community with
 the migration of Freebase content to Wikidata.
-We created the \emph{Primary Sources Tool},
-released as open source software to facilitate the transfer of the Freebase dataset.
+We programmed the \emph{Primary Sources Tool} and
+released it as open source software to facilitate the transfer of the Freebase dataset.
 The \emph{Primary Sources Tool} is also developed with an eye on
-future data migrations from other source.
+future data migrations from other sources.
 We created and published mappings of the Freebase dataset.
-Throughout the migration, we have gained insights into both Wikidata and Freebase,
+Throughout the migration, we have gained deep insights into both Wikidata and Freebase,
 and share and discuss detailed statistics on both knowledge bases.
@@
 that we present in \autoref{sec:primary-sources-tool}.
-We then present the results of the migration
+We then show the results of the migration
 and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
-Before we close, we discuss related work in \autoref{sec:related-work},
+Before we close, we report on related work in \autoref{sec:related-work},
 followed by an outlook at proposed next steps
@@
 Freebase is build on the notions of \emph{objects}, \emph{facts}, \emph{types}, and \emph{properties}.
-Each Freebase object has a~stable identifier called a \emph{``mid''} (for Metaweb ID),
+Each Freebase object has a~stable identifier called a~\emph{``mid''} (for Metaweb ID),
 one or more types, and uses properties from these types in order to provide facts.
@@
 n-ary relations with $n>2$, e.g. values like geographic coordinates,
-political positions held with a start and end date, or actors playing a character in a movie.
+political positions held with a~start and end date, or actors playing a~character in a~movie.
 CVT values are just objects, \emph{i.e.} they have a~mid and can have types
@@
 
-A~statement is composed of a claim and zero or more references for this claim.
+A~statement is composed of a~claim and zero or more references for this claim.
 The claim itself is composed of one main property--value couple that encodes
@@
 cost for the community. Simply ingesting the Freebase data would have meant overwhelming the
-existing editors and thereby harming the project in the long run. To counter this, a significant
+existing editors and thereby harming the project in the long run. To counter this, a~significant
 increase in the amount of data needs to go along with either an increase in the number of editors
@@
 Primary Sources Tool we aim to help grow the community in step with the amount of data. It is
-useful as a means to get more people to edit because it lowers the barrier to entry. It does this
+useful as a~means to get more people to edit because it lowers the barrier to entry. It does this
 by making it easier to find potential edits. At the same time it helps make some of the existing
-editors more effective by allowing them to add statements with a single click.
+editors more effective by allowing them to add statements with a~single click.
 
@@
 (note that Wikidata has a~total of 1,660 properties, and Freebase has around 37,700 properties
-\todo{This should probably have a date. As of today Wikidata has 1863 properties.}).
+\todo{This should probably have a~date. As of today Wikidata has 1863 properties.}).
 For the mapping of properties where the domain are other topics or literals,
@@
 For the challenges listed in \autoref{section:challenges-of-the-migration}
-there is a body of work dealing with it. In many cases, the problems we have encountered in
+there is a~body of work dealing with it. In many cases, the problems we have encountered in
 this migration have turned out to be much simpler than the problems solved in existing research.
@@
 The current work is, in many technical respects, rather simple:
-we are looking for a one-directional mapping (since the case of data
+we are looking for a~one-directional mapping (since the case of data
 flowing from Wikidata back to Freebase is not relevant),
-for a one-off data flow (since Freebase is now read-only),
+for a~one-off data flow (since Freebase is now read-only),
 evaluated by human contributors (therefore the quality of the mapping

### 2015-10-16 paper.tex
Proof-reading Section 2.

@@
 Google announced in 2014 to close Freebase and offer most of its content to the
-Wikidata community~\cite{freebase-end}.
+Wikidata community~\cite{freebase2014shutdown,freebase-end}.
 
-Freebase is build on the notions of \emph{objects}, \emph{facts}, \emph{types}, and \emph{properties}.
+Freebase is built on the notions of \emph{objects}, \emph{facts}, \emph{types}, and \emph{properties}.
 Each Freebase object has a~stable identifier called a~\emph{``mid''} (for Metaweb ID),
@@
 and the type \texttt{/government/us\_president} (among others) that allows the entity to have
-a fact with the property \texttt{/government/us\_president/presidency\_number}
+a fact with the property \texttt{/government/us\_president/presidency\_number} \linebreak
 and the literal integer ``44'' as the value.
 
-\begin{figure}[!htbp]
+Freebase uses Compound Value Types (CVTs) to represent
+n-ary relations with $n>2$, \emph{e.g.}, values like geographic coordinates,
+political positions held with a~start and an end date (see \autoref{fig:cvt-obama} for an example),
+or actors playing a~character in a~movie.
+CVT values are just objects, \emph{i.e.}, they have a~mid and can have types
+(although they usually have only the compound value type itself).
+Most non-CVT objects are called \emph{topics} in order to discern them from CVTs.
+
+\begin{figure}[!t]
   \centering
@@
   \caption{Exemplary Compound Value Type (CVT) in Freebase: Presidency of Barack Obama.}
-%The source is https://docs.google.com/document/d/1ELrBtxxs4ghhe7FloTUnhvpD3f7RFczT7UfxahAfjgE/edit
+  % Source: https://docs.google.com/document/d/1ELrBtxxs4ghhe7FloTUnhvpD3f7RFczT7UfxahAfjgE/edit
   \label{fig:cvt-obama}
@@
 
-Freebase uses Compound Value Types (CVTs, see \autoref{fig:cvt-obama}) to represent
-n-ary relations with $n>2$, e.g. values like geographic coordinates,
-political positions held with a~start and end date, or actors playing a~character in a~movie.
-CVT values are just objects, \emph{i.e.} they have a~mid and can have types
-(although they usually have only the compound value type itself).
-Most non-CVT objects are called \emph{topics} in order to discern them from CVTs.
-
 The content of Freebase has been partially imported from various sources
 such as Wikipedia~\cite{wikipedia-works} or
-the license-compatible part of MusicBrainz~\cite{musicbrainz}.
+the license-compa\-tible part of MusicBrainz~\cite{musicbrainz}.
 Over the years, the Freebase community and Google have maintained the knowledge base.
@@
 it counted more than 3~billion facts about almost 50M~entities.
-
 The data from Freebase is published as an N-Triples dump in RDF~\cite{rdf} under
-the Creative Commons CC-BY license.\footnote{\url{https://developers.google.com/freebase/data}}
+the Creative Commons CC-BY license.\footnote{Dump: \url{https://developers.google.com/freebase/data}}
 
@@
 Wikidata's data model relies on the notions of \emph{item} and \emph{statement}.
-An item represents an~entity, has a~stable identifier and may have labels,
-descriptions, and aliases in multiple languages, links to pages about this concept
-in the others Wikimedia projects, most prominently Wikipedia, and statements.
+An item represents an~entity, has a~stable identifier called ``qid'', and may have labels,
+descriptions, and aliases in multiple languages; further statements and links to pages
+about the entity in other Wikimedia projects---most prominently Wikipedia.
 Contrary to Freebase, Wikidata statements do not aim to encode true facts,
-but \emph{claims} from different sources which can also contradict each other.
+but \emph{claims} from different sources, which can also contradict each other.
 
 A~statement is composed of a~claim and zero or more references for this claim.
-The claim itself is composed of one main property--value couple that encodes
+The claim itself is composed of one main property--value pair that encodes
 the main (claimed) fact like ``population is 8,173,900'' and optional qualifiers
 to add information about it like ``as of June 2012''.
-\autoref{fig:statement} illustrates the terminology with an example.
+\autoref{fig:statement} illustrates the used terminology with an example.
 
-The content of Wikidata is available under Creative Commons CC0.
-As of September 2015, Wikidata counted about 70M~statements on 18M~entities.
-
-A~comparison between Freebase, Wikidata, and other free and open knowledge bases
-(DBpedia, YAGO, and OpenCyc) is available in~\cite{farbercomparative}.
-
-\begin{figure}[!htbp]
+\begin{figure}[!t]
   \centering
@@
 \end{figure}
+
+The content of Wikidata is in the public domain under Creative Commons CC0.
+As of September 2015, Wikidata counted about 70M~statements on 18M~entities.
+A~more in-depth comparison between Freebase, Wikidata, and other free and open knowledge bases
+(DBpedia, YAGO, and OpenCyc) is available in~\cite{farbercomparative} by Färber \emph{et~al.}
 

### 2015-10-16 paper.tex
Proof-reading Section 3.

@@
 
-\begin{figure}[!t]
+\begin{figure}[!htbp]
   \centering
@@
 
-During our ongoing efforts with the migration of Freebase to Wikidata
+During our ongoing efforts with the migration of Freebase to Wikidata,
 we were faced with a~number of technical and non-technical challenges
@@
 The first challenge concerns the licenses under which the datasets are published.
-Wikidata is published under the Creative Commons~0 (CC0~1.0)~\cite{cc0} license.
-that effectively puts the data in the public domain,
+Wikidata is published under the Creative Commons~0 (CC0~1.0)~\cite{cc0} license,
+which effectively puts the data in the public domain,
 whereas Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license
@@
 In a~first step, we filtered the Freebase dump for this kind of content
-before being able to create a~dump that we could relicense under CC0~1.0.
+before being able to create a~data dump that we could relicense under CC0~1.0.
 This step reduced the number of Freebase facts that could be republished by about 42M~facts
@@
 by introducing a~domain blacklist.%
-\footnote{URL blacklist:
+\footnote{Domain blacklist:
 \url{https://www.wikidata.org/wiki/Wikidata:Primary_sources_tool/URL_blacklist}}
@@
 Wikidata's editing community is in charge of the project's content. This includes collecting the
-data as well as long-term maintenance of it. Data needs to be updated as the world changes but also
+data as well as long-term maintenance of it. Data needs to be updated as the world changes, but also
 kept free of vandalism. An increase in the amount of data comes with an increase in maintenance
@@
 increase in the amount of data needs to go along with either an increase in the number of editors
-or providing of tools to assist the existing editors to allow them to be more effective. With the
-Primary Sources Tool we aim to help grow the community in step with the amount of data. It is
+or provision of tools to assist the existing editors to allow them to be more effective. With the
+Primary Sources Tool, we aim to help grow the community in step with the amount of data. It is
 useful as a~means to get more people to edit because it lowers the barrier to entry. It does this
-by making it easier to find potential edits. At the same time it helps make some of the existing
+by making it easier to find potential edits. At the same time, it helps make some of the existing
 editors more effective by allowing them to add statements with a~single click.
@@
 even if there is only a~single shared Wikipedia link.
-The precision of the mapping is naturally lower compared to Google's mapping,
+The precision of the mapping is naturally lower compared to Google's mapping
 as there are more wrong matches (often because there is no clear separation between topics
@@
 As we have shown in \autoref{sec:dataquality},
-that human curation is required before importation anyway,
+human curation is required before importation anyway,
 which is why we have decided to merge the two mapping dumps,
@@
 whereas the topics that were \emph{not} mapped have an average number of only 5.7~facts.
-We have mapped the majority of topics with more than 47~facts
+We have mapped the majority of all topics with more than 47~facts
 (191K~non mapped topics \textit{vs.} 195K~mapped topics).
@@
 
-For the mapping between Freebase and Wikidata properties we have chosen to do it by hand
+For the mapping between Freebase and Wikidata properties, we have chosen to do it by hand
 with the help of the Wikidata community.
 With that, we have been able to quickly map around 360~properties
-(note that Wikidata has a~total of 1,660 properties, and Freebase has around 37,700 properties
-\todo{This should probably have a~date. As of today Wikidata has 1863 properties.}).
+(note that Wikidata has a~total of 1,863 properties, and Freebase has around 37,700 properties
+\todo{This should probably have a~date.}).
 For the mapping of properties where the domain are other topics or literals,
@@
 we map both the property that links the topic to the CVT
-and the main property of the CVT to the same Wikidata property, and, during the mapping process,
+and the main property of the CVT to the same Wikidata property, and during the mapping process
 pick the latter as the main property of the CVT.
@@
 and use the same precision guessing algorithm as the one used by the Wikidata user interface.
-For dates, we just map the date and time values (encoded using XSD%
-\footnote{\url{ http://www.w3.org/TR/xmlschema11-2/}} types)
+For dates, we just map the date and time values
+(encoded using XSD types~\cite{campbell2003xmlschema})
 to the Wikidata ``time'' datatype, however, filter out dates before 1920 that have

### 2015-10-17 paper.tex
related work

--- 2015-10-16 paper.tex
@@
 
-\subsection{Data Topic Mappings}
+\subsection{Data Topic Mappings}\label{subsec:topic-mappings}
 
@@
 
-For the challenges listed in \autoref{section:challenges-of-the-migration}
+For the challenges listed in \autoref{sec:challenges-of-the-migration}
 there is a~body of work dealing with it. In many cases, the problems we have encountered in
@@
 \textbf{Data licensing.}
-Only dealing with two open licenses.
-
-\textbf{Topic mappings.}
-Since both databases build on Wikipedia...
+Although many books and tutorials on publishing data on the Web of Data
+(e.g.~\cite{linkeddatabook,linkeddatabestpractises}) mention the importance of licenses,
+they are often added as an afterthought.
+They have been preciously few dedicated publications on the
+topic~\cite{licenses,licensius}, none of them written by lawyers.
+Due to the lack of understanding surronding these topics, we have been
+cautious and chose to simply remove any facts from the migrating data
+where the situation is in doubt.
 
@@
 There has been extensive research on the topic of mapping the structures
-of two databases or knowledge bases~\cite{mappingsurvey1,mappingsurvey2,mappingsurvey3}.
+of two databases or knowledge bases
+(some surveys are~\cite{mappingsurvey1,mappingsurvey2,mappingsurvey3}).
 The current work is, in many technical respects, rather simple:
@@
 flowing from Wikidata back to Freebase is not relevant),
-for a~one-off data flow (since Freebase is now read-only),
-evaluated by human contributors (therefore the quality of the mapping
+a~one-off data flow (since Freebase is now read-only),
+mostly individually evaluated by human contributors
+(therefore not requiring a perfect mapping).
+The effort most similar to ours is the DBpedia Mapping Wiki~\cite{lehmann2014dbpedia}.
+The DBpedia community is manually writing and maintaining the mapping from
+the DBpedia extraction process (working on Wikipedia) to the DBpedia ontology.
+The main difference is that the DBpedia mapping is running continuously
+and does not allow for point-fixes, thus necessitating a higher quality of the mapping,
+whereas for the Freebase to Wikidata mapping every single results is expected to be curated.
+
+\textbf{Entity mappings.}
+Entity mapping (often called entity linking) deals with finding the objects
+in several sources that refer to the same entity in the domain of discourse.
+There is extensive work in this area (e.g.~\cite{entitylinkingsurvey1,entitylinkingsurvey2})
+but we avoided most of the challenges by relying on the simple fact that
+both Freebase and Wikidata have historically been bootstrapped by using Wikipedia.
+Wikipedia is often used as a benchmark for entity mapping systems~\cite{entitylinkingwikipedia}.
+As described in \autoref{subsec:topic-mappings} this lead to sufficiently good results for the head,
+and we think it would be surprising if further effort in this area would lead to reasonable gains.
 
 \textbf{Data maintenance.}
-Should also cover references (kvault) and quality.
+The Wikidata requirements~\cite{wikidatareqs} states that the data uploaded to Wikidata
+must not overwhelm the community.
+Research in understanding how systems for collaborative knowledge creation are impacted
+by events like this data migration are still in its early stages~\cite{moskaliuk2012collaborative},
+in particular for structured knowledge~\cite{horridge2014webprotege}.
+Most of the research is focused on Wikipedia~\cite{flock2015towards},
+which is understandable considering the availability of its data sets,
+in particular the whole edit history~\cite{schindler2011introducing}
+and the availability of tools for working with Wikipedia~\cite{milne2013open}.
+
+%Should also cover references (kvault) and quality.
 

### 2015-10-17 paper.tex
Addresses Jamie's comments or adds TODOs
Except the last ones about the analysis

@@
 Freebase is built on the notions of \emph{objects}, \emph{facts}, \emph{types}, and \emph{properties}.
-Each Freebase object has a~stable identifier called a~\emph{``mid''} (for Metaweb ID),
+Each Freebase object has a~stable identifier called a~\emph{``mid''} (for Machine ID),
 one or more types, and uses properties from these types in order to provide facts.
@@
 For example, a~small city in France was assigned an ISO country code,%
-\footnote{Freebase item page of the city of Saint-Martin: \url{http://www.freebase.com/m/03cc0d0}}
+\footnote{Freebase topic page of the city of Saint-Martin: \url{http://www.freebase.com/m/03cc0d0}}
 then Boston (the city in Massachusetts) had the type \texttt{/people/person},
@@
 put in relation to the number of facts per item.
+\todo{"There is no reference in the text to \autoref{fig:mapped-not-mapped}
+(which has a lot of subtle information in it.) It needs some real explanation." -- Jamie}
 
@@
 we map both the property that links the topic to the CVT
-and the main property of the CVT to the same Wikidata property, and during the mapping process
-pick the latter as the main property of the CVT.
+and the main property of the CVT to the same Wikidata property. Then, during the mapping process
+we pick the latter as the main property of the CVT \todo{Rewrite this sentence to be more understandable?}.
 For example, if we map the CVT shown in \autoref{fig:cvt-obama},
@@
 \subsection{Data Preparation}
+\todo{"the section seems to describe something more like a phased rollout or release plan than "data preparation"" -- Jamie}
 
@@
 in order to gather initial user feedback.
-In the following \todo{Weeks? Months?}, we progressively added more statements to the tool's database back-end.
+In the following months, we progressively added more statements to the tool's database back-end.
 Thereby, we were able to slowly upscale the tool's database back-end
@@
 or not yet visited.
-Statements can be grouped in ``datasets'' and ``uploads'' to
+Statements can be grouped in ``datasets'' (set of statements from the same origin)
+and ``uploads'' (set of statements uploaded at the same time) to
 distinguish data from different sources.\footnote{At the time of this writing,
@@
   \item 2,997M triples
-  \item 442M facts owned by Google%
+  \item 442M facts redistributable by Google\todo{Better formulation?}%
     \footnote{That is, the remaining Freebase triples

### 2015-10-17 paper.tex
Formulation
minor

--- 2015-10-17 paper.tex
@@
 Wikidata is published under the Creative Commons~0 (CC0~1.0)~\cite{cc0} license,
-which effectively puts the data in the public domain,
-whereas Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license
-and contains data imported from external projects not owned by Google,
-like images or descriptions extracted from Wikipedia.
-In consequence Google does not own the copyright of some parts of the content of the knowledge base,
+which effectively puts the data into the public domain.
+Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license.
+Google does not own the copyright of some parts of the content of the knowledge base,
 such as images or long entity descriptions extracted from Wikipedia.
-In a~first step, we filtered the Freebase dump for this kind of content
-before being able to create a~data dump that we could relicense under CC0~1.0.
-This step reduced the number of Freebase facts that could be republished by about 42M~facts
-from 3~billion facts in the original corpus.
+
+We filtered the Freebase dump by removing this kind of content
+before creating a~data dump that Google could relicense under CC0.
+This step reduced the number of Freebase facts that could be republished by about 42 million facts
+from 3~billion facts in the original corpus, i.e. by about $1.4\%$.
 
@@
 For these two specific cases, we have just kept the references from Freebase.
+\todo{Thomas, can you expand?}
+
 In order to provide the Wikidata community with references for the facts in Freebase,
-we have reused data from another Google research project
-called Knowledge Vault~\cite{dong2014knowledge} aimed at extracting facts from the Web.
-Whereas the fact extraction was usually correct, the pages Knowledge Vault extracted
-the references from often do not meet the Wikidata requirements for reliable references:
-they include pages in social networks, shopping sites, file sharing hosters, \emph{etc.}
+we have reused data from the Google
+Knowledge Vault~\cite{dong2014knowledge}. Knowledge Vault aims at extracting facts from the Web.
+
+The result of this step was surprising: 
+the fact extraction was usually correct, in the sense that the fact was indeed being stated on the page.
+Also the fact itself was usually accurate, in the sense that it corresponded to reality.
+But the pages the facts were extracted from in many cases did not meet
+the Wikidata requirements for reliable references:
+they include pages in social networks, reviews on shopping sites, file sharing hosters, \emph{etc.}
 It became necessary to filter the references before potential inclusion in Wikidata

### 2015-10-17 paper.tex

@@
   \item 2,997M triples
-  \item 442M facts owned by Google%
+  \item 442M unencumbered facts%
     \footnote{That is, the remaining Freebase triples

### 2015-10-17 paper.tex
section 3.3 to 3.5.2

@@
 and created the \emph{Primary Sources Tool},
-a~software solution that displays Freebase statements
-for verification to the user that can be added to the currently shown Wikidata item.
+a~widget that displays Freebase statements
+for curation by the contributor that can be added to the currently shown Wikidata item.
 The tool will be described in more detail in \autoref{sec:primary-sources-tool}.
@@
 
-The last challenge concerns the data mappings between Freebase topics and properties
+The next challenge concerns the data mappings between Freebase topics and properties
 and Wikidata items and properties.
@@
 who thus have decided to use it and further curate and maintain it by hand.
-It maps 1.15M~Freebase topics to their corresponding Wikidata items.
+It maps 1.15~million Freebase topics to their corresponding Wikidata items.
 A~second actively maintained mapping has been created by Samsung.%
@@
 as there are more wrong matches (often because there is no clear separation between topics
-and disambiguation pages in Wikipedia), however, the recall increases to 4.4M~links.
+and disambiguation pages in Wikipedia), however, the recall increases to 4.4~million~links.
 As we have shown in \autoref{sec:dataquality},
-human curation is required before importation anyway,
-which is why we have decided to merge the two mapping dumps,
-and for the resulting 6,000 conflicts decided to prioritize Google's mapping.
+human curation is required before import anyway,
+which is why we have decided to merge the two mapping dumps.
+For the 6,000 conflicts that appeared, we decided to prioritize Google's mapping.
 
@@
 To improve the result, we have also done some reconciliation based on third-party database IDs
-shared by Freebase and Wikidata, like MusicBrainz,\footnote{MusicBrainz: \url{https://musicbrainz.org}}
-VIAF,\footnote{VIAF: \url{http://viaf.org}} \emph{etc.}
-With this technique, we were able to match 800K~external database IDs,
-creating an additional mapping for 600K~topics---%
+shared by Freebase and Wikidata, like MusicBrainz~\cite{musicbrainz},
+VIAF~\cite{viaf}, \emph{etc.}
+With this technique, we were able to match 800,000~external database IDs,
+creating an additional mapping for 600,000~topics---%
 most of them already in the merged version of Google's and Samsung's mappings.
-Eventually, this reconciliation effort resulted in an additional 84K mapped items.
-We also used Google's Knowledge Graph~\cite{singhal2012} to add 100K~further mappings
+Eventually, this reconciliation effort resulted in an additional 84,000 mapped items.
+
+We also used Google's Knowledge Graph~\cite{singhal2012} to add 100,000 further mappings
 by also matching a~topic and an item if they share a~Wikipedia link with the Knowledge Graph item.
 There is some potential to add more data by looking at functional relations
-like ``father'' and ``mother'', but these relations only apply to relatively small sets of data
+like \textit{``father''} and \textit{``mother''},
+but these relations only apply to relatively small sets of data
 (like well known families), and the functional assumptions may run into some edge cases.
@@
 which may create cases where a~person has more than one male or female \texttt{/people/person/parents}.
+
 Eventually, with these four sources (Google mapping, Samsung mapping, external IDs, Knowledge Graph),
-we mapped 4.56M~items in total.
+we mapped 4.56~million items in total.
 

### 2015-10-17 paper.tex
Added exemplary works in the introduction.

--- 2015-10-17 paper.tex
@@
 natural language annotation, or translation.
-\todo{add references to papers with examples}
+Exemplary works are those of West \emph{et~al.}, who have proposed~\cite{west2014kb} a~way to
+leverage existing Web search based question-answering technology to
+fill in the gaps in knowledge bases in a~targeted way
+or those of Gesmundo and Hall~\cite{gesmundo2014kb}, who have trained
+a~syntactic parser paradigm that learns from large scale knowledge bases.
 

### 2015-10-17 paper.tex
section 3.5.3, spoke about Figure 3

--- 2015-10-17 paper.tex
@@
 One such collaborative knowledge base is Freebase,
-initially launched by Metaweb in 2007 and acquired by Google in 2010.
+publicly launched by Metaweb in 2007 and acquired by Google in 2010.
 Another example is Wikidata, a~collaborative knowledge base developed by
@@
 Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open and
-collaborative knowledge base created in 2007 by Metaweb and 
+collaborative knowledge base publicly launched in 2007 by Metaweb and 
 acquired in 2010 by Google~\cite{freebase}.
@@
 and the Knowledge Graph data described in the previous paragraph.
-Furthermore, the \emph{mapped} topics have an average number of facts of about~13.9,
+This is no surprise, since the core of both projects was kickstarted by using
+Wikipedia as a~repository of topics.
+
+The \emph{mapped} topics have an average number of 13.9~facts,
 whereas the topics that were \emph{not} mapped have an average number of only 5.7~facts.
@@
 (191K~non mapped topics \textit{vs.} 195K~mapped topics).
-This allows us to conclude that we have mapped the most important items of Freebase.
+This indicates that we have mapped the most important items of Freebase.
 \autoref{fig:mapped-not-mapped} provides an overview of mapped and non-mapped items
-put in relation to the number of facts per item.
-\todo{"There is no reference in the text to \autoref{fig:mapped-not-mapped}
-(which has a lot of subtle information in it.) It needs some real explanation." -- Jamie}
+put in relation to the number of facts per item: note that the Figure is log-scaled
+on both axes, so the seemingly small area between the two lines covers a majority of
+the topics. It can also be seen that there are a very small number of topics with
+a high number of facts which have not been covered (in the lower part of the Figure).
+These have all been manually inspected and found to be specific to the way knowledge
+in Freebase is built. The vast majority of items with more than ten facts - in the
+center of the Figure - has been mapped. The items that have not been mapped -
+visible in the upper left corner of the image - are very thin,
+i.e. mostly have a very small number of facts and
+would not have added much to the knowledge base.
 

### 2015-10-17 paper.tex
Section 3.5.3 and 3.6

@@
 
-\subsubsection{Mapping Completeness Analysis}
+\subsubsection{Topic Mapping Completeness Analysis}
 
@@
 
-For the mapping between Freebase and Wikidata properties, we have chosen to do it by hand
-with the help of the Wikidata community.
-With that, we have been able to quickly map around 360~properties
-(note that Wikidata has a~total of 1,863 properties, and Freebase has around 37,700 properties
-\todo{This should probably have a~date.}).
+For the mapping between Freebase and Wikidata properties, we have chosen to apply a~manual
+approach with the help of the Wikidata community.
+Note that a mapping of types is not needed, since Wikidata has no real notion of types
+(or, to be more specific, the property \textit{``instance of''} (P31) is just another
+property and connects to items without any special status).
+With the help of the community, we have been able to quickly map around 360~properties
+(note that Wikidata had a~total of about 1,800 properties at the time when this work
+has been conducted in the Summer of 2015, and Freebase has around 37,700 properties).
 For the mapping of properties where the domain are other topics or literals,
 this mapping provides the Wikidata property to use.
-We have also implemented a~special case for \texttt{/people/person/parents}
-in order to be able to map them to Wikidata properties ``father'' and ``mother''
-based on the person gender.
+
+For \texttt{/people/person/parents}, we have implemented a~special case
+in order to be able to map them to the Wikidata properties
+\textit{``father''} (P22) and \textit{``mother''} (P25)
+based on the person's gender.
+
 The mapping of CVTs (see \autoref{fig:cvt-obama}) is more complicated,
@@
 we map both the property that links the topic to the CVT
-and the main property of the CVT to the same Wikidata property. Then, during the mapping process
-we pick the latter as the main property of the CVT \todo{Rewrite this sentence to be more understandable?}.
+and the main property of the CVT to the same Wikidata property. In a second step, we
+then use merge these two mappings int a single Wikidata claim, on which we add the
+other properties from the CVT.
+
 For example, if we map the CVT shown in \autoref{fig:cvt-obama},
-we first use the Wikidata property \texttt{position held (P39)} to map
-\texttt{/politician/government\_positions\_held} and
-\texttt{/government\_position\_held/office\_position\_or\_title}.
-Second, for the qualifiers, we use \texttt{start time (P580)}
-for \texttt{/government\_position\_held/from} and \texttt{end time (P582)}
-for\linebreak \texttt{/government\_position\_held/to}.
-With the resulting property mapping, the created Wikidata statement
+we first use the Wikidata property \textit{``position held''} (P39) to map
+\texttt{/politician/government\_positions\_held} and \linebreak
+\texttt{/government\_position\_held/office\_position\_or\_title}. \linebreak
+Second, for the qualifiers, we use \textit{``start time''} (P580)
+for \texttt{/government\_position\_held/from} and \textit{``end time''} (P582)
+for \texttt{/government\_position\_held/to}.
+With the resulting \linebreak property mapping, the created Wikidata statement
 looks like the one presented in \autoref{fig:statement-obama}.
@@
 (encoded using XSD types~\cite{campbell2003xmlschema})
-to the Wikidata ``time'' datatype, however, filter out dates before 1920 that have
-a~higher precision than year because we do not know
+to the Wikidata ``time'' datatype. However, we remove dates before 1920 that have
+a~precision higher than year because we do not know
 if they are relative to the Julian or the Gregorian calendar.

### 2015-10-17 paper.tex
Improves 3.2

@@
 except for some specific data like populations and unemployment rates.
-For these two specific cases, we have just kept the references from Freebase.
-\todo{Thomas, can you expand?}
+For these two specific cases, we just map the ``\texttt{source}''
+\footnote{The two main properties used in Freebase for sources are
+\texttt{/measurement\_unit/dated\_integer/source} and
+\texttt{/measurement\_unit/dated\_percentage/source}}
+Freebase properties included the CVTs encoding these data into Wikidata references.
+\todo{Denny: Could you find a better formulation?}
 

### 2015-10-17 paper.tex
section 4 and 5

--- 2015-10-17 paper.tex
@@
 As outlined earlier, the \emph{Primary Sources Tool} is a~crowdsourced human curation
-software solution that displays Freebase statements for verification to the user
+software solution that displays Freebase statements for verification to the Wikidata contributor
 so that these statements can be added to the currently shown Wikidata item.
-With just one click, the user can reject or approve a~statement,
-and, in case of approval, therewith add the statement to Wikidata.
+With just one click, the contributor can reject or approve a~statement,
+and, in case of approval, add the statement to Wikidata.
 The code of the Primary Sources Tool is openly available
@@
 The tool is deployed as a~so-called gadget,
-\emph{i.e.}, as an easily activatable add-on feature in Wikidata.
+\emph{i.e.}, as an easily to active add-on feature in Wikidata.
 It is independent from Freebase and can easily be reused to import other datasets into Wikidata.
-Therefore, we have implemented an upload API in the back-end
+
+We have implemented an upload API in the back-end
 and a~dataset filter in the front-end that allows users
@@
 a~dataset extracted from natural language text.
-To visualize the migration progress, we have created a~realtime dashboard
-available publicly at \url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}.
+We expect more datasets to be added to the Primary Sources Tool in the future.
+
 At the time of writing (October, 2015), the tool has been used by more than a~hundred users
 who performed about 30,000 approval or rejection actions.
-More than 12M~statements have been uploaded in total.
+More than 12~million statements have been uploaded in total.
 \autoref{fig:primary-sources-tool} shows two screenshots
 of the tool that integrates nicely with the Wikidata user interface.
+To visualize the migration progress, we have created a~realtime dashboard.%
+\footnote{Primary Sources Dashboard:
+\url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}}
 
@@
 
-\subsection{Data Preparation}
-\todo{"the section seems to describe something more like a phased rollout or release plan than "data preparation"" -- Jamie}
-
-In order to prepare the data for integration into the Primary Sources Tool,
-we have created a~set of scripts which map the content
-of the last Freebase dump to Wikidata statements.%
-\footnote{The source code is available under the terms of the Apache~2.0 license:
-\url{https://github.com/google/freebase-wikidata-converter}}
-The Primary Sources Tool was developed in parallel with the mapping tool.
-We first created a~small dataset of around 1M statements
-based on few select properties (\emph{e.g.}, \texttt{/people/person/birth\_place})
-and deployed both the first dataset and a~basic version of the tool
-in order to gather initial user feedback.
-In the following months, we progressively added more statements to the tool's database back-end.
-Thereby, we were able to slowly upscale the tool's database back-end
-without risking back-end performance bottlenecks.
-The process of adding data in small batches of 1M~to~2M statements per batch
-further allowed us to detect some potential issues in the front-end
-and fix them before they became actual problems.
-Another positive side-effect of this approach was that it allowed us to gather quick feedback
-from the community about the already mapped data and thus to adapt the mapping scripts easily
-and correct minor issues with the data early on in the back-end.
-Upon approval or rejection of either a~claim or a~reference,
-the Wikidata item page in question reloads in order to reflect
-the potentially changed state of the migration, as,
-in case of incoming claims with references, freshly accepted claims 
-can require incoming references to be attached elsewhere in the hierarchy.
-
-\subsection{Back-end of the Tool}
-
-The objective of the back-end was to have a~REST API allowing us
-to serve data efficiently to the front-end of the tool and
-providing statistical data about the approvals and rejections done over time.
-As the resources of the Wikimedia Foundation are limited,
-the back-end was implemented in highly optimized C++
-and runs as a~FastCGI application in the lighttpd Web server.
 \autoref{fig:architecture} shows the overall architecture of the Primary Sources tool.
+In the following, we describe the back-end, the front-end, and the chosen data rollout plan.
 
@@
 
-Entities and statements are stored in a~relational database (MySQL or SQLite)
+\subsection{Back-end}
+
+The objective of the back-end was to have a~REST API allowing us
+to serve data efficiently to the front-end of the tool and
+providing statistical data about the approvals and rejections done over time.
+As the resources of the Wikimedia Foundation are limited,
+the back-end was implemented in highly optimized C++
+and runs as a~FastCGI application in the lighttpd Web server.
+
+Entities and statements are stored in a~relational database
+(first SQLite, later migrated to MariaDB)
 and follow the Wikidata data structure with an additional status field
@@
 Statements can be grouped in ``datasets'' (set of statements from the same origin)
-and ``uploads'' (set of statements uploaded at the same time) to
+and ``uploads'' (set of statements uploaded at the same time) in order to
 distinguish data from different sources.\footnote{At the time of this writing,
@@
 
-\subsection{Front-end of the Tool}
+\subsection{Front-end}
 
-For the front-end, our objective was to make the migration process
+For the front-end, our objective was to model the migration process
 as close to the natural Wikidata editing flow as possible.
@@
 when navigating Wikidata.
+
 To achieve this, we have in a~first step created a~Wikidata \emph{user script}.
@@
 User scripts can be created by anyone and might not always be stable.
+
 Once a~user script has matured, it can be converted into a~\emph{gadget}.
@@
 They can only be edited by administrators and are assumed to be stable.
+
 With our front-end, we went through this maturation steps
@@
 Existing Wikidata statements are shown as usual,
-Freebase facts that could potentially be imported into Wikidata are shown in light blue
-with instead of an ``edit'' button two new buttons ``approve reference'' and ``reject reference''
+Freebase facts that could potentially be imported into Wikidata are shown in light blue.
+Instead of an ``edit'' button they feature two new buttons,
+``approve reference'' and ``reject reference''
 (\autoref{fig:barack-obama}) or ``approve claim'' and ``reject claim''
 (\autoref{fig:cause-of-death}) respectively.
+
+\subsection{Data Rollout}
+
+In order to prepare the data for integration into the Primary Sources Tool,
+we have created a~set of scripts which map the content
+of the last Freebase dump to Wikidata statements.%
+\footnote{The source code of theses scripts is also available under the terms of the Apache~2.0 license:
+\url{https://github.com/google/freebase-wikidata-converter}}
+The Primary Sources Tool was developed in parallel with the mapping scripts.
+We first created a~small dataset of around 1 million statements
+based on few select properties (\emph{e.g.}, \texttt{/people/person/birth\_place})
+and deployed both the first dataset and a~basic version of the tool
+in order to gather initial user feedback.
+
+In the following months, we progressively added more statements to the tool's database back-end.
+Thereby, we were able to slowly upscale the tool's database back-end
+without risking back-end performance bottlenecks.
+The process of adding data in small batches of 1~million to 2~million statements per batch
+further allowed us to detect some potential issues in the front-end
+and fix them before they became actual problems.
+Another positive side-effect of this approach was that it allowed us to gather quick feedback
+from the community about the already mapped data and thus to adapt the mapping scripts early
+and correct minor issues with the data in the back-end.
+
+Upon approval or rejection of either a~claim or a~reference,
+the Wikidata item page in question reloads in order to reflect
+the potentially changed state of the migration, as,
+in case of incoming claims with references, freshly accepted claims 
+can require incoming references to be attached elsewhere in the item.
 
@@
 In order to put the statistics in this section in context,
-in the following we provide an overview of the size of the last dump of Freebase
+we first provide an overview of the size of the last dump of Freebase
 from March 2015:
@@
   \setlength\itemsep{0em}
-  \item 48M~topics
-  \item 2,997M triples
-  \item 442M unencumbered facts%
-    \footnote{That is, the remaining Freebase triples
-      after filtering out data about IDs (\texttt{/type/object/id}),
-      types (\texttt{/type/object/type}), labels, descriptions (\texttt{/type/object/name},
-      \texttt{/common/topic/description}, \emph{etc.}), and triples removed
-      for licensing (see \autoref{sec:licensing})}
-  \item 68M~labels
+  \item 48~million topics
+  \item 2,997~million triples
+  \item 442~million ``useful'' facts%
+  \item 68~million labels
 \end{itemize}
 
-As a~direct comparison, below the raw statistics for Wikidata as of August 2015
-that make the differences in pure size between the two knowledge bases quite evident.
+``Useful'' facts are the triples that remain 
+after filtering out all triples about IDs (\texttt{/type/object/id}),
+types \linebreak (\texttt{/type/object/type}), labels, descriptions \linebreak
+(\texttt{/type/object/name},
+\texttt{/common/topic/description}, \emph{etc.}), \linebreak and triples removed
+for licensing reasons (the latter were about 42~million, see \autoref{sec:licensing}).
+The triples removed in this step are not considered to be potentially useful for
+Wikidata, since IDs, labels, and descriptions are not handled through statements.
+
+As a~direct comparison, here are the raw statistics for Wikidata as of August 2015.
 
@@
     \setlength\itemsep{0em}
-    \item 14.5M~items
-    \item 66M~statements
-    \item 82M~labels
+    \item 14.5~million items
+    \item 66~million statements
+    \item 82~million labels
 \end{itemize}
@@
 \url{https://www.wikidata.org/wiki/Wikidata:Notability}}
-For example, Freebase holds data about 11.3M~musical recordings,
-8.3M~music canonical versions, 2.6M~ISBNs, \emph{etc.} that are not contained in Wikidata.
+For example, Freebase holds data about 11.3~million musical recordings,
+8.3~million music canonical versions, 2.6~million ISBNs, \emph{etc.} that are not contained in Wikidata.
+
 We also cannot compare the number of facts and the number of statements directly,
@@
 For example, the property \texttt{/people/person/place\_of\_birth} has the corresponding
-reverse property \texttt{/location/location/people\_born\_here}
+reverse property \linebreak \texttt{/location/location/people\_born\_here}
 that encodes exactly the same semantic information.
 Such reverse properties sometimes exist in Wikidata
-(like \texttt{children} for \texttt{father} and \texttt{mother}),
-but are far less common.
+(like \textit{``children''} for \textit{``father''} and \textit{``mother''}),
+but are far less common and also not automatically handled.
+
 Another point is that CVTs use a~lot of facts to convey the exact same information
@@
 For example, to encode that Barack Obama is the president
-of the United States as of June~20, 2009,
+of the United States since January~20, 2009,
 Freebase requires more than six facts as shown in \autoref{fig:cvt-obama}.
@@
 by removing sources, representing statements with qualifiers using CVTs,
-and adding reverse properties, this would lead to 110M facts,
-\emph{i.e.}, 167\% of the raw number of statements.
+and adding reverse properties, this would lead to a number of 110~million facts,
+\emph{i.e.} an increase of 167\% over the raw number of statements.
+The representation of Wikidata in RDF and its impact on the number of triples
+is discussed in more detail in~\cite{reification-wikidata}.
+
 In a~considerable amount of cases, Freebase also contains duplicate data.
 For example, many cities in the United States have duplicate CVTs for the population,
-where the only change is the encoding of the source.
+where the only difference is the encoding of the source.
 
@@
 that is shown in \autoref{fig:time-space}.
-The used method is to extract the earliest date and the longitude
-linked to each of the entities of the two knowledge bases
-and propagate them to the connected entities that do not have such data.
+
+We extracted the earliest date and the longitude
+linked to each of the entities of the two knowledge bases.
+We then propagated them to the connected entities that do not have such data.
 To implement this propagation, we set as value (date or longitude)
 the average of the values of the entities whose distance is $<10$
-with $2^{-d}$ as weighting, $d$~being the distance between the two entities.
-We see that the two knowledge bases follow the same basic patterns,
-with their coverage mostly concentrated on Europe and North America.
+with a weight of $2^{-d}$ (with $d$~being the distance between the two entities).
+
+We see that the two knowledge bases display the same basic patterns,
+with their coverage mostly concentrated on the longitudes of Europe and North America.
 There are no strong differences between them,
-yet coverage of \mbox{\emph{post}-year-2000} entities seems better in Freebase.
-Our theory is that this is \emph{(i)}~due to the absence of a~lot of musical data in Wikidata
-that in contrast is present in Freebase,
+yet coverage of \mbox{\emph{post}-year-2000} entities seems stronger in Freebase.
+
+Our theory is that this is
+\emph{(i)}~due to the absence of a~lot of musical data in Wikidata that is present in Freebase,
 and \emph{(ii)} due to the US population CVTs in Freebase.
-The big horizontal lines in \autoref{fig:freebase} and more even in \autoref{fig:wikidata}
+
+The big horizontal lines in \autoref{fig:freebase} and even more in \autoref{fig:wikidata}
 can most probably be traced back to places that do not have any linked date,
@@
 and the one covering Russia around 850.
+
 One possible conclusion from this visualization could be that Wikidata,
@@
 and good metrics of success for the migration.
-We certainly note that for knowledge bases the amount of triples is not an adequate measure
-to judge the proportion of additional good data.
+We certainly can note that for data sets to be added to a knowledge bases,
+the raw number of triples is not an adequate measure of quality.
 
@@
 
-From the Freebase dump, we have been able to create more than 17M~Wikidata claims
-(\emph{i.e.}, statements without references), including 1.5M~IDs.
-For that, we have used 31M~Freebase facts.
-With additional references, we obtain 19.6M~statements, and, after removing 1M~duplicates
-and facts already contained in Wikidata, we obtain 14M~new statements.
-Thus, if all these statements were added to Wikidata,
-this would lead to a~21\% increase of the number of statements in Wikidata.
-This raises the question why these numbers are so low compared to the size of Freebase.
-We argue that the main reason is that we have only mapped 4.56M~items to Wikidata,
-\emph{i.e.}, only 9.5\% of Freebase's topics in total, which are the subject of only 64M~facts.
-Even under ideal circumstances, we cannot map more than 64M~statements,
-and this is assuming that we could map all reverse properties, which, in fact, we could not.
+From the Freebase dump, we have been able to create more than 17~million Wikidata claims
+(\emph{i.e.}, statements without references), including 1.5~million IDs.
+For that, we have used 31~million Freebase facts.
+Including the references, we obtain 19.6~million statements, and, after removing duplicates
+and facts already contained in Wikidata, we obtain 14~million new statements.
+
+If all these statements were added to Wikidata,
+we would see a~21\% increase of the number of statements in Wikidata.
+
+This raises the question why these numbers are so low compared to the size of Freebase, given at
+3~billion facts.
+The main reason is that we have only mapped 4.56~million items to Wikidata,
+\emph{i.e.}, only 9.5\% of Freebase's topics in total.
+The mapped topics are the subject of only 64~million facts.
+So even under otherwise ideal circumstances, we cannot map more than 64~million statements.
+This assumes that we could map all reverse properties, which, in fact, we could not.
 So leaving aside the not mapped topics, we have created a~statement for more than 24\% of the facts.
-If we restrict ourselves to reviewed facts---a~set of 1.6M~human curated facts---we have far better results.
-There are 0.58M~facts whose subjects are mapped to Wikidata, and 0.52M~of them
+
+If we restrict ourselves to reviewed facts---a~set of
+1.6~million human curated facts---we have far better results.
+Of the human curated facts, 0.58~million facts have their subject mapped to Wikidata.
+Based on our property mappings, 0.52~million of these facts
 (\emph{i.e.}, 92\%) are converted to Wikidata statements.
-58\% of the statements created from reviewed fact are already in Wikidata,
-allowing us to add 0.25M~of new reviewed statements to Wikidata.
+Finally, 58\% of the statements created from reviewed fact are already in Wikidata,
+allowing us to add 0.25~million new reviewed statements to Wikidata.
 
@@
 
-We reckon that the most improvements can be achieved
-by extending the migration to more Freebase topics
-by suggesting Wikidata users to create new Wikidata items.
+The largest gains for the migration can be achieved
+by extending the mapping to more Freebase topics.
 A~possible way of realizing this is to create a~user interface%

### 2015-10-17 paper.tex
section 7

@@
 In order to suggest interesting topics to add to Wikidata,
-we could rank the not mapped yet topics per number of incoming links
+we could rank the topics that are not mapped yet by the number of incoming links
 from already mapped topics and filter less interesting types like ISBNs.
+
 Another area for improvement is to upload high quality datasets using a~bot,
@@
 like birth date, death place or gender using a~bot.
-We have also begun to import labels that are in Freebase and are absent from Wikidata.
-In the 17.2M~Freebase labels for mapped topics, only 0.9M, \emph{i.e.}, 5\%, are missing in Wikidata.
+We have also started to import labels that are in Freebase and are absent from Wikidata.
+In the 17.2~million Freebase labels for mapped topics,
+only 0.9~million, \emph{i.e.}, 5\%, are missing in Wikidata.
 
 Concluding, in a~fairly short amount of time, we have been able
-to provide to the Wikidata community more than\linebreak 14M~new Wikidata statements
-using a~novel customizable and generalizable software solution called Primary Sources Tool
-that is well integrated into the Wikidata user interface.
+to provide to the Wikidata community more than\linebreak 14~million new Wikidata statements
+using a~customizable and generalizable approach, consisting of data preparation scripts
+and the Primary Sources Tool,
+which is well integrated into the Wikidata user interface.
 The effort needed to map two fairly different knowledge bases has also been a~good occasion
-to highlight the difficulty of having good metrics to measure the size
-and in consequence the ``value'' of such collaborative knowledge bases.
-We envision that this project now with Freebase, and for even more datasets in the future,
-will facilitate to increase the completeness of Wikidata.
+to highlight the difficulty of having good metrics to measure the size of knowledge bases
+in a meaningful way, 
+and, in consequence, the ``value'' of such collaborative knowledge bases and the datasets added to them.
+We hope that with the help of the Primary Sources Tool and
+the Freebase dataset, and in future also other datasets,
+will increase the completeness and accuracy of Wikidata.
 

### 2015-10-18 paper.tex
comments from danbri

@@
 Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
-Due to the success of Wikidata, Google announced in 2014 to shut down Freebase and
+Due to the success of Wikidata, Google announced in 2014 their intent to shut down Freebase and
 help the community with the transfer of Freebase's content to Wikidata~\cite{freebase2014shutdown}.
@@
 Due to the success of Wikidata,
-Google announced in 2014 to close Freebase and offer most of its content to the
-Wikidata community~\cite{freebase2014shutdown,freebase-end}.
+Google announced in 2014 its intent to close Freebase and help with
+the migration of the content to Wikidata~\cite{freebase2014shutdown,freebase-end}.
 
@@
 except for some specific data like populations and unemployment rates.
-For these two specific cases, we just map the ``\texttt{source}''
+For these two specific cases, we map the Freebase properties describing sources,%
 \footnote{The two main properties used in Freebase for sources are
@@
 \texttt{/measurement\_unit/dated\_percentage/source}}
-Freebase properties included the CVTs encoding these data into Wikidata references.
-\todo{Denny: Could you find a better formulation?}
+expressed as CVTs, into Wikidata references on the appropriate claim.
 
@@
 
-The data quality of Freebase was examined thoroughly by the Wikidata community
-and anecdotal evidence indeed confirmed that there were certain challenges.
+The data quality of Freebase was discussed by the Wikidata community, and it
+was decided that the quality overall was not sufficient for a direct import.
 For example, a~small city in France was assigned an ISO country code,%
@@
 whereas for the Freebase to Wikidata mapping every single results is expected to be curated.
+The schema.org structured data project is also exploring mappings to and from Wikidata,
+to facilitate the use of Wikidata's vocabulary as schema.org markup across the wider Web.
+This involves similar issues mapping schema.org's CVT-like statement qualification mechanism, Roles,
+to Wikidata conventions.%
+\footnote{On Roles: \url{http://schema.org/Role}. Mappings from Schema.org to Wikidata:
+\url{https://github.com/schemaorg/schemaorg/issues/280}. On the interaction of Schema.org
+and Wikidata: \url{https://meta.wikimedia.org/wiki/Wikidata/Notes/Schema.org_and_Wikidata}}
 

### 2016-01-07 paper.tex
Make sure figure 7 is part of the text
grammar fix
Update statistics based on current numbers

@@
 Sebastian Schaffert\\
-   \affaddr{Google, Zurich, Switzerland}\\   
+   \affaddr{Google, Zürich, Switzerland}\\   
    \email{schaffert@google.com}
@@
 The tool is deployed as a~so-called gadget,
-\emph{i.e.}, as an easily to active add-on feature in Wikidata.
+\emph{i.e.}, as an easy to active add-on feature in Wikidata.
 It is independent from Freebase and can easily be reused to import other datasets into Wikidata.
@@
 
-At the time of writing (October, 2015), the tool has been used by more than a~hundred users
-who performed about 30,000 approval or rejection actions.
-More than 12~million statements have been uploaded in total.
+At the time of writing (January, 2016), the tool has been used by more than a~hundred users
+who performed about 90,000 approval or rejection actions.
+More than 14~million statements have been uploaded in total.
 \autoref{fig:primary-sources-tool} shows two screenshots
@@
 
-\begin{figure*}[h]
+\begin{figure*}[t!]
     \centering

### 2016-01-13 paper.tex
Switch to home made statement schema in order to simplify the legal process

@@
 The claim itself is composed of one main property--value pair that encodes
-the main (claimed) fact like ``population is 8,173,900'' and optional qualifiers
-to add information about it like ``as of June 2012''.
+the main (claimed) fact like ``taxon name is Pantera Leo'' and optional qualifiers
+to add information about it like ``taxon author is Carl Linnaeus''.
 \autoref{fig:statement} illustrates the used terminology with an example.
@@
   \centering
-  \includegraphics[width=8.45 cm]{img/Wikidata_statement.pdf}
-  \caption{Wikidata terminology illustrated with an example (Source:
-	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg}).}
+  \includegraphics[width=8.45 cm]{img/wikidata-statement-schema.pdf}
+  \caption{Wikidata statement terminology illustrated with an example.}
   \label{fig:statement}

### 2016-01-29 paper.tex
Uses the final stylesheet and adds the copyright text
Fixed lonely orphan 'a'-s and added the permission statement.

@@
-%\documentclass{sig-alternate}
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate-2013}
 
@@
 }
+
+\permission{Copyright is held by the International World Wide Web Conference
+Committee (IW3C2). IW3C2 reserves the right to provide a~hyperlink to the
+author's site if the Material is used in electronic media.}
+\conferenceinfo{WWW 2016,}{April 11--15, 2016, Montr\'eal, Qu\'ebec, Canada.}
+\copyrightetc{ACM \the\acmcopyr}
+\crdata{978-1-4503-4143-1/16/04. \\
+\url{http://dx.doi.org/10.1145/2872427.2874809}}
+
+\clubpenalty=10000
+\widowpenalty = 10000
+
 \begin{document}
@@
 % \category{CR number}{category}{sub-category}[optional subject descriptor]
-\category{H.3.5}{Information Storage and Retrieval}{Online Information Systems}
-\category{H.5.3}{Information Interfaces}{Group and Organization Interfaces}[Web-based interactions]
-\category{I.2.4}{Artificial Intelligence}{Knowledge Representation}
-\category{K.4.3}{Computers and Society}{Organizational Impacts}[Com\-puter-supported collaborative work]
+% \category{H.3.5}{Information Storage and Retrieval}{Online Information Systems}
+% \category{H.5.3}{Information Interfaces}{Group and Organization Interfaces}[Web-based interactions]
+% \category{I.2.4}{Artificial Intelligence}{Knowledge Representation}
+% \category{K.4.3}{Computers and Society}{Organizational Impacts}[Com\-puter-supported collaborative work]
 
@@
 and the type \texttt{/government/us\_president} (among others) that allows the entity to have
-a fact with the property \texttt{/government/us\_president/presidency\_number} \linebreak
+a~fact with the property \texttt{/government/us\_president/presidency\_number} \linebreak
 and the literal integer ``44'' as the value.
@@
 The data quality of Freebase was discussed by the Wikidata community, and it
-was decided that the quality overall was not sufficient for a direct import.
+was decided that the quality overall was not sufficient for a~direct import.
 For example, a~small city in France was assigned an ISO country code,%
@@
 put in relation to the number of facts per item: note that the Figure is log-scaled
-on both axes, so the seemingly small area between the two lines covers a majority of
-the topics. It can also be seen that there are a very small number of topics with
-a high number of facts which have not been covered (in the lower part of the Figure).
+on both axes, so the seemingly small area between the two lines covers a~majority of
+the topics. It can also be seen that there are a~very small number of topics with
+a~high number of facts which have not been covered (in the lower part of the Figure).
 These have all been manually inspected and found to be specific to the way knowledge
@@
 visible in the upper left corner of the image - are very thin,
-i.e. mostly have a very small number of facts and
+i.e. mostly have a~very small number of facts and
 would not have added much to the knowledge base.
@@
 approach with the help of the Wikidata community.
-Note that a mapping of types is not needed, since Wikidata has no real notion of types
+Note that a~mapping of types is not needed, since Wikidata has no real notion of types
 (or, to be more specific, the property \textit{``instance of''} (P31) is just another
@@
 we map both the property that links the topic to the CVT
-and the main property of the CVT to the same Wikidata property. In a second step, we
-then use merge these two mappings int a single Wikidata claim, on which we add the
+and the main property of the CVT to the same Wikidata property. In a~second step, we
+then use merge these two mappings int a~single Wikidata claim, on which we add the
 other properties from the CVT.
@@
 The Primary Sources Tool was developed in parallel with the mapping scripts.
-We first created a~small dataset of around 1 million statements
+We first created a~small dataset of around 1~million statements
 based on few select properties (\emph{e.g.}, \texttt{/people/person/birth\_place})
@@
 by removing sources, representing statements with qualifiers using CVTs,
-and adding reverse properties, this would lead to a number of 110~million facts,
+and adding reverse properties, this would lead to a~number of 110~million facts,
 \emph{i.e.} an increase of 167\% over the raw number of statements.
@@
 the average of the values of the entities whose distance is $<10$
-with a weight of $2^{-d}$ (with $d$~being the distance between the two entities).
+with a~weight of $2^{-d}$ (with $d$~being the distance between the two entities).
 
@@
 and good metrics of success for the migration.
-We certainly can note that for data sets to be added to a knowledge bases,
+We certainly can note that for data sets to be added to a~knowledge bases,
 the raw number of triples is not an adequate measure of quality.
@@
 mostly individually evaluated by human contributors
-(therefore not requiring a perfect mapping).
+(therefore not requiring a~perfect mapping).
 The effort most similar to ours is the DBpedia Mapping Wiki~\cite{lehmann2014dbpedia}.
@@
 The main difference is that the DBpedia mapping is running continuously
-and does not allow for point-fixes, thus necessitating a higher quality of the mapping,
+and does not allow for point-fixes, thus necessitating a~higher quality of the mapping,
 whereas for the Freebase to Wikidata mapping every single results is expected to be curated.
@@
 both Freebase and Wikidata have historically been bootstrapped by using Wikipedia.
-Wikipedia is often used as a benchmark for entity mapping systems~\cite{entitylinkingwikipedia}.
+Wikipedia is often used as a~benchmark for entity mapping systems~\cite{entitylinkingwikipedia}.
 As described in \autoref{subsec:topic-mappings} this lead to sufficiently good results for the head,
@@
 to highlight the difficulty of having good metrics to measure the size of knowledge bases
-in a meaningful way, 
+in a~meaningful way,
 and, in consequence, the ``value'' of such collaborative knowledge bases and the datasets added to them.

### 2016-01-29 paper.tex
Fixed the bibliography.
Reworked Abstract.

@@
 \usepackage{gensymb}
+\usepackage[super]{nth}
 % todo macro
@@
 are central for the data strategy of many projects and organizations.
-The two major collaborative knowledge bases are Google's Freebase and Wikimedia's Wikidata.
+The two major collaborative knowledge bases are Wikimedia's Wikidata and Google's Freebase.
 Due to the success of Wikidata, Google decided in 2014 to offer the content of Freebase
 to the Wikidata community.
-In this paper, we describe the ongoing transfer efforts and data mapping challenges,
+In this paper, we report on the ongoing transfer efforts and data mapping challenges,
 and provide an analysis of the effort so far.
@@
 
-\keywords{Crowdsourcing systems, Semantic Web, Wikidata, Freebase}
+\keywords{Crowdsourcing Systems, Semantic Web, Wikidata, Freebase}
 

### 2016-01-29 paper.tex
Reworked Section 1.

@@
 natural language annotation, or translation.
-Exemplary works are those of West \emph{et~al.}, who have proposed~\cite{west2014kb} a~way to
-leverage existing Web search based question-answering technology to
-fill in the gaps in knowledge bases in a~targeted way
-or those of Gesmundo and Hall~\cite{gesmundo2014kb}, who have trained
-a~syntactic parser paradigm that learns from large scale knowledge bases.
+Exemplary works are those of West \emph{et~al.}, who in~\cite{west2014kb} have proposed a~way to
+leverage Web search-based question answering technology to
+fill in the gaps in knowledge bases in a~targeted way,
+or research of Gesmundo and Hall~\cite{gesmundo2014kb}, who have trained
+a~syntactic parser paradigm that learns from large-scale knowledge bases.
 
@@
 publicly launched by Metaweb in 2007 and acquired by Google in 2010.
-Another example is Wikidata, a~collaborative knowledge base developed by
+Another example is Wikidata, a~collaborative know\-ledge base developed by
 Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
 Due to the success of Wikidata, Google announced in 2014 their intent to shut down Freebase and
-help the community with the transfer of Freebase's content to Wikidata~\cite{freebase2014shutdown}.
+help the community with the transfer of Freebase content to Wikidata~\cite{freebase2014shutdown}.
 
@@
 
-The paper is structured as follows.
+The remainder of this paper is structured as follows.
 First, we introduce Freebase and Wikidata in \autoref{sec:background}.

### 2016-01-29 paper.tex
Reworked Section 2.1.

@@
 Freebase uses Compound Value Types (CVTs) to represent
-n-ary relations with $n>2$, \emph{e.g.}, values like geographic coordinates,
+$n$-ary relations with $n>2$, \emph{e.g.}, values like geographic coordinates,
 political positions held with a~start and an end date (see \autoref{fig:cvt-obama} for an example),
@@
 CVT values are just objects, \emph{i.e.}, they have a~mid and can have types
-(although they usually have only the compound value type itself).
+(although they usually only have the compound value type itself).
 Most non-CVT objects are called \emph{topics} in order to discern them from CVTs.
@@
 When Freebase was turned read-only on March~31, 2015,
-it counted more than 3~billion facts about almost 50M~entities.
-The data from Freebase is published as an N-Triples dump in RDF~\cite{rdf} under
+it counted more than 3~billion facts about almost 50~million entities.
+Freebase data is published as an N-Triples dump in RDF~\cite{rdf} under
 the Creative Commons CC-BY license.\footnote{Dump: \url{https://developers.google.com/freebase/data}}

### 2016-01-29 paper.tex
Reworked Section 2.2.

@@
 launched in October 2012 and hosted by the Wikimedia Foundation~\cite{vrandevcic2014wikidata}.
-Its community has been growing quickly, and as of mid 2015,
+Its community has been growing quickly, and as of mid-2015,
 the community comprises about 6,000 active contributors~\cite{wikidatastats}.
@@
 Contrary to Freebase, Wikidata statements do not aim to encode true facts,
-but \emph{claims} from different sources, which can also contradict each other.
+but \emph{claims} from different sources, which can also contradict each other,
+which, for example, allows for border conflicts to be expressed
+from different political points of view.
 
@@
 The content of Wikidata is in the public domain under Creative Commons CC0.
-As of September 2015, Wikidata counted about 70M~statements on 18M~entities.
+As of September 2015, Wikidata counted about 70~million statements on 18~million entities.
 A~more in-depth comparison between Freebase, Wikidata, and other free and open knowledge bases

### 2016-01-29 paper.tex
Reworked Section 3.1.

@@
 such as images or long entity descriptions extracted from Wikipedia.
-
 We filtered the Freebase dump by removing this kind of content
@@
 This step reduced the number of Freebase facts that could be republished by about 42 million facts
-from 3~billion facts in the original corpus, i.e. by about $1.4\%$.
+from 3~billion facts in the original corpus, \emph{i.e.}, by about $1.4\%$.
 

### 2016-01-29 paper.tex
Reworked Section 3.2.

@@
 expressed as CVTs, into Wikidata references on the appropriate claim.
-
 In order to provide the Wikidata community with references for the facts in Freebase,
@@
 the Wikidata requirements for reliable references:
-they include pages in social networks, reviews on shopping sites, file sharing hosters, \emph{etc.}
+they include pages from online social network sites, reviews on shopping sites, file sharing hosters, \emph{etc.}
 It became necessary to filter the references before potential inclusion in Wikidata

### 2016-01-29 paper.tex
Reworked Section 3.3.

@@
 \footnote{Freebase topic page of the city of Saint-Martin: \url{http://www.freebase.com/m/03cc0d0}}
-then Boston (the city in Massachusetts) had the type \texttt{/people/person},
+Boston (the city in Massachusetts) had the type \texttt{/people/person},
 and several other occurrences of data quality issues were revealed.

### 2016-01-29 paper.tex
Reworked Section 3.4.

@@
 
-\subsection{Long-term maintenance}
+\subsection{Long-Term Maintenance}
 \label{sec:longtermmaintenance}
@@
 or provision of tools to assist the existing editors to allow them to be more effective. With the
-Primary Sources Tool, we aim to help grow the community in step with the amount of data. It is
-useful as a~means to get more people to edit because it lowers the barrier to entry. It does this
-by making it easier to find potential edits. At the same time, it helps make some of the existing
-editors more effective by allowing them to add statements with a~single click.
+\emph{Primary Sources Tool}, we aim at helping grow the community in step with the amount of data. It is
+useful as a~means to get more people to edit, as it lowers the barrier to entry by
+making it easier to find potential edits. At the same time, it helps make some of the existing
+editors more efficient by allowing them to add statements with a~single click.
 

### 2016-01-29 paper.tex
Reworked Section 3.5.x.

@@
 
-The next challenge concerns the data mappings between Freebase topics and properties
+The next challenge concerns the data mappings between Freebase topics and properties,
 and Wikidata items and properties.
@@
 It maps 1.15~million Freebase topics to their corresponding Wikidata items.
+
 A~second actively maintained mapping has been created by Samsung.%
@@
 even if there is only a~single shared Wikipedia link.
-The precision of the mapping is naturally lower compared to Google's mapping
+The precision of the mapping is naturally lower compared to Google's mapping,
 as there are more wrong matches (often because there is no clear separation between topics
 and disambiguation pages in Wikipedia), however, the recall increases to 4.4~million~links.
+
 As we have shown in \autoref{sec:dataquality},
@@
 With this technique, we were able to match 800,000~external database IDs,
-creating an additional mapping for 600,000~topics---%
+creating an additional mapping for 600,000~to\-pics---%
 most of them already in the merged version of Google's and Samsung's mappings.
@@
 
-We also used Google's Knowledge Graph~\cite{singhal2012} to add 100,000 further mappings
+We also used Google's Knowledge Graph~\cite{singhal2012} to add about 100,000 further mappings
 by also matching a~topic and an item if they share a~Wikipedia link with the Knowledge Graph item.
@@
 These have all been manually inspected and found to be specific to the way knowledge
-in Freebase is built. The vast majority of items with more than ten facts - in the
-center of the Figure - has been mapped. The items that have not been mapped -
-visible in the upper left corner of the image - are very thin,
-i.e. mostly have a~very small number of facts and
+in Freebase is modeled. The vast majority of items with more than ten facts---in the
+center of the Figure---has been mapped. The items that have not been mapped---%
+visible in the upper left corner of the image---are very thin,
+\emph{i.e.}, mostly have a~very small number of facts and
 would not have added much to the knowledge base.

### 2016-01-29 paper.tex
Reworked Section 3.6.

@@
 There is some potential to add more data by looking at functional relations
-like \textit{``father''} and \textit{``mother''},
+like \texttt{father} and \texttt{mother},
 but these relations only apply to relatively small sets of data
@@
 Note that a~mapping of types is not needed, since Wikidata has no real notion of types
-(or, to be more specific, the property \textit{``instance of''} (P31) is just another
+(or, to be more specific, the property \texttt{instance of} (P31) is just another
 property and connects to items without any special status).
 With the help of the community, we have been able to quickly map around 360~properties
-(note that Wikidata had a~total of about 1,800 properties at the time when this work
-has been conducted in the Summer of 2015, and Freebase has around 37,700 properties).
+(note that Wikidata had a~total of about 1,800 properties in the summer of 2015 when this work
+was conducted, and Freebase had around 37,700 properties).
 For the mapping of properties where the domain are other topics or literals,
@@
 
-For \texttt{/people/person/parents}, we have implemented a~special case
-in order to be able to map them to the Wikidata properties
-\textit{``father''} (P22) and \textit{``mother''} (P25)
+For \texttt{/people/person/parents}, we implemented a~special case
+in order to map them to the Wikidata properties
+\texttt{father} (P22) and \texttt{mother} (P25)
 based on the person's gender.
 
-The mapping of CVTs (see \autoref{fig:cvt-obama}) is more complicated,
-because it is not possible to have a~\mbox{1-to-1} relationship
+\break The mapping of CVTs (see \autoref{fig:cvt-obama}) is more complicated,
+because it is not possible to have a~\mbox{$1$-to-$1$} relationship
 between Freebase and Wikidata properties: the CVT is linked to the subject topic by one property
@@
 and the main property of the CVT to the same Wikidata property. In a~second step, we
-then use merge these two mappings int a~single Wikidata claim, on which we add the
+then merge these two mappings int a~single Wikidata claim, on which we add the
 other properties from the CVT.
@@
 For example, if we map the CVT shown in \autoref{fig:cvt-obama},
-we first use the Wikidata property \textit{``position held''} (P39) to map
+we first use the Wikidata property \texttt{position held} (P39) to map
 \texttt{/politician/government\_positions\_held} and \linebreak
 \texttt{/government\_position\_held/office\_position\_or\_title}. \linebreak
-Second, for the qualifiers, we use \textit{``start time''} (P580)
-for \texttt{/government\_position\_held/from} and \textit{``end time''} (P582)
+Second, for the qualifiers, we use \texttt{start time} (P580)
+for \texttt{/government\_position\_held/from} and \texttt{end time} (P582)
 for \texttt{/government\_position\_held/to}.
-With the resulting \linebreak property mapping, the created Wikidata statement
+With the then resulting \linebreak property mapping, the created Wikidata statement
 looks like the one presented in \autoref{fig:statement-obama}.
@@
 For CVTs, when we have a~triple whose value is a~CVT, we just retrieve it,
-map all its component triples (while ignoring ones that cannot be mapped)
+map all its component triples (while ignoring ones that cannot be mapped),
 and apply the above mechanism to get its main value.
@@
 (encoded using XSD types~\cite{campbell2003xmlschema})
-to the Wikidata ``time'' datatype. However, we remove dates before 1920 that have
+to the Wikidata \texttt{time} datatype. However, we remove dates before 1920 that have
 a~precision higher than year because we do not know
 if they are relative to the Julian or the Gregorian calendar.
-In such cases, we are not able to fill the ``calendar'' value of the Wikidata ``time'' datatype.
+In such cases, we are unable to fill the \texttt{calendar} value of the Wikidata \texttt{time} datatype.
 
@@
 Such reverse properties sometimes exist in Wikidata
-(like \textit{``children''} for \textit{``father''} and \textit{``mother''}),
+(like \texttt{children} for \texttt{father} and \texttt{mother}),
 but are far less common and also not automatically handled.

### 2016-01-29 paper.tex
Reworked Section 4.x.

@@
 and, in case of approval, add the statement to Wikidata.
-The code of the Primary Sources Tool is openly available
+The code of the \emph{Primary Sources Tool} is openly available
 under the terms of the Apache~2.0 license (\url{https://github.com/google/primarysources}).
 The tool is deployed as a~so-called gadget,
-\emph{i.e.}, as an easy to active add-on feature in Wikidata.
-It is independent from Freebase and can easily be reused to import other datasets into Wikidata.
+so that it can be easily activated as an add-on feature in Wikidata.
+It is independent from Freebase and can be---and already has been---reused to import other datasets into Wikidata.
 
@@
 a~dataset extracted from natural language text.
-We expect more datasets to be added to the Primary Sources Tool in the future.
+We expect more datasets to be added to the \emph{Primary Sources Tool} in the future.
 
@@
 \autoref{fig:primary-sources-tool} shows two screenshots
-of the tool that integrates nicely with the Wikidata user interface.
+of the tool and illustrates how it integrates nicely with the Wikidata user interface.
 To visualize the migration progress, we have created a~realtime dashboard.%
@@
     \end{subfigure}
-    \caption{Primary Sources Tool user interface. Statements coming from
+    \caption{\emph{Primary Sources Tool} user interface. Statements coming from
        Freebase that are not yet available in Wikidata are shown in light blue.
@@
 
-\autoref{fig:architecture} shows the overall architecture of the Primary Sources tool.
+\autoref{fig:architecture} shows the overall architecture of the \emph{Primary Sources Tool}.
 In the following, we describe the back-end, the front-end, and the chosen data rollout plan.
@@
     \includegraphics[width=.65\columnwidth]{img/architecture.pdf}
-    \caption{Primary Sources Tool architecture. The front-end (JavaScript) sends
+    \caption{\emph{Primary Sources Tool} architecture. The front-end (JavaScript) sends
       HTTP requests to the back-end (C++) to retrieve and update entities or
@@
 
-\subsection{Back-end}
+\subsection{Back-End}
 
@@
 and follow the Wikidata data structure with an additional status field
-to keep track of statements that either already have been approved or rejected,
+to keep track of statements that either already have been approved, rejected,
 or not yet visited.
@@
 and ``uploads'' (set of statements uploaded at the same time) in order to
-distinguish data from different sources.\footnote{At the time of this writing,
+distinguish data from different sources.\footnote{At the time of writing,
 the back-end contained five different datasets.}
@@
 that have already been updated (\emph{e.g.}, ``return 10 random rejected statements'')
-for further analysis.
-The default of this parameter is \verb|unapproved|.
+for further analysis or reinvestigattion.
+The default value of this parameter is \verb|unapproved|.
 
@@
 
-\subsection{Front-end}
+\subsection{Front-End}
 
@@
 do not appear in a~user's preferences.
-Instead, one has to add a~line of code into ones \texttt{common.js} file
+Instead, users have to add a~line of code into their \texttt{common.js} file
 in order to activate and use the script.
-User scripts can be created by anyone and might not always be stable.
+User scripts can be created by anyone and---unlike gadgets---might not always be stable.
 
@@
 
-In order to prepare the data for integration into the Primary Sources Tool,
+In order to prepare the data for integration into the \emph{Primary Sources Tool},
 we have created a~set of scripts which map the content
@@
 \url{https://github.com/google/freebase-wikidata-converter}}
-The Primary Sources Tool was developed in parallel with the mapping scripts.
+The \emph{Primary Sources Tool} was developed in parallel with the mapping scripts.
 We first created a~small dataset of around 1~million statements
@@
 in case of incoming claims with references, freshly accepted claims
-can require incoming references to be attached elsewhere in the item.
+can require incoming references to be attached elsewhere in the item,
+which is hard to keep track of without a~refresh.
 
@@
 using a~customizable and generalizable approach, consisting of data preparation scripts
-and the Primary Sources Tool,
+and the \emph{Primary Sources Tool},
 which is well integrated into the Wikidata user interface.
@@
 and, in consequence, the ``value'' of such collaborative knowledge bases and the datasets added to them.
-We hope that with the help of the Primary Sources Tool and
+We hope that with the help of the \emph{Primary Sources Tool} and
 the Freebase dataset, and in future also other datasets,

### 2016-01-29 paper.tex
Reworked Section 5.1.

@@
 ``Useful'' facts are the triples that remain
-after filtering out all triples about IDs (\texttt{/type/object/id}),
-types \linebreak (\texttt{/type/object/type}), labels, descriptions \linebreak
-(\texttt{/type/object/name},
-\texttt{/common/topic/description}, \emph{etc.}), \linebreak and triples removed
+after filtering out all triples about labels
+(\texttt{/type/object/name}, identifiers (\texttt{/type/object/id}),
+types (\texttt{/type/object/type}), descript\-ions
+(\texttt{/common/topic/description}), \emph{etc.}), and triples removed
 for licensing reasons (the latter were about 42~million, see \autoref{sec:licensing}).
@@
 
-As a~direct comparison, here are the raw statistics for Wikidata as of August 2015.
+As a~direct comparison, in the following we provide the raw statistics for Wikidata as of August 2015.
 
@@
 that is used in order to be able to traverse the Freebase graph easily in both directions.
-For example, the property \texttt{/people/person/place\_of\_birth} has the corresponding
+For example, the property \texttt{/people/person/place\-\_of\_birth} has the corresponding
 reverse property \linebreak \texttt{/location/location/people\_born\_here}
@@
 is discussed in more detail in~\cite{reification-wikidata}.
-
 In a~considerable amount of cases, Freebase also contains duplicate data.

### 2016-01-29 paper.tex
Reworked Section 5.1 and 5.2.

@@
 that is shown in \autoref{fig:time-space}.
-
 We extracted the earliest date and the longitude
@@
 There are no strong differences between them,
-yet coverage of \mbox{\emph{post}-year-2000} entities seems stronger in Freebase.
+yet coverage of \emph{post}-year-2000 entities seems stronger in Freebase.
 
@@
 We certainly can note that for data sets to be added to a~knowledge bases,
-the raw number of triples is not an adequate measure of quality.
+the raw number of triples is \emph{not} an adequate measure of quality.
 

### 2016-01-29 paper.tex
Reworked Section 5.3.
Reworked Section 6.

@@
 \widowpenalty = 10000
+
+\hyphenation{DBpedia Wikipedia Wikidata Freebase}
 
@@
 and \emph{(ii)} due to the US population CVTs in Freebase.
-
 The big horizontal lines in \autoref{fig:freebase} and even more in \autoref{fig:wikidata}
@@
 and facts already contained in Wikidata, we obtain 14~million new statements.
-
 If all these statements were added to Wikidata,
@@
 
-This raises the question why these numbers are so low compared to the size of Freebase, given at
-3~billion facts.
+This raises the question why these numbers are so low compared to the size of Freebase of 3~billion facts.
 The main reason is that we have only mapped 4.56~million items to Wikidata,
@@
 
-For the challenges listed in \autoref{sec:challenges-of-the-migration}
-there is a~body of work dealing with it. In many cases, the problems we have encountered in
+For the challenges listed in \autoref{sec:challenges-of-the-migration},
+there are a~number of works dealing with it. In many cases, the problems we have encountered in
 this migration have turned out to be much simpler than the problems solved in existing research.
@@
 they are often added as an afterthought.
-They have been preciously few dedicated publications on the
+There have been remarkably few dedicated publications on the
 topic~\cite{licenses,licensius}, none of them written by lawyers.
-Due to the lack of understanding surronding these topics, we have been
-cautious and chose to simply remove any facts from the migrating data
-where the situation is in doubt.
+Due to the lack of understanding surrounding these topics, we have been
+cautious and chose to simply remove any facts from the to-be-migrated data
+if there were doubts.
 
@@
 of two databases or knowledge bases
-(some surveys are~\cite{mappingsurvey1,mappingsurvey2,mappingsurvey3}).
+(some surveys are~\cite{mappingsurvey3,mappingsurvey2,mappingsurvey1}).
 The current work is, in many technical respects, rather simple:
@@
 and does not allow for point-fixes, thus necessitating a~higher quality of the mapping,
-whereas for the Freebase to Wikidata mapping every single results is expected to be curated.
-The schema.org structured data project is also exploring mappings to and from Wikidata,
-to facilitate the use of Wikidata's vocabulary as schema.org markup across the wider Web.
-This involves similar issues mapping schema.org's CVT-like statement qualification mechanism, Roles,
+whereas for the Freebase to Wikidata mapping every single result is expected to be curated.
+The Schema.org structured data project is also exploring mappings to and from Wikidata,
+to facilitate the use of Wikidata's vocabulary as Schema.org markup across the wider Web.
+This involves similar issues mapping\linebreak Schema.org's CVT-like statement qualification mechanism and roles
 to Wikidata conventions.%
@@
 Wikipedia is often used as a~benchmark for entity mapping systems~\cite{entitylinkingwikipedia}.
-As described in \autoref{subsec:topic-mappings} this lead to sufficiently good results for the head,
-and we think it would be surprising if further effort in this area would lead to reasonable gains.
+As described in \autoref{subsec:topic-mappings} this leads to sufficiently good results,
+and we argue it would be surprising if further effort in this area would lead to reasonable gains.
 
 \textbf{Data maintenance.}
-The Wikidata requirements~\cite{wikidatareqs} states that the data uploaded to Wikidata
+The Wikidata requirements~\cite{wikidatareqs} state that the data uploaded to Wikidata
 must not overwhelm the community.

### 2016-01-29 paper.tex
Reworked Section 7.

@@
 In this paper, we describe how we support the Wikidata community with
-the migration of Freebase content to Wikidata.
+the migration of Freebase content to\linebreak Wikidata.
 We programmed the \emph{Primary Sources Tool} and
@@
 to add information about it like ``taxon author is Carl Linnaeus''.
-\autoref{fig:statement} illustrates the used terminology with an example.
+\autoref{fig:statement} illustrates the used Wikidata terminology with an example.
 
@@
 a~Wikidata item share at least two Wikipedia links, they are assumed to describe the same subject.
-The quality of this mapping is considered very good by the Wikidata community,
+The quality of this mapping is considered very good by the\linebreak Wikidata community,
 who thus have decided to use it and further curate and maintain it by hand.
@@
 
-\subsubsection{Reconciliation Based on External Database IDs}
+\subsubsection{Reconciliation Based on External Identifiers}
 
@@
 VIAF~\cite{viaf}, \emph{etc.}
-With this technique, we were able to match 800,000~external database IDs,
+With this technique, we were able to match 800,000~external data\-base IDs,
 creating an additional mapping for 600,000~to\-pics---%
@@
 As outlined earlier, the \emph{Primary Sources Tool} is a~crowdsourced human curation
-software solution that displays Freebase statements for verification to the Wikidata contributor
+software solution that displays\linebreak Freebase statements for verification to the Wikidata contributor
 so that these statements can be added to the currently shown Wikidata item.
@@
 and, in case of approval, add the statement to Wikidata.
-The code of the \emph{Primary Sources Tool} is openly available
-under the terms of the Apache~2.0 license (\url{https://github.com/google/primarysources}).
-The tool is deployed as a~so-called gadget,
-so that it can be easily activated as an add-on feature in Wikidata.
+The code of the \emph{Primary Sources Tool} is openly available (\url{https://github.com/google/primarysources})
+under the terms of the\linebreak Apache~2.0 license.
+The tool is deployed as a~gadget,
+so that it can be easily enabled as an add-on feature in Wikidata.
 It is independent from Freebase and can be---and already has been---reused to import other datasets into Wikidata.
@@
 the back-end contained five different datasets.}
-
 The REST API of the back-end supports the following main types of requests:
@@
 Concluding, in a~fairly short amount of time, we have been able
-to provide to the Wikidata community more than\linebreak 14~million new Wikidata statements
+to provide the Wikidata community with more than\linebreak 14~million new Wikidata statements
 using a~customizable and generalizable approach, consisting of data preparation scripts
@@
 The effort needed to map two fairly different knowledge bases has also been a~good occasion
-to highlight the difficulty of having good metrics to measure the size of knowledge bases
+to highlight the difficulty of having adequate metrics to measure the size of knowledge bases
 in a~meaningful way,
@@
 We hope that with the help of the \emph{Primary Sources Tool} and
-the Freebase dataset, and in future also other datasets,
-will increase the completeness and accuracy of Wikidata.
+the Freebase dataset---and in future also other datasets---%
+we will increase the completeness and accuracy of Wikidata.
 

### 2016-01-29 paper.tex
Added a subsection on the motivation for the shutdown and on Freebase's future.

@@
 (DBpedia, YAGO, and OpenCyc) is available in~\cite{farbercomparative} by Färber \emph{et~al.}
+
+\subsection{Motivation for the Migration}
+
+When Google publicly launched Freebase back in 2007, Freebase was thought of as a ``Wikipedia for structured data''.
+The Knowledge Graph team at Google have been closely watching the Wikimedia Foundation's project Wikidata since its launch,
+and believe strongly in a robust community-driven effort to collect and curate structured knowledge about the world.
+The team now think they can serve that goal best by supporting Wikidata, as the project is growing fast,
+has an active community, and is better-suited to lead an open collaborative knowledge base~\cite{freebase2014shutdown}.
+
+In consequence, in mid-2015, the Freebase service as a standalone project was wound down.
+Freebase always has supported developer access to the data;
+in order to still cater for this need,
+a~new API for entity search powered by Google's Knowledge Graph was launched.%
+\footnote{Knowledge Graph Search API: \url{https://developers.google.com/knowledge-graph/?hl=en}}
+Freebase has as of March 31, 2015, gone read-only, \emph{i.e.},
+the website no longer accepts edits and the MQL write API was retired.
 

### 2016-01-29 paper.tex
Added new screenshot with external dataset.

@@
 Thereby, we were able to slowly upscale the tool's database back-end
-without risking back-end performance bottlenecks.
+without risking back-end performance bottlenecks,
+and so far, scale or throughput have not been a~problem.
 The process of adding data in small batches of 1~million to 2~million statements per batch
@@
 which is hard to keep track of without a~refresh.
+
+\subsection{Usage with Other Datasets}
+
+As outlined earlier, the \emph{Primary Sources Tool} from the start was designed to be used
+with other datasets apart from the Freebase dataset.
+A~concrete first example is the ``FBK StrepHit Soccer'' dataset,%
+\footnote{``FBK StrepHit Soccer'' dataset:
+\url{https://lists.wikimedia.org/pipermail/wikidata/2015-September/007014.html}}
+which, among other datasets, can be activated in the tool by clicking on its gears icon.
+The dataset selection dialog is depicted in \autoref{fig:soccer},
+as well as facts coming from this dataset.
+It is also possible to activate all datasets at once in parallel.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=0.93\columnwidth]{img/fbk-strephit-soccer.pdf}
+    \caption{\emph{Primary Sources Tool} used with the ``FBK StrepHit Soccer'' dataset,
+    the screenshot shows the dataset selection dialog and incoming facts from this dataset.}
+    \label{fig:soccer}
+\end{figure}
 
@@
 
-\section{Future Work and Conclusion}\label{sec:future-work-and-conclusion}
+\section{Future Work and Conclusions}\label{sec:future-work-and-conclusion}
 
@@
 from already mapped topics and filter less interesting types like ISBNs.
-
 Another area for improvement is to upload high quality datasets using a~bot,
@@
 like birth date, death place or gender using a~bot.
-We have also started to import labels that are in Freebase and are absent from Wikidata.
+We have started to import labels that are in Freebase but not in Wikidata.
 In the 17.2~million Freebase labels for mapped topics,
-only 0.9~million, \emph{i.e.}, 5\%, are missing in Wikidata.
+only 0.9~million, \emph{i.e.}, 5\%, lack from Wikidata.
 
@@
 We hope that with the help of the \emph{Primary Sources Tool} and
-the Freebase dataset---and in future also other datasets---%
+the Freebase dataset---and in future even more datasets---%
 we will increase the completeness and accuracy of Wikidata.
